---
title: "Pilot Conditionals"
output: pdf_document
date: '2022-11-15'
---

#Set-up and Read in Data

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-apa


```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(afex)
library(apa)

#read in data

pilot_conditional <- read.csv(here("pilot_conditionals.csv"))
```

# condition 1 = never
# condition 2 = rarely 
#condition 3 =  sometimes 
#condition 4 = never-harm
#condition 5 =  never-goodreason
#condition 6 = never-exceptional
#condition 7 = sometimes-harm
#condition 8 = sometimes-goodreason
#condition 9 = sometimes-exceptional
#condition 10 = control


# Honest Model
```{r}
honestyGD.afex <-aov_car(Honest_compositeGD ~ condition  + Error(id), data= pilot_conditional)
summary(honestyGD.afex) 
anova_apa(honestyGD.afex)  
```


# Subset to be just solo statements

```{r}
solo_stance_test <- pilot_conditional %>%
  filter(condition == "1" | condition  == "2" | condition  == "3") 
glimpse(solo_stance_test)

solo_honesty.afex <-aov_car(Honest_compositeGD ~ 
                              condition + Error(id), 
                            data= solo_stance_test)
summary(solo_honesty.afex ) 
anova_apa(solo_honesty.afex ) 

#Subet to compare never stances
never_test <- pilot_conditional %>%
  filter(condition  == "1" | condition  == "4" | 
           condition  == "5" | condition  == "6") 
glimpse(never_test)

#Honesty never ANOVA
never_test.afex <-aov_car(Honest_compositeGD ~ 
                            condition  + Error(id), 
                            data= never_test)
summary(never_test.afex) 
anova_apa(never_test.afex) 

#compare original abs (never) to other cells
#never (1) vs. harm (4)
never_v_harm <- never_test %>%
  filter(condition  == "1" | condition  == "4")
t.test(Honest_compositeGD~ condition , never_v_harm, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition , never_v_harm, var.equal = TRUE))

#never (1) vs. good reason (5)
never_v_goodreason <- never_test%>%
  filter(condition  == "1" | condition  == "5")
t.test(Honest_compositeGD~ condition , never_v_goodreason, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition , never_v_goodreason, var.equal = TRUE))

#never (1) vs. exceptional (6) 
never_v_exceptional <- never_test%>%
  filter(condition  == "1" | condition  == "6")
t.test(Honest_compositeGD~ condition , never_v_exceptional, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition , never_v_exceptional, var.equal = TRUE))

```

# Moral Model

```{r}
#Moral never ANOVA
never_testm.afex <-aov_car(M_compositeGD ~ 
                             condition  + Error(id), 
                          data= never_test)
summary(never_testm.afex ) 
anova_apa(never_testm.afex ) 

#t-test
#compare original abs (never) to other cells
#never (1) vs. harm (4), use subsetted dataframe from above

#Moral
t.test(M_compositeGD ~ condition, never_v_harm, var.equal = TRUE)
t_apa(t.test(M_compositeGD  ~ condition, never_v_harm, var.equal = TRUE))


#never (1) vs. good reason (5)
#Moral
t.test(M_compositeGD ~ condition , never_v_goodreason, var.equal = TRUE)
t_apa(t.test(M_compositeGD  ~ condition , never_v_goodreason, var.equal = TRUE))

#never (1) vs. exceptional (6) 
#moral
t.test(M_compositeGD ~ condition , never_v_exceptional, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition , never_v_exceptional, var.equal = TRUE))

#Also want to compare sometimes stances
sometimes_test <- pilot_conditional  %>%
  filter(condition  == "1" | condition  == "4" | 
           condition  == "5" | condition  == "6") 
glimpse(sometimes_test )
```

