---
title: "Pilot Conditionals"
output: pdf_document
date: '2022-11-15'
---

#Set-up and Read in Data

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-apa


```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(afex)
library(apa)
library(psych)

#read in data

pilot_conditional <- read.csv(here("pilot_conditionals.csv"))
```

#condition 1 = never
#condition 2 = rarely 
#condition 3 =  sometimes 
#condition 4 = never-harm
#condition 5 =  never-goodreason
#condition 6 = never-exceptional
#condition 7 = sometimes-harm
#condition 8 = sometimes-goodreason
#condition 9 = sometimes-exceptional
#condition 10 = control


# Composite DVs

```{r}
#Morality
moral_check <- data.frame(pilot_conditional$m1, pilot_conditional$m2, 
                          pilot_conditional$m3)
summary(moral_check)
describe(moral_check)
psych::alpha(moral_check) # rawalpha = 0.96
pilot_conditional <- mutate(pilot_conditional, 
              M_compositeGD = 
                ((pilot_conditional$m1 + pilot_conditional$m2 + 
                   pilot_conditional$m3)/3))

#Future Honesty
honest_check <- data.frame(pilot_conditional$honest_l,
                           pilot_conditional$honest_e, 
                           pilot_conditional$honest_f,
                           pilot_conditional$comm_honest)
summary(honest_check)
describe(honest_check)
psych::alpha(honest_check) # raw alpha = 0.79
pilot_conditional <- mutate(pilot_conditional, 
              Honest_compositeGD = 
                ((pilot_conditional$honest_l + pilot_conditional$honest_e
                  + pilot_conditional$honest_f +
                    pilot_conditional$comm_honest)/4))
```

# Descriptives

```{r}
# Morality
tapply(pilot_conditional$Honest_compositeGD, pilot_conditional$condition, 
       FUN = mean)
tapply(pilot_conditional$Honest_compositeGD, pilot_conditional$condition, 
       FUN = sd)
tapply(pilot_conditional$Honest_compositeGD, pilot_conditional$condition, 
       FUN = length)


#Future Honesty
tapply(pilot_conditional$M_compositeGD, pilot_conditional$condition, 
       FUN = mean)
tapply(pilot_conditional$M_compositeGD, pilot_conditional$condition, 
       FUN = sd)
tapply(pilot_conditional$M_compositeGD, pilot_conditional$condition, 
       FUN = length)

```


# Never + Sometimes Conditionals
Compare inferences in conditions 1 (never) vs. 7, 8, 9 (sometimes conditionals)

```{r}
#Subset to compare only conditions 1, 7, 8, 9
never_v_sconditions <- pilot_conditional %>%
  filter(condition == "1" | condition  == "7" | 
           condition  == "8" | condition  == "9")

glimpse(never_v_sconditions)

#Never v. Sometimes-harm (7)
never_v_harm  <- never_v_sconditions %>%
  filter(condition  == "1" | condition  == "7")

#Moral
t.test(M_compositeGD ~ condition, never_v_harm, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, never_v_harm, var.equal = TRUE))
#Never still more moral than sometimes + harm

#Honest
t.test(Honest_compositeGD~ condition, never_v_harm, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, never_v_harm, var.equal = TRUE))
#Yes, also more honest

#Never v. Sometimes-goodreason (8)
never_v_goodreason  <- never_v_sconditions %>%
  filter(condition  == "1" | condition  == "8")

#Moral
t.test(M_compositeGD ~ condition, never_v_goodreason, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, never_v_goodreason, var.equal = TRUE))
#Never still more moral than sometimes + good reason

#Honest
t.test(Honest_compositeGD~ condition, never_v_goodreason, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, never_v_goodreason, var.equal = TRUE))
#And more honest

#Never v. Sometimes -exceptional (9)
never_v_exceptional  <- never_v_sconditions %>%
  filter(condition  == "1" | condition  == "9")

#Moral
t.test(M_compositeGD ~ condition, never_v_exceptional, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, never_v_exceptional, var.equal = TRUE))
#Never still more moral than sometimes + exceptional

#Honest
t.test(Honest_compositeGD~ condition, never_v_exceptional, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, never_v_exceptional, var.equal = TRUE))
#And more honest

```


# Original Stances (never vs. rarely vs. sometimes)

Compare conditions 1, 2, 3

```{r}
# Subset to be just solo statements
solo_stance_test <- pilot_conditional %>%
  filter(condition == "1" | condition  == "2" | condition  == "3") 
glimpse(solo_stance_test)
solo_stance_test$condition <- as.factor(solo_stance_test$condition)
levels(solo_stance_test$condition)

#Morality
solo_moral.afex <-aov_car(M_compositeGD ~ 
                              condition + Error(id), 
                            data= solo_stance_test)
summary(solo_moral.afex) 
anova_apa(solo_moral.afex)
# Condition is significant on honesty

#Honesty
solo_honesty.afex <-aov_car(Honest_compositeGD ~ 
                              condition + Error(id), 
                            data= solo_stance_test)
summary(solo_honesty.afex) 
anova_apa(solo_honesty.afex)
# Condition is significant on honesty

# Main effect: never (1) vs. rarely (2) vs. sometimes (3)

#never (1) vs. rarely (2)
never_v_rarely  <- solo_stance_test %>%
  filter(condition  == "1" | condition  == "2")
#Moral
t.test(M_compositeGD ~ condition , never_v_rarely, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition , never_v_rarely, var.equal = TRUE))
#Never slightly more moral than rarely, significant p = .029

#Honest
t.test(Honest_compositeGD~ condition , never_v_rarely, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition , never_v_rarely, var.equal = TRUE))
#Never more honest than rarely, p = .019


#never (1) vs. sometimes (3)
never_v_sometimes  <- solo_stance_test %>%
  filter(condition  == "1" | condition  == "3")
#Moral
t.test(M_compositeGD ~ condition , never_v_sometimes, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition , never_v_sometimes, var.equal = TRUE))

#Honest
t.test(Honest_compositeGD ~ condition , never_v_sometimes, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition , never_v_sometimes, var.equal = TRUE))

#replicate never > sometimes effect

#rarely (2) vs. sometimes (3)
rarely_v_sometimes  <- solo_stance_test %>%
  filter(condition  == "3" | condition  == "2")

#Moral
t.test(M_compositeGD ~ condition, rarely_v_sometimes, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, rarely_v_sometimes, var.equal = TRUE))

#Honest
t.test(Honest_compositeGD~ condition, rarely_v_sometimes, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, rarely_v_sometimes, var.equal = TRUE))
#Yes replicate rarely > sometimes
```


# Compare Never alone vs. Never + Conditionals

Subset to compare never (1) vs. never + conditionals (4, 5, 6)

```{r}
#Subset to compare never stances
never_test <- pilot_conditional %>%
  filter(condition  == "1" | condition  == "4" | 
           condition  == "5" | condition  == "6") 
glimpse(never_test)

#never (1) vs. never harm (4)
never_v_nharm <- never_test %>%
  filter(condition  == "1" | condition  == "4")

#Moral
t.test(M_compositeGD ~ condition , never_v_nharm, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition , never_v_nharm, var.equal = TRUE))
#See comparably, no sign diff

#Honest
t.test(Honest_compositeGD ~ condition , never_v_nharm, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition , never_v_nharm, var.equal = TRUE))
#never alone slightly more honest, p = .029

#never (1) vs. never good reason (5)
never_v_ngoodreason <- never_test %>%
  filter(condition  == "1" | condition  == "5")

#Moral
t.test(M_compositeGD ~ condition, never_v_ngoodreason, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, never_v_ngoodreason, var.equal = TRUE))
#never alone more moral

#Honest
t.test(Honest_compositeGD ~ condition, never_v_ngoodreason, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, never_v_ngoodreason, var.equal = TRUE))
#never alone more honest

#never (1) vs. never exceptional (6) 
never_v_nexceptional <- never_test%>%
  filter(condition  == "1" | condition  == "6")

#Moral
t.test(M_compositeGD ~ condition, never_v_nexceptional, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, never_v_nexceptional, var.equal = TRUE))
#no significant diff, but never alone trending better, p = .054

#Honest
t.test(Honest_compositeGD ~ condition, never_v_nexceptional, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, never_v_nexceptional, var.equal = TRUE))
#never alone more honest

```

# Do Conditionals Make Sometimes Better?

```{r}
#Subset sometimes only
sometimes_test <- pilot_conditional  %>%
  filter(condition  == "3" | condition  == "7" | 
           condition  == "8" | condition  == "9") 
glimpse(sometimes_test)

#sometimes (3) vs. sometimes harm (7)
some_v_sharm <- sometimes_test %>%
  filter(condition  == "3" | condition  == "7")

#Moral
t.test(M_compositeGD ~ condition, some_v_sharm, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, some_v_sharm, var.equal = TRUE))
#Yes, conditional does make sometimes better

#Honest
t.test(Honest_compositeGD ~ condition, some_v_sharm, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, some_v_sharm, var.equal = TRUE))
#But does not affect honesty

#sometimes (3) vs. sometimes good reason (8)
some_v_sgoodreason <- sometimes_test %>%
  filter(condition  == "3" | condition  == "8")

#Moral
t.test(M_compositeGD ~ condition, some_v_sgoodreason, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, some_v_sgoodreason, var.equal = TRUE))
#interesting that not better

#Honest
t.test(Honest_compositeGD ~ condition, some_v_sgoodreason, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, some_v_sgoodreason, var.equal = TRUE))
#not more honest

#sometimes (3) vs. sometimes exceptional (9) 
some_v_soexceptional <- sometimes_test %>%
  filter(condition  == "3" | condition  == "9")

#Moral
t.test(M_compositeGD ~ condition, some_v_soexceptional, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, some_v_soexceptional, var.equal = TRUE))
#does make it better

#Honest
t.test(Honest_compositeGD ~ condition, some_v_soexceptional, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, some_v_soexceptional, var.equal = TRUE))
#and more honest

```

# Control v Never and Sometimes

```{r}
#Compare 1 vs. 10
#Subset to compare only conditions 1, 7, 8, 9
never_v_control <- pilot_conditional %>%
  filter(condition == "1" | condition  == "10")

glimpse(never_v_control)

#Moral
t.test(M_compositeGD ~ condition, never_v_control, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, never_v_control, var.equal = TRUE))
#no diff

#Honest
t.test(Honest_compositeGD ~ condition, never_v_control, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, never_v_control, var.equal = TRUE))
#more honest

#Compare 3 vs. 10
sometimes_v_control <- pilot_conditional %>%
  filter(condition == "3" | condition  == "10")

glimpse(sometimes_v_control)

#Moral
t.test(M_compositeGD ~ condition, sometimes_v_control, var.equal = TRUE)
t_apa(t.test(M_compositeGD ~ condition, sometimes_v_control, var.equal = TRUE))
#no diff

#Honest
t.test(Honest_compositeGD ~ condition, sometimes_v_control, var.equal = TRUE)
t_apa(t.test(Honest_compositeGD ~ condition, sometimes_v_control, var.equal = TRUE))
#more honest
```

# Look at participants own views

```{r}
#remove Control/NA (they did not have this Q)
agree_no_control <- pilot_conditional %>%
  filter(condition != "10")
glimpse(agree_no_control)

#look at agreement by stance
tapply(agree_no_control$agree, agree_no_control$condition, FUN = mean)

# Is agreement in never v. 7 or 9 significant?
# 1 vs. 7
onev7l <- agree_no_control %>%
  filter(condition == "1" | condition  == "7")
glimpse(onev7l)
t.test(agree ~ condition, onev7l, var.equal = TRUE)
t_apa(t.test(agree ~ condition, onev7l, var.equal = TRUE))
#no diff
#1 vs. 9
onev9 <- agree_no_control %>%
  filter(condition == "1" | condition  == "9")
glimpse(onev9)
t.test(agree ~ condition, onev9, var.equal = TRUE)
t_apa(t.test(agree ~ condition, onev9, var.equal = TRUE))
#no diff

#Is never v rarely agreement different?
# 1 vs. 2
onevtwo <- agree_no_control %>%
  filter(condition == "1" | condition  == "2")
glimpse(onevtwo)
t.test(agree ~ condition, onevtwo, var.equal = TRUE)
t_apa(t.test(agree ~ condition, onevtwo, var.equal = TRUE))
#no diff

```

