---
title: "Study 3"
author: "Elizabeth Huppert"
date: "1/14/2020"
output: pdf_document
---

# Set-up and Read in Data

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-apa
-dplyr
-psych
-emmeans

```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(afex)
library(apa)
library(dplyr)
library(psych)
library(emmeans)

#read in data

s3 <- read.csv(here("HypocrisyStudy3_cleaned.csv"))

```


Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


# Models

Key variable names (also see codebook for more information):

1. Proclamation:
Assignment to one of three conditions: "Lying is never [rarely/sometimes] okay" (absolute vs. ambitious vs. flexible)

2. Behavior:
Assignment to "prosocial.lie" vs. "selfish.truth"  

3. Behavlie:
prosocial lie = 1, selfish truth = 0

4. rv:
Decisions to RELY (1) or VERIFY (0) in the RV game

5. Sometimes:
Dummy-coded proclamation variable (sometimes = 1, rarely/never = 0)

6. Rarely:
Dummy-coded proclamation variable (rarley = 1, sometimes/never = 0)

7. Never:
Dummy-coded proclamation variable (never = 1, sometimes/rarely = 0)

Supplemental:

Pref = Attitudes towards honesty;1-5 statement
("Lying is always [often/sometimes/rarely/never] okay" = 1-5)

# Factorize Subject (id) and Trust (rv game pass or rely)

```{r}
s3$ID <- as.factor(s3$ID)
s3$rv_f <- as.factor(s3$rv)
s3$proclamation <- as.factor(s3$proclamation)
s3$behavior <- as.factor(s3$behavior)
```

# Composite Evaluation Variables

Items with high agreement were combined as per our pre-registration.

```{r}
#Hypocrisy
hypocrisy3_check <- data.frame(s3$Hypocrisy_1, s3$Hypocrisy_2, s3$Hypocrisy_3, s3$Hypocrisy_4, s3$Hypocrisy_5)
summary(hypocrisy3_check)
describe(hypocrisy3_check)
psych::alpha(hypocrisy3_check) #alpha = 0.92
s3 <- mutate(s3, 
             Hypocrisy_composite3 = ((s3$Hypocrisy_1 + s3$Hypocrisy_2 + s3$Hypocrisy_3 + s3$Hypocrisy_4 + s3$Hypocrisy_5)/5))

#Morality  
moral3_check <- data.frame(s3$Moral_1, s3$Moral_2, s3$Moral_3)
summary(moral3_check)
describe(moral3_check)
psych::alpha(moral3_check) #alpha = .96
s3 <- mutate(s3, 
             Moral_composite3 = ((s3$Moral_1+s3$Moral_2+s3$Moral_3)/3))


#Commitment to Honesty 
honest3_check <- data.frame(s3$Honest_frequency, s3$Honest_likely, s3$Honest_extreme, s3$Honest_committment)
summary(honest3_check)
describe(honest3_check)
psych::alpha(honest3_check) #alpha = 0.84
s3<- mutate(s3, 
            Honest_composite3 = ((s3$Honest_frequency + s3$Honest_likely + s3$Honest_extreme + s3$Honest_committment)/4))


```

Evaluation variables:

Hypocrisy_composite3 = hypocrisy composite of 5 items (Ratings: 1-7)
Moral_composite3 = morality composite of 3 items (Ratings: 1-7)
Honest_composite3 = commitment to honesty composite of 4 items (Ratings: 1-7)

#Hypocrisy Model

```{r}
#ANOVA
hypocrisy_3.afex <-aov_car(Hypocrisy_composite3 ~ proclamation*behavior + Error(ID), data=s3)
summary(hypocrisy_3.afex) 
anova_apa(hypocrisy_3.afex)
```

#Hypocrisy Descriptives

```{r}
#Cells
tapply(s3$Hypocrisy_composite3, list(s3$proclamation, s3$behavior), mean)
tapply(s3$Hypocrisy_composite3, list(s3$proclamation, s3$behavior), sd)
tapply(s3$Hypocrisy_composite3, list(s3$proclamation, s3$behavior), length)

#Across Proclamation
tapply(s3$Hypocrisy_composite3, s3$proclamation, mean)
tapply(s3$Hypocrisy_composite3, s3$proclamation, sd)
tapply(s3$Hypocrisy_composite3, s3$proclamation, length)

#Across Behavior
tapply(s3$Hypocrisy_composite3, s3$behavior, mean)
tapply(s3$Hypocrisy_composite3, s3$behavior, sd)
tapply(s3$Hypocrisy_composite3, s3$behavior, length)

#Overall
mean(s3$Hypocrisy_composite3)
sd(s3$Hypocrisy_composite3)
length(s3$Hypocrisy_composite3)

```

#Hypocrisy Simple Effects - Subsetting Data

```{r}
#How does behavior vary by proclamation type?
#Subset for main effects tests

never_s3 <- s3 %>%
  filter(proclamation == "never") #192 - never

rarely_s3 <- s3 %>%
  filter(proclamation == "rarely") #202 - rarely

sometimes_s3 <- s3 %>%
  filter(proclamation == "sometimes") #204 - never

#Subset for one level of one factor 

never_exclude <- s3 %>%
  filter(proclamation != "never")  #406, rarely and sometimes

rarely_exclude <- s3 %>%
  filter(proclamation != "rarely") #396, never and sometimes

sometimes_exclude <- s3 %>%
  filter(proclamation != "sometimes") #394, never and rarely

#Selfish truth - rarely sometimes
never_truth <- never_exclude %>%
  filter(behavior == "selfish.truth") #197

#Prosocial lie - rarely sometimes
never_lie <- never_exclude %>%
  filter(behavior == "prosocial.lie") #209

#Selfish truth - never sometimes
rarely_truth <- rarely_exclude %>%
  filter(behavior == "selfish.truth") #194

#Prosocial lie- never sometimes
rarely_lie <- rarely_exclude %>%
  filter(behavior == "prosocial.lie") #202

#Selfish truth - never rarely
sometimes_truth <- sometimes_exclude %>%
  filter(behavior == "selfish.truth") #189

#Prosocial lie -never rarely
sometimes_lie <- sometimes_exclude %>%
  filter(behavior == "prosocial.lie") #205
```

#Hypocrisy Simple Effects - T-tests

```{r}
#T-tests
#Rarely vs. sometimes, selfish truth
t.test(Hypocrisy_composite3 ~ proclamation, never_truth, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, never_truth, var.equal = TRUE))

#Rarely vs. sometimes, prosocial lie
t.test(Hypocrisy_composite3 ~ proclamation, never_lie, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, never_lie, var.equal = TRUE))

#Never vs. sometimes, selfish truth
t.test(Hypocrisy_composite3 ~ proclamation, rarely_truth, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, rarely_truth, var.equal = TRUE))

#Never vs. sometimes, prosocial lie
t.test(Hypocrisy_composite3 ~ proclamation, rarely_lie, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, rarely_lie, var.equal = TRUE))

#Never vs. rarely, selfish truth
t.test(Hypocrisy_composite3 ~ proclamation, sometimes_truth, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, sometimes_truth, var.equal = TRUE))

#Never vs. rarely, prosocial lie
t.test(Hypocrisy_composite3 ~ proclamation, sometimes_lie, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, sometimes_lie, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
hyp_model = aov_ez('ID', 'Hypocrisy_composite3', s3,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(hyp_model)
means <- emmeans(hyp_model, ~ proclamation|behavior)
print(means)
post1 <- emmeans(hyp_model, ~ proclamation|behavior)
pairs(post1)


```


#Morality Model

```{r}
#ANOVA
moral_3.afex <-aov_car(Moral_composite3 ~ proclamation*behavior + Error(ID), data=s3)
summary(moral_3.afex) 
anova_apa(moral_3.afex)

#Abs vs. Flex morality focal - need cohen's D
#abs mean =  5.027778, sd = 1.427859, 192 
#flex mean =  4.075163, sd = 1.424938, 204
#pooled SD = sqrt(((1.427859^2) + (1.424938^2))/2)
sqrt((((1.427859^2) + (1.424938^2))/2)) #1.426399

#cohens = (mean - mean)/SD pooeld
(5.027778-4.075163)/1.426399 #0.6678461

d3 <- cohens_d(t_test(Moral_composite3 ~ proclamation, rarely_exclude)) 
#see Hypocrisy Simple Effects above to exclude rarely, N = 396
d3 #Cohen's d abs. vs. flex. on morality (abs value)  = 0.6678664 (0.67)
```


#Morality Descriptives

```{r}
#Cells
tapply(s3$Moral_composite3, list(s3$proclamation, s3$behavior), mean)
tapply(s3$Moral_composite3, list(s3$proclamation, s3$behavior), sd)
tapply(s3$Moral_composite3, list(s3$proclamation, s3$behavior), length)

#Across Proclamation
tapply(s3$Moral_composite3, s3$proclamation, mean)
tapply(s3$Moral_composite3, s3$proclamation, sd)
tapply(s3$Moral_composite3, s3$proclamation, length)

#Across Behavior
tapply(s3$Moral_composite3, s3$behavior, mean)
tapply(s3$Moral_composite3, s3$behavior, sd)
tapply(s3$Moral_composite3, s3$behavior, length)

#Overall
mean(s3$Moral_composite3)
sd(s3$Moral_composite3)
length(s3$Moral_composite3)

```

#Morality Simple Effects 

Note: For these tests, use subsetted data from Hypocrisy simple effects test (previous code chunk).


```{r}
#Main effect of proclamation
#Never vs. rarely only
t.test(Moral_composite3 ~ proclamation, sometimes_exclude, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, sometimes_exclude, var.equal = TRUE))

#Never vs. sometimes  only
t.test(Moral_composite3 ~ proclamation, rarely_exclude, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, rarely_exclude, var.equal = TRUE))

#Rarely  vs. sometimes  only
t.test(Moral_composite3 ~ proclamation, never_exclude, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, never_exclude, var.equal = TRUE))


# Simple Effects

#T-tests
#Rarely vs. sometimes, selfish truth
t.test(Moral_composite3 ~ proclamation, never_truth, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, never_truth, var.equal = TRUE))

#Rarely vs. sometimes, prosocial lie
t.test(Moral_composite3 ~ proclamation, never_lie, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, never_lie, var.equal = TRUE))

#Never vs. sometimes, selfish truth
t.test(Moral_composite3 ~ proclamation, rarely_truth, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, rarely_truth, var.equal = TRUE))

#Never vs. sometimes, prosocial lie
t.test(Moral_composite3 ~ proclamation, rarely_lie, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, rarely_lie, var.equal = TRUE))

#Never vs. rarely, selfish truth
t.test(Moral_composite3 ~ proclamation, sometimes_truth, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, sometimes_truth, var.equal = TRUE))

#Never vs. rarely, prosocial lie
t.test(Moral_composite3 ~ proclamation, sometimes_lie, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, sometimes_lie, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
mor_model = aov_ez('ID', 'Moral_composite3', s3,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(mor_model)
means <- emmeans(mor_model, ~ proclamation|behavior)
print(means)
post1 <- emmeans(mor_model, ~ proclamation|behavior)
pairs(post1)
post2 <- emmeans(mor_model, ~ proclamation)
pairs(post2) 


```

# Commitment to Honesty  Model

```{r}
#ANOVA
honesty_3.afex <-aov_car(Honest_composite3 ~ proclamation*behavior + Error(ID), data=s3)
summary(honesty_3.afex)
anova_apa(honesty_3.afex)
```

# Commitment to Honesty Descriptives

```{r}
#Cells
tapply(s3$Honest_composite3, list(s3$proclamation, s3$behavior), mean)
tapply(s3$Honest_composite3, list(s3$proclamation, s3$behavior), sd)
tapply(s3$Honest_composite3, list(s3$proclamation, s3$behavior), length)

#Across Proclamation
tapply(s3$Honest_composite3, s3$proclamation, mean)
tapply(s3$Honest_composite3, s3$proclamation, sd)
tapply(s3$Honest_composite3, s3$proclamation, length)

#Across Behavior
tapply(s3$Honest_composite3, s3$behavior, mean)
tapply(s3$Honest_composite3, s3$behavior, sd)
tapply(s3$Honest_composite3, s3$behavior, length)

#Overall
mean(s3$Honest_composite3)
sd(s3$Honest_composite3)
length(s3$Honest_composite3)


```

# Commitment to Honesty Simple Effects - T-tests

Note: For these tests, use subsetted data from Hypocrisy simple effects test (previous code chunk).

```{r}
#Main effect 
#Never vs. rarely only
t.test(Honest_composite3 ~ proclamation, sometimes_exclude, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, sometimes_exclude, var.equal = TRUE))

#Never vs.sometimes  only
t.test(Honest_composite3 ~ proclamation, rarely_exclude, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, rarely_exclude, var.equal = TRUE))

#Rarely vs. sometimes  only
t.test(Honest_composite3 ~ proclamation, never_exclude, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, never_exclude, var.equal = TRUE))

#Proclamation within levels of behavior, subsetted data

#Selfish truth: sometimes vs. rarely 
t.test(Honest_composite3 ~ proclamation, never_truth, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, never_truth, var.equal = TRUE))

#Prosocial lie: sometimes vs. rarely 
t.test(Honest_composite3 ~ proclamation, never_lie, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, never_lie, var.equal = TRUE))

#Selfish truth: never vs. sometimes
t.test(Honest_composite3~ proclamation, rarely_truth, var.equal = TRUE)
t_apa(t.test(Honest_composite3~ proclamation, rarely_truth, var.equal = TRUE))

#Prosocial lie: never vs. sometimes
t.test(Honest_composite3 ~ proclamation, rarely_lie, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, rarely_lie, var.equal = TRUE))

#Selfish truth: never vs. rarely
t.test(Honest_composite3 ~ proclamation, sometimes_truth, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, sometimes_truth, var.equal = TRUE))

#Prosocial lie: never vs. rarely
t.test(Honest_composite3 ~ proclamation, sometimes_lie, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, sometimes_lie, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
hon_model = aov_ez('ID', 'Honest_composite3', s3,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(hon_model)
means <- emmeans(hon_model, ~ proclamation|behavior)
print(means)
post1 <- emmeans(hon_model, ~ proclamation|behavior)
pairs(post1)  
post2 <- emmeans(hon_model, ~ proclamation)
pairs(post2)  
```

# Behavior Model

"rv" is trust in the RELY-or-VERIFY game. 1 = RELY, 0 = VERIFY.

```{r}
#Reported Model
rv.glm <- glm(rv_f ~ sometimes + rarely + behavlie + 
                sometimes*behavlie + rarely*behavlie,
              data=s3, family = binomial(link = "logit"))
summary(rv.glm)

# Confirm that the model looks the same with dummy-coded variables as factors
#Factorize 0,1 integers (dummy-coded variables)
s3$sometimes_f <- as.factor(s3$sometimes)
s3$rarely_f <- as.factor(s3$rarely)
s3$behavlie_f  <- as.factor(s3$behavlie)

#re-run model - consistent
rv_test.glm <- glm(rv_f ~ sometimes_f + rarely_f + behavlie_f + 
                sometimes_f*behavlie_f + rarely_f*behavlie_f,
              data=s3, family = binomial(link = "logit"))
summary(rv_test.glm) #confirmed

#Exploratory
rv.glm2 <- glm(rv_f ~ never + rarely + behavlie + 
                never*behavlie + rarely*behavlie,
              data=s3, family = binomial(link = "logit"))
summary(rv.glm2)

#factorize never
s3$never_f <- as.factor(s3$never)

#re-run model
rv_test.glm2 <- glm(rv_f ~ never_f + rarely_f + behavlie_f + 
                never_f*behavlie_f + rarely_f*behavlie_f,
              data=s3, family = binomial(link = "logit"))
summary(rv_test.glm2)

#Frequencies - proclamation
table(s3$proclamation, s3$rv_f) #1 = RELY, 0 = VERIFY

#never verify: 103/192, 54%
#rarely verify: 111/202, 55%
#sometimes  verify: 145 /204, 71%

#never rely: 89/192, 46%
#rarely rely: 91/202, 45%
#sometimes  rely: 59/204, 29%

#Frequencies proclamation and behavior by cell
table(s3$proclamation, s3$behavior, s3$rv_f)
table(s3$behavior, s3$rv_f) 


#Compare to equilibrium

#equilibrium 40% rely
#sometimes = 29% rely
prop.test(59, 204, p = .4, correct = FALSE)
```

#Attitudes Towards Honesty Measure

#Distribution of Responses

```{r}
table(s3$pref)
#94 "never" (5) / 598, 16%
#297 "rarely" (4) / 598, 50%
#195 "sometimes" (3) / 598, 33%
#10 "often" (2) -  1.7%
#2 "always" (1) - .3%

```


#Center honesty preferences for use in models

```{r}
#standardize - reported
s3 <- mutate(s3, pref.center = scale(s3$pref))

#mean center - for comparison
s3 <- mutate(s3, pref.center.2 = scale(s3$pref, scale = FALSE))

```

# SI Appendix 3 - Regressions

```{r}
#Preferences Regression - Hypocrisy
#Scaled by mean and SD
hypocrisy.lm <- lm(Hypocrisy_composite3 ~ sometimes*pref.center, data= s3)
summary(hypocrisy.lm)

#Mean centered
hypocrisy.lm2 <- lm(Hypocrisy_composite3 ~ sometimes*pref.center.2, data= s3)
summary(hypocrisy.lm2)

#Look at mean hypocrisy ratings by proclamation and preferences 
tapply(s3$Hypocrisy_composite3, list(s3$proclamation, s3$pref), mean)
tapply(s3$Hypocrisy_composite3, list(s3$proclamation, s3$pref), sd)
tapply(s3$Hypocrisy_composite3, list(s3$sometimes, s3$pref), mean)
tapply(s3$Hypocrisy_composite3, list(s3$sometimes, s3$pref), sd)
tapply(s3$Hypocrisy_composite3, s3$sometimes, mean)
tapply(s3$Hypocrisy_composite3, s3$sometimes, sd)

#Preferences Regression - Morality
#Scaled by mean and SD
moral.lm <- lm(Moral_composite3 ~ sometimes*pref.center, data= s3)
summary(moral.lm)

#Mean centered
moral.lm2 <- lm(Moral_composite3 ~ sometimes*pref.center.2, data= s3)
summary(moral.lm2)

#Look at mean morality ratings by proclamation and preferences 
tapply(s3$Moral_composite3, list(s3$proclamation, s3$pref), mean)
tapply(s3$Moral_composite3, list(s3$proclamation, s3$pref), sd)
tapply(s3$Moral_composite3, list(s3$proclamation, s3$pref), length)
tapply(s3$Moral_composite3, list(s3$sometimes, s3$pref), mean)
tapply(s3$Moral_composite3, s3$proclamation, mean)
tapply(s3$Moral_composite3, s3$rarely, mean)
tapply(s3$Moral_composite3, s3$rarely, sd)
tapply(s3$Moral_composite3, s3$sometimes, mean)
tapply(s3$Moral_composite3, s3$sometimes,sd)

#Preferences Regression - Commitment to Honesty
#Scaled by mean and SD
honest.lm <- lm(Honest_composite3 ~  sometimes*pref.center, data= s3)
summary(honest.lm)

#Mean centered
honest.lm2 <- lm(Honest_composite3 ~  sometimes*pref.center.2, data= s3)
summary(honest.lm2)

#Look at mean commitment to honesty ratings by proclamation and preferences 
tapply(s3$Honest_composite3, list(s3$proclamation, s3$pref), mean)
tapply(s3$Honest_composite3, list(s3$proclamation, s3$pref), sd)
tapply(s3$Honest_composite3, list(s3$sometimes, s3$pref), mean)
tapply(s3$Honest_composite3, s3$proclamation, mean)
tapply(s3$Honest_composite3, s3$pref, mean)
tapply(s3$Honest_composite3, s3$rarely, mean)
tapply(s3$Honest_composite3, s3$sometimes, mean)
tapply(s3$Honest_composite3, s3$sometimes, sd)

#Logistic Regression (trust) with own attitudes towards honesty
rv3.glm <- glm(rv_f ~ sometimes*pref.center,
              data=s3, family = binomial(link = "logit"))
summary(rv3.glm)

#Just main effect model
rv4.glm <- glm(rv_f ~ sometimes + pref.center,
              data=s3, family = binomial(link = "logit"))
summary(rv4.glm)

#Frequencies
table(s3$rv_f, s3$pref, s3$sometimes)
#0 = verify, 1 = rely
table(s3$rv_f, s3$pref, s3$proclamation)
table(s3$rv_f, s3$pref)
#note that separate tables 0 = never/rarely , 1 = sometimes; 
#within tables, 0 = verify, 1 = rely
#total per cell
table(s3$pref)

#Percentages RELY on never
#always 0/2 0%
#often 3/10 30%
#sometimes 22/195 11%
#rarely 44/297 15%
#never 20/94 21%

#Percentages RELY on rarely
#always 0/2 0%
#often 0/10 0%
#sometimes 23/195 12%
#rarely 55/297 19%
#never 13/94 14%

#Percentages RELY on never/rarely
#always 0/2, 0%
#often, 3/10 30%
#sometimes, 45/195 23%
#rarely, 99/297 33%
#never, 33/94

#Percentages RELY on sometimes
#always 0/2, 0%
#often, 1/10 10%
#sometimes, 28/195 14%
#rarely, 26/297 9%
#never, 4/94 4%

```

# Attitudes as a Covariate - pre-registered

```{r}
#Preferences Covariate - Hypocrisy
hypocrisy_pref.center.afex <-aov_car(Hypocrisy_composite3 ~ proclamation*behavior + pref.center + Error(ID), data= s3, factorize = FALSE, anova_table = list(es = "pes"))
summary(hypocrisy_pref.center.afex)

#Preferences Covariate - Moral
moral_pref2.afex <- aov_car(Moral_composite3 ~ proclamation*behavior + pref.center + Error(ID), data= s3, factorize = FALSE, anova_table = list(es = "pes"))
summary(moral_pref2.afex)

#Preferences Covariate - Commitment to honesty
honest.pref.center.afex <-aov_car(Honest_composite3 ~ proclamation*behavior + pref.center + Error(ID), data= s3, factorize = FALSE, anova_table = list(es = "pes"))
summary(honest.pref.center.afex)

```

#Notes

The moderated mediation models on moral character and trust behavior were conducted in SPSS. The syntax is copied below for use within SPSS.

# Syntax

Study 3 Trust: First, Open "HypocrisyStudy3_cleaned.xlsx" within SPSS. This excel file is available in this R project and on the OSF page for this project. Then run the code below.

*1. Recreate composite variables*
COMPUTE Hypocrisy_C=MEAN(Hypocrisy_1,Hypocrisy_2,Hypocrisy_3,Hypocrisy_4,Hypocrisy_5).
EXECUTE.

COMPUTE Honesty_C=MEAN(Honest_frequency,Honest_likely,Honest_extreme,Honest_committment).
EXECUTE.

*2. Run mediation analysis to get indirect effects. - use point and click within Process Macro*

*Run Hayes’ (2017) PROCESS Macro for SPSS, Model 7, 10,000 bootstraps*
IV = sometimes
M1 = Honesty_C
M2 = Hypocrisy_C
Y = rv
W = behavlie

*3. Run regressions to get X-->M and M-->Y pathways for each level of moderator.*

SORT CASES  BY behavlie.
SPLIT FILE LAYERED BY behavlie.

*Test M-->Y pathways*

LOGISTIC REGRESSION VARIABLES rv
  /METHOD=ENTER Hypocrisy_C Honesty_C sometimes 
  /CRITERIA=PIN(.05) POUT(.10) ITERATE(20) CUT(.5).


*Test X-->M1 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Honesty_C
  /METHOD=ENTER sometimes.
  
  *Test X-->M2 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Hypocrisy_C
  /METHOD=ENTER sometimes.


Study 3 Morality: Use the same data file in SPSS.

*1. Recreate composite variables*

COMPUTE Hypocrisy_C=MEAN(Hypocrisy_1,Hypocrisy_2,Hypocrisy_3,Hypocrisy_4,Hypocrisy_5).
EXECUTE.

COMPUTE Honesty_C=MEAN(Honest_frequency,Honest_likely,Honest_extreme,Honest_committment).
EXECUTE.

COMPUTE Moral_C=MEAN(Moral_1, Moral_2, Moral_3).
EXECUTE.

*2. Run mediation analysis to get indirect effects. - use point and click within Process Macro*

*Run Hayes’ (2016) PROCESS Macro for SPSS, Model 7, 10,000 bootstraps*
IV = sometimes
M1 = Hypocrisy_C
M2 = Honesty_C
Y = Moral_C
W = behavlie

*3. Run regressions to get X-->M and M-->Y pathways for each level of moderator.*

SORT CASES  BY behavlie.
SPLIT FILE LAYERED BY behavlie.

*Test M-->Y pathways*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Moral_C
  /METHOD=ENTER sometimes Hypocrisy_C, Honesty_C.
  
  *Test X-->M1 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Honesty_C
  /METHOD=ENTER sometimes.

*Test X-->M2 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Hypocrisy_C
  /METHOD=ENTER sometimes.

