---
title: "Supplemental Study 5 (Study 10)"
author: "Elizabeth Huppert"
date: "8/9/2021"
output: html_document
---
# Set-up

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-psych
-reshape2
-apa
-dplyr
-emmeans

# Load Packages and Data

```{r, include = FALSE}
library(here)
library(tidyverse)
library(psych)
library(reshape2)
library(afex)
library(apa)
library(dplyr)
library(emmeans)

#read in data

s11 <- read.csv(here("HypocrisyStudySI_5.csv"))

```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.

Key Variable Names (also see codebook for more information):

1. Condition:
Assignment to absolute vs. flexible honesty stance

2. Country
1 = India, 2 = USA (where participants were recruited from on MTurk)

3. advice
Weight of advice measure derived from the Advice Game (participants made an initial estimate about the amount of money in a jar of coins, were sent advice on the amount of money in a jar of coins, and had the chance to revise this guess and submit a final estimate. See codebook or SOM for more details on the calculation for this measure using the initial estimate, advised amount, and final estimate).


# Re-code condition for ease of interpretation - "proc"

```{r}
s11$proc[s11$condition=="1"] <- "absolute"
s11$proc[s11$condition=="2"] <- "flexible"
```


# Factorize Country and Subject (id)

Note: Country 1 is India and Country 2 is the US.

```{r}
s11$Country <- as.factor(s11$Country)
s11$id<- as.factor(s11$id)
```

# Composite variables

Items with high agreement were combined as per our pre-registration.

```{r}
#Time One
#Hypocrisy
#hypocrisy_1 - this person is a hypocrite
s11$h1[s11$hypocrite=="Strongly disagree"] <- "1"
s11$h1[s11$hypocrite=="Disagree"] <- "2"
s11$h1[s11$hypocrite=="Somewhat disagree"] <- "3"
s11$h1[s11$hypocrite=="Neither agree nor disagree"] <- "4"
s11$h1[s11$hypocrite=="Somewhat agree"] <- "5"
s11$h1[s11$hypocrite=="Agree"] <- "6"
s11$h1[s11$hypocrite=="Strongly agree"] <- "7"
s11$h1 <- as.numeric(s11$h1)
#inauthentic
s11$h2[s11$inauthentic=="Strongly disagree"] <- "1"
s11$h2[s11$inauthentic=="Disagree"] <- "2"
s11$h2[s11$inauthentic=="Somewhat disagree"] <- "3"
s11$h2[s11$inauthentic=="Neither agree nor disagree"] <- "4"
s11$h2[s11$inauthentic=="Somewhat agree"] <- "5"
s11$h2[s11$inauthentic=="Agree"] <- "6"
s11$h2[s11$inauthentic=="Strongly agree"] <- "7"
s11$h2 <- as.numeric(s11$h2)
#disingenuous
s11$h3[s11$disingenuous=="Strongly disagree"] <- "1"
s11$h3[s11$disingenuous=="Disagree"] <- "2"
s11$h3[s11$disingenuous=="Somewhat disagree"] <- "3"
s11$h3[s11$disingenuous=="Neither agree nor disagree"] <- "4"
s11$h3[s11$disingenuous=="Somewhat agree"] <- "5"
s11$h3[s11$disingenuous=="Agree"] <- "6"
s11$h3[s11$disingenuous=="Strongly agree"] <- "7"
s11$h3 <- as.numeric(s11$h3)
#cronbachs alpha for 3  hypocrisy items - time one
hypoSI5_df <- data.frame(s11$h1, s11$h2, s11$h3)
summary(hypoSI5_df)
describe(hypoSI5_df)
psych::alpha(hypoSI5_df) # raw = 0.95
#hypocrisy items over 0.6 so create a composite
s11 <- mutate(s11, 
                   SI5_hcomposite = 
                     ((s11$h1+s11$h2+s11$h3)/3))

#Time Two
#hypocrisy
#hypo_2 - this person is a hypocrite
s11$h1.2[s11$hypo_2 =="Strongly disagree"] <- "1"
s11$h1.2[s11$hypo_2 =="Disagree"] <- "2"
s11$h1.2[s11$hypo_2 =="Somewhat disagree"] <- "3"
s11$h1.2[s11$hypo_2 =="Neither agree nor disagree"] <- "4"
s11$h1.2[s11$hypo_2 =="Somewhat agree"] <- "5"
s11$h1.2[s11$hypo_2 =="Agree"] <- "6"
s11$h1.2[s11$hypo_2 =="Strongly agree"] <- "7"
s11$h1.2 <- as.numeric(s11$h1.2)
#inauth_2 
s11$h2.2[s11$inauth_2 =="Strongly disagree"] <- "1"
s11$h2.2[s11$inauth_2 =="Disagree"] <- "2"
s11$h2.2[s11$inauth_2 =="Somewhat disagree"] <- "3"
s11$h2.2[s11$inauth_2 =="Neither agree nor disagree"] <- "4"
s11$h2.2[s11$inauth_2 =="Somewhat agree"] <- "5"
s11$h2.2[s11$inauth_2 =="Agree"] <- "6"
s11$h2.2[s11$inauth_2 =="Strongly agree"] <- "7"
s11$h2.2 <- as.numeric(s11$h2.2)
#disingen_2
s11$h3.2[s11$disingen_2=="Strongly disagree"] <- "1"
s11$h3.2[s11$disingen_2=="Disagree"] <- "2"
s11$h3.2[s11$disingen_2=="Somewhat disagree"] <- "3"
s11$h3.2[s11$disingen_2=="Neither agree nor disagree"] <- "4"
s11$h3.2[s11$disingen_2=="Somewhat agree"] <- "5"
s11$h3.2[s11$disingen_2=="Agree"] <- "6"
s11$h3.2[s11$disingen_2=="Strongly agree"] <- "7"
s11$h3.2 <- as.numeric(s11$h3.2)
#cronbachs alpha for 3  hypocrisy items - time two
hypoSI5_df2 <- data.frame(s11$h1.2, s11$h2.2, s11$h3.2)
summary(hypoSI5_df2)
describe(hypoSI5_df2)
psych::alpha(hypoSI5_df2) # raw = 0.94
#hypocrisy items over 0.6 so create a composite
s11 <- mutate(s11, 
                   SI5_hcomposite2 = 
                     ((s11$h1.2 + s11$h2.2 + s11$h3.2)/3))

#Time One
#Commitment to honesty
#honest_freq, reverse code
s11$hf1[s11$lie_freq=="Not often at all"] <- "7"
s11$hf1[s11$lie_freq=="Not very often"] <- "6"
s11$hf1[s11$lie_freq=="Slightly often"] <- "5"
s11$hf1[s11$lie_freq=="Somewhat often"] <- "4"
s11$hf1[s11$lie_freq=="Moderately often"] <- "3"
s11$hf1[s11$lie_freq=="Very often"] <- "2"
s11$hf1[s11$lie_freq=="Extremely often"] <- "1"
s11$hf1 <- as.numeric(s11$hf1)
#honest_likely, reverse code
s11$hl1[s11$future_lie=="Not at all likely"] <- "7"
s11$hl1[s11$future_lie=="Not very likely"] <- "6"
s11$hl1[s11$future_lie=="Slightly likely"] <- "5"
s11$hl1[s11$future_lie=="Somewhat likely"] <- "4"
s11$hl1[s11$future_lie=="Moderately likely"] <- "3"
s11$hl1[s11$future_lie=="Very likely"] <- "2"
s11$hl1[s11$future_lie=="Extremely likely"] <- "1"
s11$hl1 <- as.numeric(s11$hl1)
#honest_extreme
s11$he1[s11$extreme_lie=="Not at all extreme"] <-  "1"
s11$he1[s11$extreme_lie=="Not very extreme"] <- "2"
s11$he1[s11$extreme_lie=="Slightly extreme"] <- "3"
s11$he1[s11$extreme_lie=="Somewhat extreme"] <- "4"
s11$he1[s11$extreme_lie=="Moderately extreme"] <- "5"
s11$he1[s11$extreme_lie=="Very extreme"] <- "6"
s11$he1[s11$extreme_lie=="The most extreme"] <- "7"
s11$he1 <- as.numeric(s11$he1)
#committment_honest_1
s11$ch1[s11$comm_h=="Not at all"] <- " 1"
s11$ch1[s11$comm_h=="Not very"] <- "2"
s11$ch1[s11$comm_h=="Slightly"] <- "3"
s11$ch1[s11$comm_h=="Somewhat"] <- "4"
s11$ch1[s11$comm_h=="Moderately"] <- "5"
s11$ch1[s11$comm_h=="Very"] <- "6"
s11$ch1[s11$comm_h=="Extremely"] <- "7"
s11$ch1 <- as.numeric(s11$ch1)
#look at different honesty items - 4
SI5_honesty_df <- data.frame(s11$hf1, s11$hl1, s11$he1, s11$ch1)
summary(SI5_honesty_df)
describe(SI5_honesty_df)
psych::alpha(SI5_honesty_df) # raw= 0.67
#over .6 so combine
s11 <- mutate(s11, 
                   SI_honest_composite = 
                     ((s11$hf1 + s11$hl1 + s11$he1 + s11$ch1)/4))

#Time two
#Commitment to honesty

#honest_freq, reverse code
s11$hf1.2[s11$lie_freq2=="Not often at all"] <- "7"
s11$hf1.2[s11$lie_freq2=="Not very often"] <- "6"
s11$hf1.2[s11$lie_freq2=="Slightly often"] <- "5"
s11$hf1.2[s11$lie_freq2=="Somewhat often"] <- "4"
s11$hf1.2[s11$lie_freq2=="Moderately often"] <- "3"
s11$hf1.2[s11$lie_freq2=="Very often"] <- "2"
s11$hf1.2[s11$lie_freq2=="Extremely often"] <- "1"
s11$hf1.2<- as.numeric(s11$hf1.2)
#honest_likely, reverse code
s11$hl1.2[s11$future_lie2=="Not at all likely"] <- "7"
s11$hl1.2[s11$future_lie2=="Not very likely"] <- "6"
s11$hl1.2[s11$future_lie2=="Slightly likely"] <- "5"
s11$hl1.2[s11$future_lie2=="Somewhat likely"] <- "4"
s11$hl1.2[s11$future_lie2=="Moderately likely"] <- "3"
s11$hl1.2[s11$future_lie2=="Very likely"] <- "2"
s11$hl1.2[s11$future_lie2=="Extremely likely"] <- "1"
s11$hl1.2 <- as.numeric(s11$hl1.2)
#honest_extreme
s11$he1.2[s11$extreme_lie2=="Not at all extreme"] <-  "1"
s11$he1.2[s11$extreme_lie2=="Not very extreme"] <- "2"
s11$he1.2[s11$extreme_lie2=="Slightly extreme"] <- "3"
s11$he1.2[s11$extreme_lie2=="Somewhat extreme"] <- "4"
s11$he1.2[s11$extreme_lie2=="Moderately extreme"] <- "5"
s11$he1.2[s11$extreme_lie2=="Very extreme"] <- "6"
s11$he1.2[s11$extreme_lie2=="The most extreme"] <- "7"
s11$he1.2 <- as.numeric(s11$he1.2)
#committment_honest_1
s11$ch1.2[s11$comm_h2=="Not at all"] <- " 1"
s11$ch1.2[s11$comm_h2=="Not very"] <- "2"
s11$ch1.2[s11$comm_h2=="Slightly"] <- "3"
s11$ch1.2[s11$comm_h2=="Somewhat"] <- "4"
s11$ch1.2[s11$comm_h2=="Moderately"] <- "5"
s11$ch1.2[s11$comm_h2=="Very"] <- "6"
s11$ch1.2[s11$comm_h2=="Extremely"] <- "7"
s11$ch1.2 <- as.numeric(s11$ch1.2)
#look at different honesty items - 4
SI5_honesty_df2 <- data.frame(s11$hf1.2, s11$hl1.2, s11$he1.2, s11$ch1.2)
summary(SI5_honesty_df2)
describe(SI5_honesty_df2)
psych::alpha(SI5_honesty_df2) # raw= 0.70
#over .6 so combine
s11 <- mutate(s11, 
                   SI_honest_composite2 = 
                     ((s11$hf1.2 + s11$hl1.2 + s11$he1.2 + s11$ch1.2)/4))
#Time One
#Moral
#mora
s11$m1[s11$moral =="Not at all"] <- "1"
s11$m1[s11$moral =="Not very"] <- "2"
s11$m1[s11$moral =="Slightly"] <- "3"
s11$m1[s11$moral =="Somewhat"] <- "4"
s11$m1[s11$moral =="Moderately"] <- "5"
s11$m1[s11$moral =="Very"] <- "6"
s11$m1[s11$moral =="Extremely"] <- "7"
s11$m1 <- as.numeric(s11$m1)
#ethical
s11$m2[s11$ethical=="Not at all"] <- "1"
s11$m2[s11$ethical=="Not very"] <- "2"
s11$m2[s11$ethical=="Slightly"] <- "3"
s11$m2[s11$ethical=="Somewhat"] <- "4"
s11$m2[s11$ethical=="Moderately"] <- "5"
s11$m2[s11$ethical=="Very"] <- "6"
s11$m2[s11$ethical=="Extremely"] <- "7"
s11$m2 <- as.numeric(s11$m2)
#trust
s11$m3[s11$trust =="Not at all"] <- "1"
s11$m3[s11$trust =="Not very"] <- "2"
s11$m3[s11$trust =="Slightly"] <- "3"
s11$m3[s11$trust =="Somewhat"] <- "4"
s11$m3[s11$trust =="Moderately"] <- "5"
s11$m3[s11$trust =="Very"] <- "6"
s11$m3[s11$trust =="Extremely"] <- "7"
s11$m3 <- as.numeric(s11$m3)
#moral composite
SI5_moral_df <- data.frame(s11$m1, s11$m2, s11$m3)
summary(SI5_moral_df)
describe(SI5_moral_df)
psych::alpha(SI5_moral_df) # raw = 0.93
s11 <- mutate(s11, 
                   SI_moral_composite = ((s11$m1+s11$m2+s11$m3)/3))

#Time Two
#moral
s11$m1.2[s11$moral_2=="Not at all"] <- "1"
s11$m1.2[s11$moral_2=="Not very"] <- "2"
s11$m1.2[s11$moral_2=="Slightly"] <- "3"
s11$m1.2[s11$moral_2=="Somewhat"] <- "4"
s11$m1.2[s11$moral_2=="Moderately"] <- "5"
s11$m1.2[s11$moral_2=="Very"] <- "6"
s11$m1.2[s11$moral_2=="Extremely"] <- "7"
s11$m1.2<- as.numeric(s11$m1.2)
#ethical
s11$m2.2[s11$ethical_2=="Not at all"] <- "1"
s11$m2.2[s11$ethical_2=="Not very"] <- "2"
s11$m2.2[s11$ethical_2=="Slightly"] <- "3"
s11$m2.2[s11$ethical_2=="Somewhat"] <- "4"
s11$m2.2[s11$ethical_2=="Moderately"] <- "5"
s11$m2.2[s11$ethical_2=="Very"] <- "6"
s11$m2.2[s11$ethical_2=="Extremely"] <- "7"
s11$m2.2 <- as.numeric(s11$m2.2)
#trust
s11$m3.2[s11$trust_2 =="Not at all"] <- "1"
s11$m3.2[s11$trust_2 =="Not very"] <- "2"
s11$m3.2[s11$trust_2 =="Slightly"] <- "3"
s11$m3.2[s11$trust_2 =="Somewhat"] <- "4"
s11$m3.2[s11$trust_2 =="Moderately"] <- "5"
s11$m3.2[s11$trust_2 =="Very"] <- "6"
s11$m3.2[s11$trust_2=="Extremely"] <- "7"
s11$m3.2 <- as.numeric(s11$m3.2)
#moral composite
SI5_moral_df2 <- data.frame(s11$m1.2, s11$m2.2, s11$m3.2)
summary(SI5_moral_df2)
describe(SI5_moral_df2)
psych::alpha(SI5_moral_df2) # raw = 0.97
s11 <- mutate(s11, 
                   SI_moral_composite2 = ((s11$m1.2 + s11$m2.2 + s11$m3.2 )/3))

```

Evaluation variables:

Timepoint 1:

SI5_hcomposite = hypocrisy composite of 3 items at timepoint 1 
SI_honest_composite = commitment to honesty composite of 4 items at timepoint 1
SI_moral_composite = morality composite of 3 items at timepoint 1

Timepoint 2 (same 1-7 Likert-type scales):

SI5_hcomposite2 = hypocrisy composite of 3 items at timepoint 2
SI_honest_composite2 = commitment to honesty composite of 4 items at timepoint 2
SI_moral_composite2 = morality composite of 3 items at timepoint 2


# Analysis

# Correlation of Moral Judgments Across Time

```{r}
#Absolute time one vs. time two
absolute_s11 <- s11 %>%
  filter(proc ==  "absolute") #n = 100

#Just using US 
absolute_S11_us <- absolute_s11 %>%
  filter(Country == "2") #46

#Flexible time one vs. time two
flexible_s11 <- s11 %>%
  filter(proc ==  "flexible") #n = 96

#Just using US 
flexible_s11_us <- flexible_s11 %>%
  filter(Country == "2") #54

#Use just the absolute dataset with us only
cor.test(absolute_S11_us$SI_moral_composite, 
         absolute_S11_us$SI_moral_composite2)
#r = 0.06927773  

#Use just the flex dataset with us only
cor.test(flexible_s11_us$SI_moral_composite, 
         flexible_s11_us$SI_moral_composite2)
#r = 0.4563668 
```

# Correlation of Moral Judgments Across Time

```{r}
#Absolute time one vs. time two
#Use just the absolute dataset
length(absolute_s5$ID) #306
cor.test(absolute_s5$Moral.1_composite5, absolute_s5$Moral.2_composite5 )
#r = 0.5005439 

length(flexible_s5$ID) #294
cor.test(flexible_s5$Moral.1_composite5, flexible_s5$Moral.2_composite5 )
#r = 0.627813
```

# Hypocrisy Model

```{r}
#Dataframe for Hypocrisy
hypo5_SI_df <-melt(s11, 
                    id.vars=c("condition", "id", "proc", "Country"),
                    #measure command is for the DV
                    measure.vars=c("SI5_hcomposite","SI5_hcomposite2"),
                    variable.name="h5.time",
                    value.name="h5value"
)


#ANOVA
hSI5.afex <- aov_car(
  h5value ~ proc*h5.time + Error(id/h5.time),
  data = hypo5_SI_df)
summary(hSI5.afex)
anova_apa(hSI5.afex)
```

# Hypocrisy Descriptives 

```{r}
#Cells: Proclamation and Time
tapply(hypo5_SI_df$h5value, list(hypo5_SI_df$proc, hypo5_SI_df$h5.time),
       FUN = length)

tapply(hypo5_SI_df$h5value, list(hypo5_SI_df$proc, hypo5_SI_df$h5.time),
       FUN = mean)

tapply(hypo5_SI_df$h5value, list(hypo5_SI_df$proc, hypo5_SI_df$h5.time),
       FUN = sd)

#Across Proclamation
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc, FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc,FUN = length)

#Across Time
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = length)

#Overall
mean(hypo5_SI_df$h5value)
sd(hypo5_SI_df$h5value)
length(hypo5_SI_df$h5value)
```


# Country and Hypocrisy (analysis, descriptives)

```{r}
#ANOVA
hSI5_c.afex <- aov_car(
  h5value ~ proc*h5.time*Country + Error(id/h5.time),
  data = hypo5_SI_df)
summary(hSI5_c.afex )
anova_apa(hSI5_c.afex )

#Cells
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = mean)

tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = sd)

tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = length)

#Across Country and Time 
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = mean)
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = sd)
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = length)

#Across Proclamation Time 
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$h5.time), 
       FUN = mean)
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$h5.time), 
       FUN = sd)
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$h5.time), 
       FUN = length)

#Across Country
tapply(hypo5_SI_df$h5value, hypo5_SI_df$Country,FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$Country,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$Country,FUN = length)

#Across Time
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = length)

#Across Proclamation
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc,FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc,FUN = length)

```

# Morality Model

```{r}
moral5_SI_df <-melt(s11, 
                     id.vars=c("condition", "id", "proc", "Country"),
                     #measure command is for the DV
                     measure.vars=c("SI_moral_composite", "SI_moral_composite2"),
                     variable.name="m5.time",
                     value.name="m5value"
)

#ANOVA
m_SI5.afex <- aov_car(
  m5value ~ proc*m5.time + Error(id/m5.time),
  data = moral5_SI_df)
summary(m_SI5.afex)
anova_apa(m_SI5.afex)
```

# Morality Descriptives 

```{r}
#Cells: Proclamation and Time
tapply(moral5_SI_df$m5value , list(moral5_SI_df$proc, moral5_SI_df$m5.time),
       FUN = length)

tapply(moral5_SI_df$m5value , list(moral5_SI_df$proc, moral5_SI_df$m5.time),
       FUN = mean)

tapply(moral5_SI_df$m5value , list(moral5_SI_df$proc, moral5_SI_df$m5.time),
       FUN = sd)


#Across Proclamation
tapply(moral5_SI_df$m5value, moral5_SI_df$proc, FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$proc,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$proc,FUN = length)

#Across Time
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = length)

#Overall
mean(moral5_SI_df$m5value)
sd(moral5_SI_df$m5value)
length(moral5_SI_df$m5value)
```


# Country and Morality (analysis, descriptives)

```{r}
#ANOVA
m_SI5_c.afex <- aov_car(
  m5value ~ proc*m5.time*Country + Error(id/m5.time),
  data = moral5_SI_df)
summary(m_SI5_c.afex)
anova_apa(m_SI5_c.afex)

#Cells
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = mean)

tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = sd)

tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = length)

#Across Country and Time 
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = mean)
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = sd)
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = length)

#Across Proclamation and Time 
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$m5.time), 
       FUN = mean)
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$m5.time), 
       FUN = sd)
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$m5.time), 
       FUN = length)

#Country
tapply(moral5_SI_df$m5value, moral5_SI_df$Country,FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$Country,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$Country,FUN = length)

#Proclamation
tapply(moral5_SI_df$m5value, moral5_SI_df$proc,FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$proc,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$proc,FUN = length)

#Time
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = length)

```

# Morality with Country T-tests at time two

```{r}
#T-test at time two absolute vs. flexible by country
#US
US_only <- s11 %>%
  filter(Country == "2")
India_only <- s11 %>%
  filter(Country == "1")


t.test(SI_moral_composite2 ~ proc, US_only, var.equal = TRUE)
t_apa(t.test(SI_moral_composite2 ~ proc, US_only, var.equal = TRUE))

t.test(SI_moral_composite2 ~ proc, India_only, var.equal = TRUE)
t_apa(t.test(SI_moral_composite2 ~ proc, India_only, var.equal = TRUE))

```


# Commitment to Honesty Model

```{r}
honest5_SI_df <-melt(s11, 
                   id.vars=c("condition", "id", "proc", "Country"),
                   #measure command is for the DV
                   measure.vars=c("SI_honest_composite","SI_honest_composite2"),
                   variable.name="honest5.time",
                   value.name="honest5value"
)

#ANOVA
hon_SI5.afex <- aov_car(
  honest5value ~ proc*honest5.time + Error(id/honest5.time),
  data = honest5_SI_df)
summary(hon_SI5.afex)
anova_apa(hon_SI5.afex)
```

# Commitment to Honesty Descriptives 

```{r}
#Cells: Proclamation and Time
tapply(honest5_SI_df$honest5value , list(honest5_SI_df$proc, honest5_SI_df$honest5.time),
       FUN = length)

tapply(honest5_SI_df$honest5value , list(honest5_SI_df$proc, honest5_SI_df$honest5.time),
       FUN = mean)

tapply(honest5_SI_df$honest5value , list(honest5_SI_df$proc, honest5_SI_df$honest5.time),
       FUN = sd)


#Across Proclamation
tapply(honest5_SI_df$honest5value, honest5_SI_df$proc, FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$proc,FUN = sd)
tapply(honest5_SI_df$honest5value, hhonest5_SI_df$proc,FUN = length)

#Across Time
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = sd)
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = length)

#Overall
mean(honest5_SI_df$honest5value)
sd(honest5_SI_df$honest5value)
length(honest5_SI_df$honest5value)
```

# Commitment to Honesty t-test without Country 
(Just looking at Proclamation).

```{r}
#T-test at time two
t.test(SI_honest_composite2 ~ proc, s11, var.equal = TRUE)
t_apa(t.test(SI_honest_composite2~ proc, s11, var.equal = TRUE))
```

# Country and Commitment to Honesty (analysis, descriptives)

```{r}
#ANOVA
hon_SI5_c.afex <- aov_car(
  honest5value ~ proc*honest5.time*Country + Error(id/honest5.time),
  data = honest5_SI_df)
summary(hon_SI5_c.afex)
anova_apa(hon_SI5_c.afex)

#Cells
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$proc, honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = mean)

tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$proc, honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = sd)

tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$proc, honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = length)

#Across Country and Time 
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = mean)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = sd)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = length)

#Across Country and Proclamation 
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$proc), 
       FUN = mean)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$proc), 
       FUN = sd)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$proc), 
       FUN = length)

#Across Time and Proclamation 
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$honest5.time, honest5_SI_df$proc), 
       FUN = mean)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$honest5.time, honest5_SI_df$proc), 
       FUN = sd)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$honest5.time, honest5_SI_df$proc), 
       FUN = length)

#Across Country
tapply(honest5_SI_df$honest5value, honest5_SI_df$Country,FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$Country,FUN = sd)
tapply(honest5_SI_df$honest5value, honest5_SI_df$Country,FUN = length)

#Across Proclamation
tapply(honest5_SI_df$honest5value, honest5_SI_df$proc,FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$proc,FUN = sd)
tapply(honest5_SI_df$honest5value, honest5_SI_df$proc,FUN = length)

#Across Time
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = sd)
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = length)
```

# Committment to Honesty with Country t-tests 

```{r}
t.test(SI_honest_composite2 ~ proc, US_only, var.equal = TRUE)
t_apa(t.test(SI_honest_composite2 ~ proc, US_only, var.equal = TRUE))

t.test(SI_honest_composite2 ~ proc, India_only, var.equal = TRUE)
t_apa(t.test(SI_honest_composite2 ~ proc, India_only, var.equal = TRUE))
```

# Advice Game

Note: Subject 113 had the same initial estimate of the amount of money in the jar of coins as the Advisor advised (later in the game), so we excluded this subject from analysis. See SOM for further details.

```{r}
#Remove subject 113 from this analysis since same guess as advice at T1
trust_df <- s11 %>%
  subset(s11$id != "113")


#ANOVA on advice
trust.afex <- aov_car(
  advice ~ proc + Error(id),
  data = trust_df)
summary(trust.afex)
anova_apa(trust.afex)



#Across Proclamation
tapply(trust_df$advice, trust_df$proc, FUN = mean)
tapply(trust_df$advice, trust_df$proc,FUN = sd)
tapply(trust_df$advice, trust_df$proc,FUN = length)


#Overall
mean(trust_df$advice)
sdtrust_df$advice)
length(trust_df$advice)
```

# Country and Advice Game

```{r}
#ANOVA
trust2.afex <- aov_car(
  advice ~ proc*Country + Error(id),
  data = trust_df)
summary(trust2.afex)
anova_apa(trust2.afex)

#Cells
tapply(trust_df$advice, list(trust_df$proc, trust_df$Country),FUN = mean)
tapply(trust_df$advice, list(trust_df$proc, trust_df$Country),FUN = sd)
tapply(trust_df$advice, list(trust_df$proc, trust_df$Country),FUN = length)

#Across Country
tapply(trust_df$advice, trust_df$Country,FUN = mean)
tapply(trust_df$advice, trust_df$Country,FUN = sd)
tapply(trust_df$advice, trust_df$Country,FUN = length)

#Across Proclamation
tapply(trust_df$advice, trust_df$proc,FUN = mean)
tapply(trust_df$advice, trust_df$proc,FUN = sd)
tapply(trust_df$advice, trust_df$proc,FUN = length)

```

