---
title: "Study1"
author: "Elizabeth Huppert"
date: "1/12/2021"
output: pdf_document
---


#Set-up and Read in Data

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-apa
-psych
-dplyr
-emmeans


```{r setup, include=FALSE}

library(here)
library(tidyverse)
library(afex)
library(apa)
library(psych)
library(dplyr)
library(emmeans)

#read in data

s1 <- read.csv(here("HypocrisyStudy1_cleaned.csv")) #1021
```


Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


# Models

Key variable names (also see codebook for more information):

1. Proclamation:
Assignment to absolute vs. flexible honesty stance

2. Perspective:
Perspective of statement as first-, second-, or third-person
(i.e. "It is never okay to lie" vs. "I would never lie" vs. "You should never lie")

3. Frame:
Truth or lie Frame (i.e. "It is always imperative to tell the truth" vs. "I would always tell the truth" vs. "You should always tell the truth"")

4. Voting:
Likelihood of voting for Matthew Johnson (1 -7)

# Record ordering of Proclamation for ease of interpretation

Coded to: Absolute = 1, Flexible = 0

```{r}
s1$Proclamation <- factor(s1$Proclamation, levels = c("ambiguous", "absolute"), labels = c("flexible", "absolute"))

```

# Composite Evaluation Variables 

Items with high agreement were combined as per our pre-registration.

```{r}
#Hypocrisy
hypocrisy1_check.df <- data.frame(s1$Hypocrisy_1, s1$Hypocrisy_2, s1$Hypocrisy_3, s1$Hypocrisy_4, s1$Hypocrisy_5)
summary(hypocrisy1_check.df)
describe(hypocrisy1_check.df)
psych::alpha(hypocrisy1_check.df) #alpha = 0.88
s1 <-  mutate(s1, 
              Hypocrisy_composite = ((s1$Hypocrisy_1 + s1$Hypocrisy_2 + s1$Hypocrisy_3 + s1$Hypocrisy_4 + s1$Hypocrisy_5)/5))

#Morality
moral1_check.df <- data.frame(s1$Moral_1, s1$Moral_2, s1$Moral_3)
summary(moral1_check.df)
describe(moral1_check.df)
psych::alpha(moral1_check.df) #alpha = 0.94
s1 <- mutate(s1, 
             Moral_composite = ((s1$Moral_1 + s1$Moral_2 + s1$Moral_3)/3))


#Future Honesty
honest1_check.df <- data.frame(s1$Honest_frequency, s1$Honest_likelihood, s1$Honest_extreme, s1$Honest_committment)
summary(honest1_check.df)
describe(honest1_check.df)
psych::alpha(honest1_check.df) #alpha = 0.75
s1<- mutate(s1, 
            Honest_composite = ((s1$Honest_frequency + s1$Honest_likelihood + s1$Honest_extreme + s1$Honest_committment)/4))

```

Evaluation variables:

Hypocrisy_composite = hypocrisy composite of 5 items (Ratings: 1-7)
Moral_composite = morality composite of 3 items (Ratings: 1-7)
Honest_composite = honesty thresholds composite of 4 items (Ratings: 1-7)

# Hypocrisy Model

```{r}
#ANOVA
hypocrisy_1.afex <-aov_car(Hypocrisy_composite ~ Proclamation*Perspective*Frame + Error(ID), data=s1)
summary(hypocrisy_1.afex) 
anova_apa(hypocrisy_1.afex)
```


# Hypocrisy Descriptives

```{r}
#Cells
tapply(s1$Hypocrisy_composite, list(s1$Proclamation, s1$Perspective, s1$Frame), mean)
tapply(s1$Hypocrisy_composite, list(s1$Proclamation, s1$Perspective, s1$Frame), sd)
tapply(s1$Hypocrisy_composite, list(s1$Proclamation, s1$Perspective, s1$Frame), length)

#Across Proclamation*Frame
tapply(s1$Hypocrisy_composite, list(s1$Proclamation, s1$Frame), mean)
tapply(s1$Hypocrisy_composite, list(s1$Proclamation, s1$Frame), sd)
tapply(s1$Hypocrisy_composite, list(s1$Proclamation, s1$Frame), length)

#Across Proclamation*Perspective
tapply(s1$Hypocrisy_composite, list(s1$Proclamation, s1$Perspective), mean)
tapply(s1$Hypocrisy_composite, list(s1$Proclamation, s1$Perspective), sd)
tapply(s1$Hypocrisy_composite, list(s1$Proclamation, s1$Perspective), length)

#Across Frame*Perspective
tapply(s1$Hypocrisy_composite, list(s1$Perspective, s1$Frame), mean)
tapply(s1$Hypocrisy_composite, list(s1$Perspective, s1$Frame), sd)
tapply(s1$Hypocrisy_composite, list(s1$Perspective, s1$Frame), length)

#Across Proclamation
tapply(s1$Hypocrisy_composite, s1$Proclamation, mean)
tapply(s1$Hypocrisy_composite, s1$Proclamation, sd)
tapply(s1$Hypocrisy_composite, s1$Proclamation, length)

#Across Frame
tapply(s1$Hypocrisy_composite, s1$Frame, mean)
tapply(s1$Hypocrisy_composite, s1$Frame, sd)
tapply(s1$Hypocrisy_composite, s1$Frame, length)

#Across Perspective
tapply(s1$Hypocrisy_composite, s1$Perspective, mean)
tapply(s1$Hypocrisy_composite, s1$Perspective, sd)
tapply(s1$Hypocrisy_composite, s1$Perspective, length)

#Overall
mean(s1$Hypocrisy_composite)
sd(s1$Hypocrisy_composite)
length(s1$Hypocrisy_composite)
```

# Morality Model

```{r}
#ANOVA
moral_1.afex <-aov_car(Moral_composite ~ Proclamation*Perspective*Frame + Error(ID), data=s1)
summary(moral_1.afex) 
anova_apa(moral_1.afex)

#Abs vs. Flex morality focal - need cohen's D
#abs mean = 2.87, sd = 1.22, 528 
#flex mean =  2.32, sd = 1.03, 493
#pooled SD = sqrt(((1.22^2) + (1.03^2))/2)
sqrt((((1.22^2) + (1.03^2))/2)) #1.129

#cohens = (mean - mean)/SD pooeld
(2.87-2.32)/1.129 #0.487

d <- cohens_d(t_test(Moral_composite ~ Proclamation, s1))
d #Cohen's d abs. vs. flex. on morality (abs value)  = 0.487

```

# Morality Descriptives

```{r}
#Cells
tapply(s1$Moral_composite, list(s1$Proclamation, s1$Perspective, s1$Frame), mean)
tapply(s1$Moral_composite, list(s1$Proclamation, s1$Perspective, s1$Frame), sd)
tapply(s1$Moral_composite, list(s1$Proclamation, s1$Perspective, s1$Frame), length)

#Across Proclamation*Frame
tapply(s1$Moral_composite, list(s1$Proclamation, s1$Frame), mean)
tapply(s1$Moral_composite, list(s1$Proclamation, s1$Frame), sd)
tapply(s1$Moral_composite, list(s1$Proclamation, s1$Frame), length)

#Across Proclamation*Perspective
tapply(s1$Moral_composite, list(s1$Proclamation, s1$Perspective), mean)
tapply(s1$Moral_composite, list(s1$Proclamation, s1$Perspective), sd)
tapply(s1$Moral_composite, list(s1$Proclamation, s1$Perspective), length)

#Across Frame*Perspective
tapply(s1$Moral_composite, list(s1$Perspective, s1$Frame), mean)
tapply(s1$Moral_composite, list(s1$Perspective, s1$Frame), sd)
tapply(s1$Moral_composite, list(s1$Perspective, s1$Frame), length)

#Across Proclamation
tapply(s1$Moral_composite, s1$Proclamation, mean)
tapply(s1$Moral_composite, s1$Proclamation, sd)
tapply(s1$Moral_composite, s1$Proclamation, length)

#Across Frame
tapply(s1$Moral_composite, s1$Frame, mean)
tapply(s1$Moral_composite, s1$Frame, sd)
tapply(s1$Moral_composite, s1$Frame, length)

#Across Perspective
tapply(s1$Moral_composite, s1$Perspective, mean)
tapply(s1$Moral_composite, s1$Perspective, sd)
tapply(s1$Moral_composite, s1$Perspective, length)

#Overall
mean(s1$Moral_composite)
sd(s1$Moral_composite)
length(s1$Moral_composite)
```

# Future Honesty Model

```{r}
#ANOVA
honest_1.afex <-aov_car(Honest_composite ~ Proclamation*Perspective*Frame + Error(ID), data=s1)
summary(honest_1.afex) 
anova_apa(honest_1.afex)
```


# Future Honesty Descriptives

```{r}
#Cells
tapply(s1$Honest_composite, list(s1$Proclamation, s1$Perspective, s1$Frame), mean)
tapply(s1$Honest_composite, list(s1$Proclamation, s1$Perspective, s1$Frame), sd)
tapply(s1$Honest_composite, list(s1$Proclamation, s1$Perspective, s1$Frame), length)

#Across Proclamation*Frame
tapply(s1$Honest_composite, list(s1$Proclamation, s1$Frame), mean)
tapply(s1$Honest_composite, list(s1$Proclamation, s1$Frame), sd)
tapply(s1$Honest_composite, list(s1$Proclamation, s1$Frame), length)

#Across Proclamation*Perspective
tapply(s1$Honest_composite, list(s1$Proclamation, s1$Perspective), mean)
tapply(s1$Honest_composite, list(s1$Proclamation, s1$Perspective), sd)
tapply(s1$Honest_composite, list(s1$Proclamation, s1$Perspective), length)

#Across Frame*Perspective
tapply(s1$Honest_composite, list(s1$Perspective, s1$Frame), mean)
tapply(s1$Honest_composite, list(s1$Perspective, s1$Frame), sd)
tapply(s1$Honest_composite, list(s1$Perspective, s1$Frame), length)

#Across Proclamation
tapply(s1$Honest_composite, s1$Proclamation, mean)
tapply(s1$Honest_composite, s1$Proclamation, sd)
tapply(s1$Honest_composite, s1$Proclamation, length)

#Across Frame
tapply(s1$Honest_composite, s1$Frame, mean)
tapply(s1$Honest_composite, s1$Frame, sd)
tapply(s1$Honest_composite, s1$Frame, length)

#Across Perspective
tapply(s1$Honest_composite, s1$Perspective, mean)
tapply(s1$Honest_composite, s1$Perspective, sd)
tapply(s1$Honest_composite, s1$Perspective, length)

#Overall
mean(s1$Honest_composite)
sd(s1$Honest_composite)
length(s1$Honest_composite)
```

# Voting Intentions Model

```{r}
#ANOVA
Voting_1.afex <-aov_car(Voting ~ Proclamation*Perspective*Frame + Error(ID), data=s1)
summary(Voting_1.afex) 
anova_apa(Voting_1.afex)
```

# Voting Descriptives

```{r}
#Cells
tapply(s1$Voting, list(s1$Proclamation, s1$Perspective, s1$Frame), mean)
tapply(s1$Voting, list(s1$Proclamation, s1$Perspective, s1$Frame), sd)
tapply(s1$Voting, list(s1$Proclamation, s1$Perspective, s1$Frame), length)

#Across Proclamation*Frame
tapply(s1$Voting, list(s1$Proclamation, s1$Frame), mean)
tapply(s1$Voting, list(s1$Proclamation, s1$Frame), sd)
tapply(s1$Voting, list(s1$Proclamation, s1$Frame), length)

#Across Proclamation*Perspective
tapply(s1$Voting, list(s1$Proclamation, s1$Perspective), mean)
tapply(s1$Voting, list(s1$Proclamation, s1$Perspective), sd)
tapply(s1$Voting, list(s1$Proclamation, s1$Perspective), length)

#Across Frame*Perspective
tapply(s1$Voting, list(s1$Perspective, s1$Frame), mean)
tapply(s1$Voting, list(s1$Perspective, s1$Frame), sd)
tapply(s1$Voting, list(s1$Perspective, s1$Frame), length)

#Across Proclamation
tapply(s1$Voting, s1$Proclamation, mean)
tapply(s1$Voting, s1$Proclamation, sd)
tapply(s1$Voting, s1$Proclamation, length)

#Across Frame
tapply(s1$Voting, s1$Frame, mean)
tapply(s1$Voting, s1$Frame, sd)
tapply(s1$Voting, s1$Frame, length)

#Across Perspective
tapply(s1$Voting, s1$Perspective, mean)
tapply(s1$Voting, s1$Perspective, sd)
tapply(s1$Voting, s1$Perspective, length)

#Overall
mean(s1$Voting)
sd(s1$Voting)
length(s1$Voting)
```

# Subsetting Data for Simple Effects

```{r}
#How does Proclamation vary within just third-person lie frame?
thirdperson_lie <- s1 %>%
  filter(Perspective == "general") %>%
  filter(Frame == "lie") #174

#How does Proclamation vary within just third-person truth frame?
thirdperson_truth <- s1 %>%
  filter(Perspective == "general") %>%
  filter(Frame == "truth") #208

#How does Proclamation vary within just first-person lie frame?
firstperson_lie <- s1 %>%
  filter(Perspective == "I") %>%
  filter(Frame == "lie") #207

#How does Proclamation vary within just first-person truth frame?
firstperson_truth <- s1 %>%
  filter(Perspective == "I") %>%
  filter(Frame == "truth") #213

#How does Proclamation vary within just second-person lie frame?
secperson_lie <- s1 %>%
  filter(Perspective == "you") %>%
  filter(Frame == "lie") #211

#How does Proclamation vary within just second-person truth frame?
secperson_truth <- s1 %>%
  filter(Perspective == "you") %>%
  filter(Frame == "truth") #192
```

# Voting Simple Effects - T-tests

```{r}
#Proclamation within third person general lie frame
t.test(Voting ~ Proclamation, thirdperson_lie, var.equal = TRUE)
t_apa(t.test(Voting ~ Proclamation, thirdperson_lie, var.equal = TRUE))

#Proclamation within third person general truth frame
t.test(Voting ~ Proclamation, thirdperson_truth, var.equal = TRUE) 
t_apa(t.test(Voting ~ Proclamation, thirdperson_truth, var.equal = TRUE))

#Proclamation within first person lie frame
t.test(Voting ~ Proclamation, firstperson_lie, var.equal = TRUE)
t_apa(t.test(Voting ~ Proclamation, firstperson_lie, var.equal = TRUE))

#Proclamation within first person truth frame
t.test(Voting ~ Proclamation, firstperson_truth, var.equal = TRUE) 
t_apa(t.test(Voting ~ Proclamation, firstperson_truth, var.equal = TRUE))

#Proclamation within second lie frame
t.test(Voting ~ Proclamation, secperson_lie, var.equal = TRUE) 
t_apa(t.test(Voting ~ Proclamation, secperson_lie, var.equal = TRUE))

#Proclamation within second truth frame
t.test(Voting ~ Proclamation, secperson_truth, var.equal = TRUE) 
t_apa(t.test(Voting ~ Proclamation, secperson_truth, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
voting_model = aov_ez('ID', 'Voting', s1,
                    within = c (),
                    between = c ('Proclamation', 'Perspective', 'Frame'),
                    anova_table = list(es = 'pes'))
print(voting_model)
means <- emmeans(voting_model, ~ Proclamation|Perspective|Frame)
print(means)
post1 <- emmeans(voting_model, ~ Proclamation|Perspective|Frame)
pairs(post1)

```

# Morality Simple Effects - T-tests

```{r}
#Proclamation within third person general lie frame
t.test(Moral_composite~ Proclamation, thirdperson_lie, var.equal = TRUE)
t_apa(t.test(Moral_composite~ Proclamation, thirdperson_lie, var.equal = TRUE))

#Proclamation within third person general truth frame
t.test(Moral_composite~ Proclamation, thirdperson_truth, var.equal = TRUE) 
t_apa(t.test(Moral_composite~ Proclamation, thirdperson_truth, var.equal = TRUE))

#Proclamation within first person lie frame
t.test(Moral_composite~ Proclamation, firstperson_lie, var.equal = TRUE)
t_apa(t.test(Moral_composite~ Proclamation, firstperson_lie, var.equal = TRUE))

#Proclamation within first person truth frame
t.test(Moral_composite~ Proclamation, firstperson_truth, var.equal = TRUE) 
t_apa(t.test(Moral_composite~ Proclamation, firstperson_truth, var.equal = TRUE))

#Proclamation within second lie frame
t.test(Moral_composite~ Proclamation, secperson_lie, var.equal = TRUE) 
t_apa(t.test(Moral_composite~ Proclamation, secperson_lie, var.equal = TRUE))

#Proclamation within second truth frame
t.test(Moral_composite~ Proclamation, secperson_truth, var.equal = TRUE) 
t_apa(t.test(Moral_composite~ Proclamation, secperson_truth, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
moral_model = aov_ez('ID', 'Moral_composite', s1,
                    within = c (),
                    between = c ('Proclamation', 'Perspective', 'Frame'),
                    anova_table = list(es = 'pes'))
print(moral_model)
means <- emmeans(moral_model, ~ Proclamation|Perspective|Frame)
print(means)
post2 <- emmeans(moral_model, ~ Proclamation|Perspective|Frame)
pairs(post2)

```

See the attached R script "Study1_mediation.R" for the multiple mediation analysis. As mentioned, further analysis notes available upon request.
