---
title: "Study 5"
author: "Elizabeth Huppert"
date: "1/14/2020"
output: pdf_document
---

#Set-up

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-psych
-reshape2
-apa
-dplyr
-emmeans

#Load Packages and Data

```{r, include = FALSE}
library(here)
library(tidyverse)
library(psych)
library(reshape2)
library(afex)
library(apa)
library(dplyr)
library(emmeans)

#read in data

s5 <- read.csv(here("HypocrisyStudy5_cleaned.csv"))

```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


#Models

Key Variable Names (also see codebook for more information):

1. Proclamation:
Assignment to absolute vs. flexible honesty stance

2. Order:
Survey1 vs. game1 refers to order in which target information is presented

-survey1 (evaluations at timepoint 1 after just survey information, evaluations at timepoint 2 after the proscoial lie behavior)
-game1 (evaluations at timepoint 1 after just prosocial lie behavior, timepoint 2 is the survey information)

3. Time:
Within subject factor, evaluations are reported at two points in time

For supplement (The Choice Game):
Trustbeh = KEEP or PASS in The Coin Flip Game 
(0 = KEEP, 1 = PASS)

#Recode proclamation for ease of interpretation

```{r}
s5$proclamation <- factor(s5$proclamation, levels = c("ambiguous", "absolute"))
```

#Composite evaluation variables

Items with high agreement were combined as per our pre-registration.

```{r}
#Time one 
#Hypocrisy
hypocrisy_5_check <- data.frame(s5$hypocrisy_1, s5$hypocrisy_2, s5$hypocrisy_4, s5$hypocrisy_5)
summary(hypocrisy_5_check)
describe(hypocrisy_5_check)
psych::alpha(hypocrisy_5_check) #alpha = 0.89 
s5 <- mutate(s5, Hypocrisy.1_composite5 = ((s5$hypocrisy_1 + s5$hypocrisy_2 + s5$hypocrisy_4 + s5$hypocrisy_5)/4))

#Morality
morality5_check <- data.frame(s5$moral_1, s5$moral_2, s5$moral_3)
summary(morality5_check )
describe(morality5_check )
psych::alpha(morality5_check ) #alpha = 0.97
s5 <- mutate(s5, Moral.1_composite5 = ((s5$moral_1 +s5$moral_2 + s5$moral_3)/3))

#Commitment to Honesty
Honest5_df <- data.frame(s5$honest_freq_1, s5$honest_likely_1, s5$honest_extreme_1, s5$committment_honesty_1)
summary(Honest5_df)
describe(Honest5_df)
psych::alpha(Honest5_df) #alpha = 0.85
s5 <- mutate(s5, Honest.1_composite5 = ((s5$honest_freq_1 + s5$honest_likely_1 + s5$honest_extreme_1 + s5$committment_honesty_1)/4))


#Time two  
#Hypocrisy
hypocrisy_5_check.2 <- data.frame(s5$hypocrisy_1.2, s5$hypocrisy_2.2, s5$hypocrisy_4.2, s5$hypocrisy_5.2)
summary(hypocrisy_5_check.2)
describe(hypocrisy_5_check.2)
psych::alpha(hypocrisy_5_check.2) #alpha = 0.91
s5 <- mutate(s5, 
             Hypocrisy.2_composite5 = (s5$hypocrisy_1.2 + s5$hypocrisy_2.2 + s5$hypocrisy_4.2 + s5$hypocrisy_5.2)/4)

#Morality
morality5_check.2 <- data.frame(s5$moral_1.2, s5$moral_2.2, s5$moral_3.2)
summary(morality5_check.2)
describe(morality5_check.2)
psych::alpha(morality5_check.2) #alpha = 0.97
s5 <- mutate(s5, Moral.2_composite5  = ((s5$moral_1.2+s5$moral_2.2+s5$moral_3.2)/3))

#Commitment to Honesty
Honest5_df.2  <- data.frame(s5$honest_freq_2, s5$honest_likely_2, s5$honest_extreme_2, s5$committment_honesty_2)
summary(Honest5_df.2)
describe(Honest5_df.2)
psych::alpha(Honest5_df.2) #alpha = 0.82
s5 <- mutate(s5, Honest.2_composite5 = ((s5$honest_freq_2 + s5$honest_likely_2 + s5$honest_extreme_2 + s5$committment_honesty_2)/4))

#Correlation between Morality time 1 and time 2 composite for post-hoc power analysis
cor.test(s5$Moral.1_composite5, s5$Moral.2_composite5) #r = .58

#Supplemental (guilt and moral standards/realism) 
#Guilt time 1
cor.test(s5$guilt_1, s5$guilt_2) #r = 0.93
s5 <- mutate(s5, Guilt_composite = ((s5$guilt_1+s5$guilt_2)/2))

#Moral Standards time 1
cor(s5$moral_standards1, s5$moral_standards1.2)
cor.test(s5$moral_standards1, s5$moral_standards2) #r = 0.37; not combined

#Guilt time 2
cor.test(s5$guilt_1.2, s5$guilt_2.2) #r = 0.91
s5 <- mutate(s5, Guilt.2_composite = ((s5$guilt_1.2 + s5$guilt_2.2)/2))

#Moral Standards time 2
cor.test(s5$moral_standards1.2, s5$moral_standards2.2) # .48; not combined

```

Evaluation variables:

Timepoint 1:

Hypocrisy.1_composite5 = hypocrisy composite of 4 items at timepoint 1 
Guilt_composite = guilt composite of 2 items at timepoint 1
Moral.1_composite5 = morality composite of 3 items at timepoint 1
Honest.1_composite5 = committment to honesty composite of 4 items at timepoint 1

Timepoint 2 (same 1-7 Likert-type scales):

Hypocrisy.2_composite5  = hypocrisy composite of 4 items at timepoint 2
Guilt.2_composite = guilt composite of 2 items at timepoint 2
Moral.2_composite5 = morality composite of 3 items at timepoint 2
Honest.2_composite5 = committment to honesty composite of 4 items at timepoint 2

#Hypocrisy Model

```{r}
#Dataframe for Hypocrisy
hypocrisy_df <-melt(s5, 
                id.vars=c("condition", "ID", "proclamation", "order"),
                #measure command is for the DV
                measure.vars=c("Hypocrisy.1_composite5","Hypocrisy.2_composite5"),
                variable.name="hypocrisy.time",
                value.name="hypocrisy.value"
)

#ANOVA
hypocrisy5.afex <- aov_car(
  hypocrisy.value ~ proclamation*order*hypocrisy.time + Error(ID/hypocrisy.time),
  data = hypocrisy_df)
summary(hypocrisy5.afex)
anova_apa(hypocrisy5.afex)

```

#Descriptives Hypocrisy

```{r}
#Cells
tapply(hypocrisy_df$hypocrisy.value, 
       list(hypocrisy_df$proclamation, hypocrisy_df$order, hypocrisy_df$hypocrisy.time), 
       FUN = mean)

tapply(hypocrisy_df$hypocrisy.value, 
       list(hypocrisy_df$proclamation, hypocrisy_df$order, hypocrisy_df$hypocrisy.time), 
       FUN = sd)

tapply(hypocrisy_df$hypocrisy.value, 
       list(hypocrisy_df$proclamation, hypocrisy_df$order, hypocrisy_df$hypocrisy.time), 
       FUN = length)

#Across Proclamation and Time
tapply(hypocrisy_df$hypocrisy.value, list(hypocrisy_df$proclamation, hypocrisy_df$hypocrisy.time),
       FUN = length)

tapply(hypocrisy_df$hypocrisy.value, list(hypocrisy_df$proclamation, hypocrisy_df$hypocrisy.time),
       FUN = mean)

tapply(hypocrisy_df$hypocrisy.value, list(hypocrisy_df$proclamation, hypocrisy_df$hypocrisy.time),
       FUN = sd)

#Across Order and Time
tapply(hypocrisy_df$hypocrisy.value, list(hypocrisy_df$order, 
                                                hypocrisy_df$hypocrisy.time),FUN = length)
tapply(hypocrisy_df$hypocrisy.value, list(hypocrisy_df$order, 
                                                hypocrisy_df$hypocrisy.time),FUN = mean)
tapply(hypocrisy_df$hypocrisy.value, list(hypocrisy_df$order, 
                                                hypocrisy_df$hypocrisy.time),FUN = sd)

#Across Proclamation and Order
tapply(hypocrisy_df$hypocrisy.value, list(hypocrisy_df$proclamation, 
                                                hypocrisy_df$order),FUN = length)
tapply(hypocrisy_df$hypocrisy.value, list(hypocrisy_df$proclamation, 
                                                hypocrisy_df$order),FUN = mean)
tapply(hypocrisy_df$hypocrisy.value, list(hypocrisy_df$proclamation, 
                                                hypocrisy_df$order),FUN = sd)

#Across Proclamation
tapply(hypocrisy_df$hypocrisy.value, hypocrisy_df$proclamation,FUN = mean)
tapply(hypocrisy_df$hypocrisy.value, hypocrisy_df$proclamation,FUN = sd)
tapply(hypocrisy_df$hypocrisy.value, hypocrisy_df$proclamation,FUN = length)

#Across Time
tapply(hypocrisy_df$hypocrisy.value, hypocrisy_df$hypocrisy.time,FUN = mean)
tapply(hypocrisy_df$hypocrisy.value, hypocrisy_df$hypocrisy.time,FUN = sd)
tapply(hypocrisy_df$hypocrisy.value, hypocrisy_df$hypocrisy.time,FUN = length)

#AcrossOrder
tapply(hypocrisy_df$hypocrisy.value, hypocrisy_df$order,FUN = mean)
tapply(hypocrisy_df$hypocrisy.value, hypocrisy_df$order,FUN = sd)
tapply(hypocrisy_df$hypocrisy.value, hypocrisy_df$order,FUN = length)

#Overall
mean(hypocrisy_df$hypocrisy.value)
sd(hypocrisy_df$hypocrisy.value)
length(hypocrisy_df$hypocrisy.value)

```

#Follow-up tests for two*way interactions: Hypocrisy

```{r}
#Proclamation*Time - paired t-tests

#Time 1 vs. 2 on absolute only
#Paired t-test
absolute_s5 <- s5 %>%
  filter(proclamation == "absolute")

t.test(absolute_s5$Hypocrisy.1_composite5, absolute_s5$Hypocrisy.2_composite5, paired = TRUE)
t_apa(t.test(absolute_s5$Hypocrisy.1_composite5, absolute_s5$Hypocrisy.2_composite5, paired = TRUE))

#Time 1 vs. 2 on flexible only
#Paired t-test
flexible_s5 <- s5 %>%
  filter(proclamation == "ambiguous")

t.test(flexible_s5$Hypocrisy.1_composite5, flexible_s5$Hypocrisy.2_composite5, paired = TRUE)
t_apa(t.test(flexible_s5$Hypocrisy.1_composite5, flexible_s5$Hypocrisy.2_composite5, paired = TRUE))

#Proclamation*Order 

#Effect of order in just absolute
absolute_hypo <- hypocrisy_df %>%
  filter(proclamation ==  "absolute")

#independent t-test
t.test(hypocrisy.value ~ order, absolute_hypo , var.equal = TRUE)
t_apa(t.test(hypocrisy.value ~ order, absolute_hypo , var.equal = TRUE))

#Effect of order in just flexible
flexible_hypo <- hypocrisy_df %>%
  filter(proclamation ==  "ambiguous")

#independent t-test
t.test(hypocrisy.value ~ order, flexible_hypo , var.equal = TRUE)
t_apa(t.test(hypocrisy.value ~ order, flexible_hypo, var.equal = TRUE))

#Effect of proc in just survey1
survey1_hypo <- hypocrisy_df %>%
  filter(order==  "survey1")

#independent t-test
t.test(hypocrisy.value ~ proclamation, survey1_hypo, var.equal = TRUE)
t_apa(t.test(hypocrisy.value ~ proclamation, survey1_hypo, var.equal = TRUE))


#Effect of proc in just game1
game1_hypo <- hypocrisy_df %>%
  filter(order==  "game1")

#independent t-test
t.test(hypocrisy.value ~ proclamation, game1_hypo, var.equal = TRUE)
t_apa(t.test(hypocrisy.value ~ proclamation, game1_hypo, var.equal = TRUE))



#Alternative ANOVA and tukey post-hoc tests
hyp_model = aov_ez('ID', 'hypocrisy.value', hypocrisy_df,
                    within = c ('hypocrisy.time'),
                    between = c ('proclamation', 'order'),
                    anova_table = list(es = 'pes'))
print(hyp_model)

em1 <- emmeans::emmeans(hyp_model, pairwise ~ proclamation:hypocrisy.time)
em1$contrasts
ptmeans <- emmeans(hyp_model, ~ hypocrisy.time|proclamation)
print(ptmeans)
post1 <- emmeans(hyp_model, ~ hypocrisy.time|proclamation)
pairs(post1)

em2 <- emmeans::emmeans(hyp_model, pairwise ~ proclamation:order)
em2$contrasts
post3 <- emmeans(hyp_model, ~ proclamation|order)
pairs(post3) 
pomeans <- emmeans(hyp_model, ~ order|proclamation)
print(pomeans)
post2 <- emmeans(hyp_model, ~ order|proclamation)
pairs(post2)
```

#Morality 

```{r}
#Dataframe for Morality
hypo_moral5 <-melt(s5, 
                       id.vars=c("condition", "ID","proclamation", "order"),
                       #measure command is for the DV
                       measure.vars=c("Moral.1_composite5","Moral.2_composite5"),
                       variable.name="moral.time",
                       value.name="moral.value"
)

#ANOVA
moral.afex <- aov_car(moral.value ~ proclamation*order*moral.time + Error(ID/moral.time), data=hypo_moral5)
summary(moral.afex)
anova_apa(moral.afex)

#Abs vs. Flex morality focal at time two - need cohen's D
#abs mean =   4.54, sd = 1.59, 294 
#flex mean =  3.92, sd = 1.39, 306
#pooled SD = sqrt(((1.59^2) + (1.39^2))/2)
sqrt((((1.59^2) + (1.39^2))/2)) #1.493352

#cohens = (mean - mean)/SD pooeld
(4.54-3.92)/1.493352 # 0.42

d5 <- cohens_d(t_test(Moral.2_composite5 ~ proclamation, s5)) 
#see Hypocrisy Simple Effects above to exclude rarely, N = 600
d5 #Cohen's d abs. vs. flex. on morality (abs value)  = 0.42, enter this in power
```

# Morality Descriptives

```{r}
#Cells
tapply(hypo_moral5$moral.value, 
       list(hypo_moral5$proclamation, hypo_moral5$order, hypo_moral5$moral.time), 
       FUN = mean)
tapply(hypo_moral5$moral.value, 
       list(hypo_moral5$proclamation, hypo_moral5$order, hypo_moral5$moral.time), 
       FUN = sd)
tapply(hypo_moral5$moral.value, 
       list(hypo_moral5$proclamation, hypo_moral5$order, 
            hypo_moral5$moral.time), 
       FUN = length)

#Across Proclamation and Time
tapply(hypo_moral5$moral.value, list(hypo_moral5$proclamation, 
                                     hypo_moral5$moral.time),FUN = length)
tapply(hypo_moral5$moral.value, list(hypo_moral5$proclamation, 
                                     hypo_moral5$moral.time),FUN = mean)
tapply(hypo_moral5$moral.value, list(hypo_moral5$proclamation, 
                                     hypo_moral5$moral.time),FUN = sd)

#Across Order and Time
tapply(hypo_moral5$moral.value, list(hypo_moral5$order, 
                                     hypo_moral5$moral.time),FUN = length)
tapply(hypo_moral5$moral.value, list(hypo_moral5$order, 
                                     hypo_moral5$moral.time),FUN = mean)
tapply(hypo_moral5$moral.value, list(hypo_moral5$order, 
                                     hypo_moral5$moral.time),FUN = sd)

#Across Proclamation and Order
tapply(hypo_moral5$moral.value, list(hypo_moral5$proclamation, 
                                                hypo_moral5$order),FUN = length)
tapply(hypo_moral5$moral.value, list(hypo_moral5$proclamation, 
                                                hypo_moral5$order),FUN = mean)
tapply(hypo_moral5$moral.value, list(hypo_moral5$proclamation, 
                                                hypo_moral5$order),FUN = sd)
#Across Proclamation
tapply(hypo_moral5$moral.value, hypo_moral5$proclamation,FUN = mean)
tapply(hypo_moral5$moral.value, hypo_moral5$proclamation,FUN = sd)
tapply(hypo_moral5$moral.value, hypo_moral5$proclamation,FUN = length)

#Across Order
tapply(hypo_moral5$moral.value, hypo_moral5$order,FUN = mean)
tapply(hypo_moral5$moral.value, hypo_moral5$order,FUN = sd)
tapply(hypo_moral5$moral.value, hypo_moral5$order,FUN = length)

#Across Time
tapply(hypo_moral5$moral.value, hypo_moral5$moral.time,FUN = mean)
tapply(hypo_moral5$moral.value, hypo_moral5$moral.time,FUN = sd)
tapply(hypo_moral5$moral.value, hypo_moral5$moral.time,FUN = length)

#Overall
mean(hypo_moral5$moral.value)
sd(hypo_moral5$moral.value)
length(hypo_moral5$moral.value)
```


# Follow-up tests for two*way interactions: Morality

```{r}
#Proclamation*Time 

#Time 1 vs. 2 on absolute only
#Paired t-test
absolute_s5 <- s5 %>%
  filter(proclamation == "absolute")

t.test(absolute_s5$Moral.1_composite5, absolute_s5$Moral.2_composite5, paired = TRUE)
t_apa(t.test(absolute_s5$Moral.1_composite5, absolute_s5$Moral.2_composite5, paired = TRUE))

#Time 1 vs. 2 on flexible only
#Paired t-test
flexible_s5 <- s5 %>%
  filter(proclamation == "ambiguous")

t.test(flexible_s5$Moral.1_composite5, flexible_s5$Moral.2_composite5, paired = TRUE)
t_apa(t.test(flexible_s5$Moral.1_composite5, flexible_s5$Moral.2_composite5, paired = TRUE))

#Order*Time 

#Time 1 vs. 2 on survey1 only
#Paired t-test
survey1_s5 <- s5 %>%
  filter(order == "survey1")

t.test(survey1_s5$Moral.1_composite5, survey1_s5$Moral.2_composite5, paired = TRUE)
t_apa(t.test(survey1_s5$Moral.1_composite5, survey1_s5$Moral.2_composite5, paired = TRUE))


#Time 1 vs. 2 on game1 only
#Paired t-test
game1_s5 <- s5 %>%
  filter(order == "game1")

t.test(game1_s5$Moral.1_composite5, game1_s5$Moral.2_composite5, paired = TRUE)
t_apa(t.test(game1_s5$Moral.1_composite5, game1_s5$Moral.2_composite5, paired = TRUE))


#Proclamation*Order

#Effect of order in just absolute targets
absolute_moral <- hypo_moral5 %>%
  filter(proclamation ==  "absolute")

#independent t-test
t.test(moral.value ~ order, absolute_moral , var.equal = TRUE)
t_apa(t.test(moral.value ~ order, absolute_moral, var.equal = TRUE))

#Effect of order in just flexible targets
flexible_moral <- hypo_moral5 %>%
  filter(proclamation ==  "ambiguous")

#independent t-test
t.test(moral.value ~ order, flexible_moral, var.equal = TRUE)
t_apa(t.test(moral.value ~ order, flexible_moral, var.equal = TRUE))

#Effect of proc in just survey1 ordering
survey1_moral <- hypo_moral5  %>%
  filter(order==  "survey1")

#independent t-test
t.test(moral.value ~ proclamation, survey1_moral, var.equal = TRUE)
t_apa(t.test(moral.value ~ proclamation, survey1_moral, var.equal = TRUE))

#Effect of proc in just game1 ordering
game1_moral <- hypo_moral5  %>%
  filter(order==  "game1")

#independent t-test
t.test(moral.value ~ proclamation, game1_moral, var.equal = TRUE)
t_apa(t.test(moral.value ~ proclamation, game1_moral, var.equal = TRUE))


#Alternative ANOVA and tukey post-hoc tests
mor_model = aov_ez('ID', 'moral.value', hypo_moral5,
                    within = c ('moral.time'),
                    between = c ('proclamation', 'order'),
                    anova_table = list(es = 'pes'))
print(mor_model)

em4 <- emmeans::emmeans(mor_model, pairwise ~ moral.time:proclamation)
em4$contrasts
ptmeans <- emmeans(mor_model, ~ moral.time|proclamation)
print(ptmeans)
post1 <- emmeans(mor_model, ~ moral.time|proclamation)
pairs(post1)

em5 <- emmeans::emmeans(mor_model, pairwise ~ order:proclamation)
em5$contrasts
pomeans <- emmeans(mor_model, ~ order|proclamation)
print(pomeans)
post2 <- emmeans(mor_model, ~ order|proclamation)
pairs(post2)  

em6 <- emmeans::emmeans(mor_model, pairwise ~ moral.time:order)
em6$contrasts
tomeans <- emmeans(mor_model, ~ moral.time|order)
print(tomeans)
post3 <- emmeans(mor_model, ~ moral.time|order)
pairs(post3)  


```

#Commitment to Honesty

```{r}
#Dataframe for Commitment to Honesty
hypo_honest5 <-melt(s5, 
                   id.vars=c("condition", "ID", "proclamation", "order"),
                   #measure command is for the DV
                   measure.vars=c("Honest.1_composite5","Honest.2_composite5"),
                   variable.name="honest.time",
                   value.name="honest.value"
)


#ANOVA
honest.afex <- aov_car(honest.value ~ proclamation*order*honest.time + Error(ID/honest.time), data=hypo_honest5)
summary(honest.afex)
anova_apa(honest.afex)
```

#Commitment to Honesty Descriptives

```{r}
#Cells
tapply(hypo_honest5$honest.value, 
       list(hypo_honest5$proclamation, hypo_honest5$order, hypo_honest5$honest.time), 
       FUN = mean)
tapply(hypo_honest5$honest.value, 
       list(hypo_honest5$proclamation, hypo_honest5$order, hypo_honest5$honest.time), 
       FUN = sd)
tapply(hypo_honest5$honest.value, 
       list(hypo_honest5$proclamation, hypo_honest5$order, 
            hypo_honest5$honest.time), 
       FUN = length)

#Across Proclamation and Time
tapply(hypo_honest5$honest.value, list(hypo_honest5$proclamation, 
                                     hypo_honest5$honest.time),FUN = length)
tapply(hypo_honest5$honest.value, list(hypo_honest5$proclamation, 
                                     hypo_honest5$honest.time),FUN = mean)
tapply(hypo_honest5$honest.value, list(hypo_honest5$proclamation, 
                                     hypo_honest5$honest.time),FUN = sd)

#Across Order and Time
tapply(hypo_honest5$honest.value, list(hypo_honest5$order, 
                                     hypo_honest5$honest.time),FUN = length)
tapply(hypo_honest5$honest.value, list(hypo_honest5$order, 
                                     hypo_honest5$honest.time), FUN = mean)
tapply(hypo_honest5$honest.value, list(hypo_honest5$order, 
                                     hypo_honest5$honest.time),FUN = sd)


#Across Proclamation and Order
tapply(hypo_honest5$honest.value, list(hypo_honest5$proclamation, 
                                                hypo_honest5$order),FUN = length)
tapply(hypo_honest5$honest.value, list(hypo_honest5$proclamation, 
                                               hypo_honest5$order),FUN = mean)
tapply(hypo_honest5$honest.value, list(hypo_honest5$proclamation, 
                                               hypo_honest5$order),FUN = sd)

#Across Proclamation
tapply(hypo_honest5$honest.value, hypo_honest5$proclamation,FUN = mean)
tapply(hypo_honest5$honest.value, hypo_honest5$proclamation,FUN = sd)
tapply(hypo_honest5$honest.value, hypo_honest5$proclamation,FUN = length)

#Across Order
tapply(hypo_honest5$honest.value, hypo_honest5$order,FUN = mean)
tapply(hypo_honest5$honest.value, hypo_honest5$order,FUN = sd)
tapply(hypo_honest5$honest.value, hypo_honest5$order,FUN = length)

#Across Time
tapply(hypo_honest5$honest.value, hypo_honest5$honest.time,FUN = mean)
tapply(hypo_honest5$honest.value, hypo_honest5$honest.time,FUN = sd)
tapply(hypo_honest5$honest.value, hypo_honest5$honest.time,FUN = length)

#Overall
mean(hypo_honest5$honest.value)
sd(hypo_honest5$honest.value)
length(hypo_honest5$honest.value)

```

#Follow-up tests for two*way interactions: Commitment to Honesty

```{r}
#Proclamation*Time 

#Time 1 vs. 2 on absolute only
#Paired t-test
absolute_s5 <- s5 %>%
  filter(proclamation == "absolute")

t.test(absolute_s5$Honest.1_composite5, absolute_s5$Honest.2_composite5, paired = TRUE)
t_apa(t.test(absolute_s5$Honest.1_composite5, absolute_s5$Honest.2_composite5, paired = TRUE))

#Time 1 vs. 2 on flexible only
#Paired t-test
flexible_s5 <- s5 %>%
  filter(proclamation == "ambiguous")

t.test(flexible_s5$Honest.1_composite5, flexible_s5$Honest.2_composite5, paired = TRUE)
t_apa(t.test(flexible_s5$Honest.1_composite5, flexible_s5$Honest.2_composite5, paired = TRUE))

#Order*Time 

#Time 1 vs. 2 on survey1 only
#Paired t-test
survey1_s5 <- s5 %>%
  filter(order == "survey1")

t.test(survey1_s5$Honest.1_composite5, survey1_s5$Honest.2_composite5, paired = TRUE)
t_apa(t.test(survey1_s5$Honest.1_composite5, survey1_s5$Honest.2_composite5, paired = TRUE))

#Time 1 vs. 2 on game1 only
#Paired t-test
game1_s5 <- s5 %>%
  filter(order == "game1")

t.test(game1_s5$Honest.1_composite5, game1_s5$Honest.2_composite5, paired = TRUE)
t_apa(t.test(game1_s5$Honest.1_composite5, game1_s5$Honest.2_composite5, paired = TRUE))


#Proclamation*Order

#Effect of order in just absolute
absolute_honest <- hypo_honest5 %>%
  filter(proclamation ==  "absolute")

#independent t-test
t.test(honest.value ~ order, absolute_honest, var.equal = TRUE)
t_apa(t.test(honest.value ~ order, absolute_honest, var.equal = TRUE))

#Effect of order in just flexible
flexible_honest <- hypo_honest5 %>%
  filter(proclamation ==  "ambiguous")

#independent t-test
t.test(honest.value ~ order, flexible_honest, var.equal = TRUE)
t_apa(t.test(honest.value ~ order, flexible_honest, var.equal = TRUE))


#Effect of proc in just survey1
survey1_honest <- hypo_honest5  %>%
  filter(order==  "survey1")

#independent t-test
t.test(honest.value ~ proclamation, survey1_honest, var.equal = TRUE)
t_apa(t.test(honest.value ~ proclamation, survey1_honest, var.equal = TRUE))


#Effect of proc in just game1
game1_honest <- hypo_honest5  %>%
  filter(order==  "game1")

#independent t-test
t.test(honest.value ~ proclamation, game1_honest, var.equal = TRUE)
t_apa(t.test(honest.value ~ proclamation, game1_honest, var.equal = TRUE))


#Alternative ANOVA and tukey post-hoc tests
hon_model = aov_ez('ID', 'honest.value', hypo_honest5,
                    within = c ('honest.time'),
                    between = c ('proclamation', 'order'),
                    anova_table = list(es = 'pes'))
print(hon_model)

em7 <- emmeans::emmeans(hon_model, pairwise ~ honest.time:proclamation)
em7$contrasts
ptmeans <- emmeans(hon_model, ~ honest.time|proclamation)
print(ptmeans)
post1 <- emmeans(hon_model, ~ honest.time|proclamation)
pairs(post1)

em8 <- emmeans::emmeans(hon_model, pairwise ~ order:proclamation)
em8$contrasts
pomeans <- emmeans(hon_model, ~ order|proclamation)
print(pomeans)
post2 <- emmeans(hon_model, ~ order|proclamation)
pairs(post2)  
post4 <- emmeans(hon_model, ~ proclamation|order)
pairs(post4) 

em9 <- emmeans::emmeans(hon_model, pairwise ~ honest.time:order)
em9$contrasts
tomeans <- emmeans(hon_model, ~ honest.time|order)
print(tomeans)
post3 <- emmeans(hon_model, ~ honest.time|order)
pairs(post3) 

 
```

#Supplemental Information

#Moral Standards Model

```{r}
#Dataframe for Moral Standards (moral_standards1) - "This person has high moral standards"
hypo_ms <-melt(s5, 
                    id.vars=c("condition", "ID", "proclamation", "order"),
                    #measure command is for the DV
                    measure.vars=c("moral_standards1","moral_standards1.2"),
                    variable.name="ms.time",
                    value.name="ms.value"
)


#ANOVA
moralstandards.afex <- aov_car(ms.value ~ proclamation*order*ms.time + Error(ID/ms.time), data= hypo_ms)
summary(moralstandards.afex)
anova_apa(moralstandards.afex)

```

#Moral Standards Descriptives

```{r}
#Cells
tapply(hypo_ms$ms.value , 
       list(hypo_ms$proclamation, hypo_ms$order, hypo_ms$ms.time), 
       FUN = mean)
tapply(hypo_ms$ms.value , 
       list(hypo_ms$proclamation, hypo_ms$order, hypo_ms$ms.time), 
       FUN = sd)
tapply(hypo_ms$ms.value , 
       list(hypo_ms$proclamation, hypo_ms$order, 
            hypo_ms$ms.time), 
       FUN = length)

#Across Proclamation and Time
tapply(hypo_ms$ms.value , list(hypo_ms$proclamation, 
                                     hypo_ms$ms.time),FUN = length)
tapply(hypo_ms$ms.value , list(hypo_ms$proclamation, 
                                     hypo_ms$ms.time),FUN = mean)
tapply(hypo_ms$ms.value , list(hypo_ms$proclamation, 
                                     hypo_ms$ms.time),FUN = sd)

#Across Order and Time
tapply(hypo_ms$ms.value , list(hypo_ms$order, 
                                     hypo_ms$ms.time),FUN = length)
tapply(hypo_ms$ms.value , list(hypo_ms$order, 
                                     hypo_ms$ms.time), FUN = mean)
tapply(hypo_ms$ms.value , list(hypo_ms$order, 
                                     hypo_ms$ms.time),FUN = sd)


#Across Proclamation and Order
tapply(hypo_ms$ms.value , list(hypo_ms$proclamation, 
                                                hypo_ms$order),FUN = length)
tapply(hypo_ms$ms.value , list(hypo_ms$proclamation, 
                                               hypo_ms$order),FUN = mean)
tapply(hypo_ms$ms.value , list(hypo_ms$proclamation, 
                                               hypo_ms$order),FUN = sd)

#Across Proclamation
tapply(hypo_ms$ms.value , hypo_ms$proclamation,FUN = mean)
tapply(hypo_ms$ms.value , hypo_ms$proclamation,FUN = sd)
tapply(hypo_ms$ms.value , hypo_ms$proclamation,FUN = length)

#Across Order
tapply(hypo_ms$ms.value , hypo_ms$order,FUN = mean)
tapply(hypo_ms$ms.value , hypo_ms$order,FUN = sd)
tapply(hypo_ms$ms.value , hypo_ms$order,FUN = length)

#Across Time
tapply(hypo_ms$ms.value , hypo_ms$ms.time,FUN = mean)
tapply(hypo_ms$ms.value , hypo_ms$ms.time,FUN = sd)
tapply(hypo_ms$ms.value , hypo_ms$ms.time,FUN = length)

#Overall
mean(hypo_ms$ms.value)
sd(hypo_ms$ms.value)
length(hypo_ms$ms.value)
```

#Follow-up tests for two*way interactions: Moral Standards

```{r}
#Proclamation*Time 

#Time 1 vs. 2 on absolute only
#Paired t-test
absolute_s5 <- s5 %>%
  filter(proclamation == "absolute")

t.test(absolute_s5$moral_standards1, absolute_s5$moral_standards1.2, paired = TRUE)
t_apa(t.test(absolute_s5$moral_standards1, absolute_s5$moral_standards1.2, paired = TRUE))

#Time 1 vs. 2 on flexible only
#Paired t-test
flexible_s5 <- s5 %>%
  filter(proclamation == "ambiguous")

t.test(flexible_s5$moral_standards1, flexible_s5$moral_standards1.2, paired = TRUE)
t_apa(t.test(flexible_s5$moral_standards1, flexible_s5$moral_standards1.2, paired = TRUE))


#Proclamation*Order 

#Effect of order in just absolute
absolute_ms <- hypo_ms %>%
  filter(proclamation ==  "absolute")

#independent t-test
t.test(ms.value~ order, absolute_ms , var.equal = TRUE)
t_apa(t.test(ms.value ~ order, absolute_ms , var.equal = TRUE))

#Effect of order in just flexible
flexible_ms <- hypo_ms %>%
  filter(proclamation ==  "ambiguous")

#independent t-test
t.test(ms.value~ order, flexible_ms, var.equal = TRUE)
t_apa(t.test(ms.value ~ order, flexible_ms, var.equal = TRUE))


#Effect of proc in just survey1
survey1_ms <- hypo_ms  %>%
  filter(order==  "survey1")

#independent t-test
t.test(ms.value~ proclamation, survey1_ms, var.equal = TRUE)
t_apa(t.test(ms.value ~ proclamation, survey1_ms, var.equal = TRUE))

#Effect of proc in just game1
game1_ms <- hypo_ms  %>%
  filter(order==  "game1")


#Alternative ANOVA and tukey post-hoc tests
ms_model = aov_ez('ID', 'ms.value', hypo_ms,
                    within = c ('ms.time'),
                    between = c ('proclamation', 'order'),
                    anova_table = list(es = 'pes'))
print(ms_model)

em9 <- emmeans::emmeans(ms_model, pairwise ~ ms.time:proclamation)
em9$contrasts
ptmeans <- emmeans(ms_model, ~ ms.time|proclamation)
print(ptmeans)
post1 <- emmeans(ms_model, ~ ms.time|proclamation)
pairs(post1)

em10 <- emmeans::emmeans(ms_model, pairwise ~ order:proclamation)
em10$contrasts
pomeans <- emmeans(ms_model, ~ order|proclamation)
print(pomeans)
post2 <- emmeans(ms_model, ~ order|proclamation)
pairs(post2)  
post3 <- emmeans(ms_model, ~ proclamation|order)
pairs(post3) 
```

#Moral Standards - Realism

```{r}
#Dataframe for Realism - "This person is realistic"
hypo_ms2 <-melt(s5, 
                    id.vars=c("condition", "ID", "proclamation", "order"),
                    #measure command is for the DV
                    measure.vars=c("moral_standards2","moral_standards2.2"),
                    variable.name="ms2.time",
                    value.name="ms2.value"
)

#ANOVA
realism.afex <- aov_car(ms2.value ~ proclamation*order*ms2.time + Error(ID/ms2.time), data= hypo_ms2)
summary(realism.afex)
anova_apa(realism.afex)

```

#Realism Descriptive Statistics

```{r}
#Cells
tapply(hypo_ms2$ms2.value, 
       list(hypo_ms2$proclamation, hypo_ms2$order, hypo_ms2$ms2.time), 
       FUN = mean)
tapply(hypo_ms2$ms2.value, 
       list(hypo_ms2$proclamation, hypo_ms2$order, hypo_ms2$ms2.time), 
       FUN = sd)
tapply(hypo_ms2$ms2.value, 
       list(hypo_ms2$proclamation, hypo_ms2$order, 
            hypo_ms2$ms2.time), 
       FUN = length)

#Across Proclamation and Time
tapply(hypo_ms2$ms2.value, list(hypo_ms2$proclamation, 
                                     hypo_ms2$ms2.time),FUN = length)
tapply(hypo_ms2$ms2.value, list(hypo_ms2$proclamation, 
                                     hypo_ms2$ms2.time),FUN = mean)
tapply(hypo_ms2$ms2.value, list(hypo_ms2$proclamation, 
                                     hypo_ms2$ms2.time),FUN = sd)

#Across Order and Time
tapply(hypo_ms2$ms2.value, list(hypo_ms2$order, 
                                     hypo_ms2$ms2.time),FUN = length)
tapply(hypo_ms2$ms2.value, list(hypo_ms2$order, 
                                     hypo_ms2$ms2.time), FUN = mean)
tapply(hypo_ms2$ms2.value, list(hypo_ms2$order, 
                                     hypo_ms2$ms2.time),FUN = sd)


#Across Proclamation and Order
tapply(hypo_ms2$ms2.value, list(hypo_ms2$proclamation, 
                                                hypo_ms2 $order),FUN = length)
tapply(hypo_ms2$ms2.value, list(hypo_ms2$proclamation, 
                                               hypo_ms2$order),FUN = mean)
tapply(hypo_ms2$ms2.value, list(hypo_ms2$proclamation, 
                                               hypo_ms2$order),FUN = sd)

#Across Proclamation
tapply(hypo_ms2$ms2.value, hypo_ms2$proclamation,FUN = mean)
tapply(hypo_ms2$ms2.value, hypo_ms2$proclamation,FUN = sd)
tapply(hypo_ms2$ms2.value, hypo_ms2$proclamation,FUN = length)

#Across Order
tapply(hypo_ms2$ms2.value, hypo_ms2$order,FUN = mean)
tapply(hypo_ms2$ms2.value, hypo_ms2$order,FUN = sd)
tapply(hypo_ms2$ms2.value, hypo_ms2$order,FUN = length)

#Across Time
tapply(hypo_ms2$ms2.value, hypo_ms2$ms2.time,FUN = mean)
tapply(hypo_ms2$ms2.value, hypo_ms2$ms2.time,FUN = sd)
tapply(hypo_ms2$ms2.value, hypo_ms2$ms2.time,FUN = length)

#Overall
mean(hypo_ms2$ms2.value)
sd(hypo_ms2$ms2.value)
length(hypo_ms2$ms2.value)
```

#Follow-up tests for interactions: Realism

```{r}
#Proclamation*Time 

#Time 1 vs. 2 on absolute only
#Paired t-test
absolute_s5 <- s5 %>%
  filter(proclamation == "absolute")

t.test(absolute_s5$moral_standards2, absolute_s5$moral_standards2.2, paired = TRUE)
t_apa(t.test(absolute_s5$moral_standards2, absolute_s5$moral_standards2.2, paired = TRUE))

#Time 1 vs. 2 on flexible only
#Paired t-test
flexible_s5 <- s5 %>%
  filter(proclamation == "ambiguous")

t.test(flexible_s5$moral_standards2, flexible_s5$moral_standards2.2, paired = TRUE)
t_apa(t.test(flexible_s5$moral_standards2, flexible_s5$moral_standards2.2, paired = TRUE))

#Order*Time 

#Time 1 vs. 2 on survey1 only
#Paired t-test
survey1_s5 <- s5 %>%
  filter(order == "survey1")

t.test(survey1_s5$moral_standards2, survey1_s5$moral_standards2.2, paired = TRUE)
t_apa(t.test(survey1_s5$moral_standards2, survey1_s5$moral_standards2.2, paired = TRUE))

#Time 1 vs. 2 on game1 only
#Paired t-test
game1_s5 <- s5 %>%
  filter(order == "game1")

t.test(game1_s5$moral_standards2, game1_s5$moral_standards2.2, paired = TRUE)
t_apa(t.test(game1_s5$moral_standards2, game1_s5$moral_standards2.2, paired = TRUE))


#Proclamation*Order 

#Effect of order in just absolute
absolute_ms2 <- hypo_ms2 %>%
  filter(proclamation ==  "absolute")

#independent t-test
t.test(ms2.value ~ order, absolute_ms2, var.equal = TRUE)
t_apa(t.test(ms2.value ~ order, absolute_ms2, var.equal = TRUE))

#Effect of order in just flexible
flexible_ms2 <- hypo_ms2 %>%
  filter(proclamation ==  "ambiguous")

#independent t-test
t.test(ms2.value ~ order, flexible_ms2, var.equal = TRUE)
t_apa(t.test(ms2.value ~ order, flexible_ms2, var.equal = TRUE))

#Effect of proc in just survey1
survey1_ms2 <- hypo_ms2  %>%
  filter(order==  "survey1")

#independent t-test
t.test(ms2.value ~ proclamation, survey1_ms2, var.equal = TRUE)
t_apa(t.test(ms2.value ~ proclamation, survey1_ms2, var.equal = TRUE))

#Effect of proc in just game1
game1_ms2 <- hypo_ms2 %>%
  filter(order==  "game1")

#independent t-test
t.test(ms2.value ~ proclamation, game1_ms2, var.equal = TRUE)
t_apa(t.test(ms2.value ~ proclamation, game1_ms2, var.equal = TRUE))


#Alternative ANOVA and tukey post-hoc tests
ms2_model = aov_ez('ID', 'ms2.value', hypo_ms2,
                    within = c ('ms2.time'),
                    between = c ('proclamation', 'order'),
                    anova_table = list(es = 'pes'))
print(ms2_model)

em11 <- emmeans::emmeans(ms2_model, pairwise ~ order:proclamation)
em11$contrasts
pomeans <- emmeans(ms2_model, ~ order|proclamation)
print(pomeans)
post2 <- emmeans(ms2_model, ~ order|proclamation)
pairs(post2)  
post3 <- emmeans(ms2_model, ~ proclamation|order)
pairs(post3)

em12 <- emmeans::emmeans(ms2_model, pairwise ~ order:proclamation)
em12$contrasts
ptmeans <- emmeans(ms2_model, ~ ms2.time|proclamation)
print(ptmeans)
post1 <- emmeans(ms2_model, ~ ms2.time|proclamation)
pairs(post1)

 
```

#Guilt

```{r}
#ANOVA (time two only)
guilt.afex_time <- aov_car(guilt_2.2 ~ proclamation*order + Error(ID), data= s5)
summary(guilt.afex_time)
anova_apa(guilt.afex_time)
```

#Guilt Descriptives for Main Effect of Proclamation

```{r}
#Cells
tapply(s5$guilt_2.2, 
       list(s5$proclamation, s5$order), 
       FUN = mean)
tapply(s5$guilt_2.2, 
       list(s5$proclamation, s5$order), 
       FUN = sd)
tapply(s5$guilt_2.2, 
       list(s5$proclamation, s5$order), 
       FUN = length)

#Across Proclamation
tapply(s5$guilt_2.2, s5$proclamation,FUN = mean)
tapply(s5$guilt_2.2, s5$proclamation,FUN = sd)
tapply(s5$guilt_2.2, s5$proclamation,FUN = length)

#Across Order
tapply(s5$guilt_2.2, s5$order,FUN = mean)
tapply(s5$guilt_2.2, s5$order,FUN = sd)
tapply(s5$guilt_2.2, s5$order,FUN = length)

#Overall
mean(s5$guilt_2.2)
sd(s5$guilt_2.2)
length(s5$guilt_2.2)

```

#Trust Game

```{r}
#Logistic Regression
model.trust_study5 <- glm(trustbeh ~ proclamation*order, data=s5, family = binomial(link = "logit"))
summary(model.trust_study5)
#1 = pass, 0 = keep

chisq.test(s5$proclamation, s5$trustbeh)
table(s5$proclamation,s5$trustbeh)

#percentages who KEEP
table(s5$proclamation, s5$order, s5$trustbeh)

#absolute survey 1 KEEP - 77, 
#ambiguous survey 1 KEEP - 83
#absolute game 1 KEEP - 69
#aambiguous game 1 KEEP - 81
```

See Study5_mediation.R Rscript for mediation results.
