---
title: "Study3"
author: "Elizabeth Huppert"
date: "5/4/2020"
output: pdf_document
---

#Set-up and Read in Data

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-apa
-psych
-dplyr
-emmeans

```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(afex)
library(apa)
library(psych)
library(dplyr)
library(emmeans)

#read in data

s3 <- read.csv(here("HypocrisyStudy3_cleaned.csv"))

```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


# Models

Key variable names (also see codebook for more information):

1. Proclamation:
Assignment to one of three conditions: "Lying is never [rarely/sometimes] okay" (absolute vs. ambitious vs. flexible)

2. Behavior:
Assignment to "prosocial.truth" vs. "selfish.lie" 

3. Behavlie:
selfish lie = 1, prosocial truth = 0

4. rv:
Decisions to RELY (1) or VERIFY (0) in the RV game

5. Sometimes:
Dummy-coded proclamation variable (sometimes = 1, rarely/never = 0)

6. Rarely:
Dummy-coded proclamation variable (rarley = 1, sometimes/never = 0)

7. Never:
Dummy-coded proclamation variable (never = 1, sometimes/rarely = 0)


Supplemental:

Pref = Attitudes towards honesty; 1-5 statement
("Lying is always [often/sometimes/rarely/never] okay" = 1-5)


#Composite Evaluation Variables

Items with high agreement were combined as per our pre-registration.

```{r}
#Hypocrisy
hypocrisy_3_check  <- data.frame(s3$Hypocrisy_1, s3$Hypocrisy_2, s3$Hypocrisy_3, s3$Hypocrisy_4, s3$Hypocrisy_5)
summary(hypocrisy_3_check)
describe(hypocrisy_3_check)
psych::alpha(hypocrisy_3_check) #alpha = 0.96
s3 <- mutate(s3, Hypocrisy_composite3 = ((s3$Hypocrisy_1 + s3$Hypocrisy_2 + s3$Hypocrisy_3 + s3$Hypocrisy_4 + s3$Hypocrisy_5)/5))
                                            
#Morality
moral_3_check <- data.frame(s3$Moral_1, s3$Moral_2, s3$Moral_3)
summary(moral_3_check)
describe(moral_3_check)
psych::alpha(moral_3_check) #alpha = 0.98
s3 <- mutate(s3, Moral_composite3 = ((s3$Moral_1 + s3$Moral_2 + s3$Moral_3)/3))

#Future Honesty
honest_3_check <- data.frame(s3$Honest_frequency, s3$Honest_likely, s3$Honest_extreme, s3$Honest_committment)
summary(honest_3_check)
describe(honest_3_check)
psych::alpha(honest_3_check) #alpha = 0.92
s3 <- mutate(s3, Honest_composite3 = ((s3$Honest_frequency + s3$Honest_likely + s3$Honest_extreme + s3$Honest_committment)/4))
                                             
#Social Influence
cor.test(s3$Social_benefit1, s3$Social_benefit2) #r = 0.84
s3 <- mutate(s3, SI_composite3 = ((s3$Social_benefit1 + s3$Social_benefit2)/2))

```

Evaluation variables:

Hypocrisy_composite3 = hypocrisy composite of 5 items (Ratings: 1-7)
Moral_composite3 = morality composite of 3 items (Ratings: 1-7)
Honest_composite3 = future honesty composite of 4 items (Ratings: 1-7)
SI_composite3 = social influence composite of 2 items  (Ratings: 1-7)


#Hypocrisy Model

```{r}
#ANOVA
hypocrisy_3.afex <- aov_car(Hypocrisy_composite3 ~ proclamation * behavior + Error(ID), s3)
summary(hypocrisy_3.afex)
anova_apa(hypocrisy_3.afex)

```

#Hypocrisy Descriptives

```{r}
#Cells
tapply(s3$Hypocrisy_composite3, list(s3$proclamation, s3$behavior), mean)
tapply(s3$Hypocrisy_composite3, list(s3$proclamation, s3$behavior), sd)
tapply(s3$Hypocrisy_composite3, list(s3$proclamation, s3$behavior), length)

#Across Proclamation
tapply(s3$Hypocrisy_composite3, s3$proclamation, mean)
tapply(s3$Hypocrisy_composite3, s3$proclamation, sd)
tapply(s3$Hypocrisy_composite3, s3$proclamation, length)

#Across Behavior
tapply(s3$Hypocrisy_composite3, s3$behavior, mean)
tapply(s3$Hypocrisy_composite3, s3$behavior, sd)
tapply(s3$Hypocrisy_composite3, s3$behavior, length)

#Overall
mean(s3$Hypocrisy_composite3)
sd(s3$Hypocrisy_composite3)
length(s3$Hypocrisy_composite3)

```

#Hypocrisy Simple Effects - Subsetting Data

```{r}
#How does behavior vary by proclamation type?
#Subset for main effects tests

never_s3 <- s3 %>%
  filter(proclamation == "never") #201 - never

rarely_s3 <- s3 %>%
  filter(proclamation == "rarely") #197 - rarely

sometimes_s3 <- s3 %>%
  filter(proclamation == "sometimes") #198 - never


#Subset for one level of one factor 

never_exclude_5 <- s3 %>%
  filter(proclamation != "never")  #395, rarely and sometimes

rarely_exclude_5 <- s3 %>%
  filter(proclamation != "rarely") #399, never and sometimes

sometimes_exclude_5 <- s3 %>%
  filter(proclamation != "sometimes") #398, never and rarely


#Selfish lie - rarely vs sometimes
never_lie_5 <- never_exclude_5 %>%
  filter(behavior  == "selfish.lie") #197

#Prosocial truth - rarely vs sometimes
never_truth_5 <- never_exclude_5 %>%
  filter(behavior == "prosocial.truth") #198

#Selfish lie - never vs sometimes
rarely_lie_5 <- rarely_exclude_5 %>%
  filter(behavior == "selfish.lie") #205

#Prosocial truth - never vs sometimes
rarely_truth_5 <- rarely_exclude_5 %>%
  filter(behavior == "prosocial.truth") #194

#Selfish lie - never vs rarely
sometimes_lie_5 <- sometimes_exclude_5 %>%
  filter(behavior == "selfish.lie") #200

#Prosocial truth - never vs rarely
sometimes_truth_5 <- sometimes_exclude_5 %>%
  filter(behavior == "prosocial.truth") #198

```

#Hypocrisy Simple Effects - T-tests

```{r}
#Main effect
#Rarely vs. never
t.test(Hypocrisy_composite3 ~ proclamation, sometimes_exclude_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, sometimes_exclude_5, var.equal = TRUE))

#Never vs. sometimes  
t.test(Hypocrisy_composite3 ~ proclamation, rarely_exclude_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, rarely_exclude_5, var.equal = TRUE))

#Rarely vs. sometimes  
t.test(Hypocrisy_composite3 ~ proclamation, never_exclude_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, never_exclude_5, var.equal = TRUE))


#Within levels of behavior 

#Selfish lie: sometimes vs. rarely
t.test(Hypocrisy_composite3 ~ proclamation, never_lie_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, never_lie_5, var.equal = TRUE))

#Prosocial truth: sometimes vs. rarely
t.test(Hypocrisy_composite3 ~ proclamation, never_truth_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, never_truth_5, var.equal = TRUE))

#Selfish lie: sometimes vs. never
t.test(Hypocrisy_composite3 ~ proclamation, rarely_lie_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, rarely_lie_5, var.equal = TRUE))

#Prosocial truth: sometimes vs. never
t.test(Hypocrisy_composite3 ~ proclamation, rarely_truth_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, rarely_truth_5, var.equal = TRUE))

#Selfish lie: never vs. rarely
t.test(Hypocrisy_composite3 ~ proclamation, sometimes_lie_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, sometimes_lie_5, var.equal = TRUE))

#Prosocial truth never vs. rarely
t.test(Hypocrisy_composite3 ~ proclamation, sometimes_truth_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite3 ~ proclamation, sometimes_truth_5, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
hyp_model = aov_ez('ID', 'Hypocrisy_composite3', s3,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(hyp_model)
cellmeans <- emmeans(hyp_model, ~ proclamation|behavior)
print(cellmeans)
mmeans <- emmeans(hyp_model, ~ proclamation)
print(mmeans)
post1 <- emmeans(hyp_model, ~ proclamation)
pairs(post1)  
post2 <- emmeans(hyp_model, ~ proclamation|behavior)
pairs(post2)  
```

#Morality 

```{r}
#ANOVA
moral_3.afex <- aov_car(Moral_composite3 ~ proclamation * behavior + Error(ID), s3)
summary(moral_3.afex)
anova_apa(moral_3.afex)

```

#Morality Descriptives

```{r}
#Cells
tapply(s3$Moral_composite3, list(s3$proclamation, s3$behavior), mean)
tapply(s3$Moral_composite3, list(s3$proclamation, s3$behavior), sd)
tapply(s3$Moral_composite3, list(s3$proclamation, s3$behavior), length)

#Across Proclamation
tapply(s3$Moral_composite3, s3$proclamation, mean)
tapply(s3$Moral_composite3, s3$proclamation, sd)
tapply(s3$Moral_composite3, s3$proclamation, length)

#Across behavior
tapply(s3$Moral_composite3, s3$behavior, mean)
tapply(s3$Moral_composite3, s3$behavior, sd)
tapply(s3$Moral_composite3, s3$behavior, length)

#Overall
mean(s3$Moral_composite3)
sd(s3$Moral_composite3)
length(s3$Moral_composite3)

```

#Morality Simple Effects

Note: For these tests, use subsetted data from Hypocrisy simple effects test (previous code chunk).


```{r}
#Main Effect
#Never vs. rarely
t.test(Moral_composite3 ~ proclamation, sometimes_exclude_5, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, sometimes_exclude_5, var.equal = TRUE))

#Never vs. sometimes 
t.test(Moral_composite3 ~ proclamation, rarely_exclude_5, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, rarely_exclude_5, var.equal = TRUE))

#Rarely vs. sometimes  
t.test(Moral_composite3 ~ proclamation, never_exclude_5, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, never_exclude_5, var.equal = TRUE))


#Within levels of behaviors 

#Prosocial truth: rarely vs. sometimes
t.test(Moral_composite3 ~ proclamation, never_truth_5, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, never_truth_5, var.equal = TRUE))

#Selfish lie: rarely vs. sometimes
t.test(Moral_composite3 ~ proclamation, never_lie_5, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, never_lie_5, var.equal = TRUE))


#Prosocial truth: never vs. sometimes
t.test(Moral_composite3 ~ proclamation, rarely_truth_5, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, rarely_truth_5, var.equal = TRUE))

#Selfish lie: never vs. sometimes
t.test(Moral_composite3 ~ proclamation, rarely_lie_5, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, rarely_lie_5, var.equal = TRUE))

#Prosocial truth: never vs. rarely
t.test(Moral_composite3 ~ proclamation, sometimes_truth_5, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, sometimes_truth_5, var.equal = TRUE))

#Selfish lie: never vs. rarely
t.test(Moral_composite3 ~ proclamation, sometimes_lie_5, var.equal = TRUE)
t_apa(t.test(Moral_composite3 ~ proclamation, sometimes_lie_5, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
mor_model = aov_ez('ID', 'Moral_composite3', s3,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(mor_model)
cellmeans <- emmeans(mor_model, ~ proclamation|behavior)
print(cellmeans)
mmeans <- emmeans(mor_model, ~ proclamation)
print(mmeans)
post1 <- emmeans(mor_model, ~ proclamation|behavior)
pairs(post1)  
post2 <- emmeans(mor_model, ~ proclamation)
pairs(post2)  
```

#Future Honesty

```{r}
#ANOVA
honesty_3.afex <- aov_car(Honest_composite3 ~ proclamation * behavior + Error(ID), s3)
summary(honesty_3.afex)
anova_apa(honesty_3.afex)
```

#Future Honesty Descriptives

```{r}
#Cells
tapply(s3$Honest_composite3, list(s3$proclamation, s3$behavior), mean)
tapply(s3$Honest_composite3, list(s3$proclamation, s3$behavior), sd)
tapply(s3$Honest_composite3, list(s3$proclamation, s3$behavior), length)

#Across Proclamation
tapply(s3$Honest_composite3, s3$proclamation, mean)
tapply(s3$Honest_composite3, s3$proclamation, sd)
tapply(s3$Honest_composite3, s3$proclamation, length)

#Across Behavior
tapply(s3$Honest_composite3, s3$behavior, mean)
tapply(s3$Honest_composite3, s3$behavior, sd)
tapply(s3$Honest_composite3, s3$behavior, length)

#Overall
mean(s3$Honest_composite3)
sd(s3$Honest_composite3)
length(s3$Honest_composite3)

```

#Future Honesty Simple Effects

Note: For these tests, use subsetted data from Hypocrisy simple effects test (previous code chunk).


```{r}
#Main Effect
#Never vs. rarely
t.test(Honest_composite3  ~ proclamation, sometimes_exclude_5, var.equal = TRUE)
t_apa(t.test(Honest_composite3  ~ proclamation, sometimes_exclude_5, var.equal = TRUE))

#Never vs. sometimes  
t.test(Honest_composite3  ~ proclamation, rarely_exclude_5, var.equal = TRUE)
t_apa(t.test(Honest_composite3  ~ proclamation, rarely_exclude_5, var.equal = TRUE))

#Rarely  vs. sometimes 
t.test(Honest_composite3 ~ proclamation, never_exclude_5, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, never_exclude_5, var.equal = TRUE))

#Within levels of behavior 

#Prosocial truth: rarely vs. sometimes
t.test(Honest_composite3  ~ proclamation, never_truth_5, var.equal = TRUE)
t_apa(t.test(Honest_composite3  ~ proclamation, never_truth_5, var.equal = TRUE))

#Selfish lie: rarely vs. sometimes
t.test(Honest_composite3  ~ proclamation, never_lie_5, var.equal = TRUE)
t_apa(t.test(Honest_composite3  ~ proclamation, never_lie_5, var.equal = TRUE))

#Prosocial truth: never vs. sometimes
t.test(Honest_composite3  ~ proclamation, rarely_truth_5, var.equal = TRUE)
t_apa(t.test(Honest_composite3  ~ proclamation, rarely_truth_5, var.equal = TRUE))

#Selfish lie: never vs. sometimes
t.test(Honest_composite3  ~ proclamation, rarely_lie_5, var.equal = TRUE)
t_apa(t.test(Honest_composite3  ~ proclamation, rarely_lie_5, var.equal = TRUE))

#Prosocial truth: never vs. rarely
t.test(Honest_composite3 ~ proclamation, sometimes_truth_5, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, sometimes_truth_5, var.equal = TRUE))

#Selfish lie: never vs. rarely
t.test(Honest_composite3 ~ proclamation, sometimes_lie_5, var.equal = TRUE)
t_apa(t.test(Honest_composite3 ~ proclamation, sometimes_lie_5, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
hon_model = aov_ez('ID', 'Honest_composite3', s3,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(hon_model)
cellmeans <- emmeans(hon_model, ~ proclamation|behavior)
print(cellmeans)
mmeans <- emmeans(hon_model, ~ proclamation)
print(mmeans)
post1 <- emmeans(hon_model, ~ proclamation|behavior)
pairs(post1)  
post2 <- emmeans(hon_model, ~ proclamation)
pairs(post2)  
```

#Social Influence

```{r}
#ANOVA
SI.afex <- aov_car(SI_composite3 ~ proclamation * behavior + Error(ID), s3)
summary(SI.afex )
anova_apa(SI.afex)
```

#Descriptives for Social Influence

```{r}
#Cells
tapply(s3$SI_composite3, list(s3$proclamation, s3$behavior), mean)
tapply(s3$SI_composite3, list(s3$proclamation, s3$behavior), sd)
tapply(s3$SI_composite3, list(s3$proclamation, s3$behavior), length)

#Across Proclamation
tapply(s3$SI_composite3, s3$proclamation, mean)
tapply(s3$SI_composite3, s3$proclamation, sd)
tapply(s3$SI_composite3, s3$proclamation, length)

#Across Behavior
tapply(s3$SI_composite3, s3$behavior, mean)
tapply(s3$SI_composite3, s3$behavior, sd)
tapply(s3$SI_composite3, s3$behavior, length)

#Overall
mean(s3$SI_composite3)
sd(s3$SI_composite3)
length(s3$SI_composite3)

```

#Social Benefit Simple Effects 

Note: For these tests, use subsetted data from Hypocrisy simple effects test (previous code chunk).


```{r}
#Proclamation within subsetted data
#Never vs. rarely
t.test(SI_composite3  ~ proclamation, sometimes_exclude_5, var.equal = TRUE)
t_apa(t.test(SI_composite3  ~ proclamation, sometimes_exclude_5, var.equal = TRUE))

#Never vs. sometimes  
t.test(SI_composite3  ~ proclamation, rarely_exclude_5, var.equal = TRUE)
t_apa(t.test(SI_composite3  ~ proclamation, rarely_exclude_5, var.equal = TRUE))

#Rarely vs. sometimes 
t.test(SI_composite3 ~ proclamation, never_exclude_5, var.equal = TRUE)
t_apa(t.test(SI_composite3 ~ proclamation, never_exclude_5, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
SI_model = aov_ez('ID', 'SI_composite3', s3,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(SI_model)
means <- emmeans(SI_model, ~ proclamation)
print(means)
post1 <- emmeans(SI_model, ~ proclamation)
pairs(post1)  

```

#Behavior in the RELY-or-VERIFY game

```{r}
#Reported Model
rv_3.glm <- glm(rv ~ sometimes + rarely + behavlie 
                + sometimes*behavlie + rarely*behavlie, 
                data=s3, family = binomial(link = "logit"))
summary(rv_3.glm) 

#Exploratory
rv.glm3_2 <- glm(rv ~ never + rarely + behavlie + 
                never*behavlie + rarely*behavlie,
              data=s3, family = binomial(link = "logit"))
summary(rv.glm3_2)



#Frequencies - proclamation
table(s3$proclamation, s3$rv) 

#never rely:  95/201, 47%
#rarely rely: 83/197, 42%
#sometimes rely: 61/198, 31%


#never 106/201 verify, 53%
#rarely 114/197  verify, 58%
#sometimes 137/198 verify, 69%

#Frequencies proclamation and behavior by cell
table(s3$proclamation, s3$behavior, s3$rv)
table(s3$behavior, s3$rv) 

#178 prosocial rely, 117 verify - 178/295; 60%
#61 selfish rely, 240 selfish verify - 61/01 - 20%

```

#Attitudes Towards Honesty Measure

#Distribution of Responses

```{r}
#Distributions

table(s3$pref)
#109 "never" (5) / 596, 18%
#330 "rarely" (4) / 596, 55%
#144 "sometimes" (3) / 596, 24%
#9 "often" (2) 
#4 "always" (1)

```


#Center honesty preferences for use in models

```{r}
s3 <- mutate(s3, pref.center = scale(s3$pref))

```

# SI Appendix 3 - Regressions

```{r}
#Preferences Regression - Hypocrisy
hypocrisy_2.lm <- lm(Hypocrisy_composite3 ~ sometimes + rarely + sometimes*pref.center + rarely*pref.center, data= s3)
summary(hypocrisy_2.lm )

#Look at mean hypocrisy ratings by proclamation and preferences 
tapply(s3$Hypocrisy_composite3, list(s3$proclamation, s3$pref), mean)
tapply(s3$Hypocrisy_composite3, list(s3$sometimes, s3$pref), mean)
tapply(s3$Hypocrisy_composite3, s3$rarely, mean)
tapply(s3$Hypocrisy_composite3, s3$sometimes, mean)
tapply(s3$Hypocrisy_composite3, s3$sometimes, sd)

#Preferences Regression - Morality
moral_2.lm <- lm(Moral_composite3 ~ sometimes + rarely + sometimes*pref.center + rarely*pref.center, data= s3)
summary(moral_2.lm)

#Look at mean morality ratings by proclamation and preferences 
tapply(s3$Moral_composite3, list(s3$proclamation, s3$pref), mean)
tapply(s3$Moral_composite3, list(s3$sometimes, s3$pref), mean)
tapply(s3$Moral_composite3, s3$proclamation, mean)
tapply(s3$Moral_composite3, s3$sometimes, mean)
tapply(s3$Moral_composite3, s3$sometimes, sd)


#Preferences Regression - Future Honesty
honest_2.lm <- lm(Honest_composite3 ~ sometimes + rarely + sometimes*pref.center + rarely*pref.center, data= s3)
summary(honest_2.lm)

#Look at mean future honesty ratings by proclamation and preferences 
tapply(s3$Honest_composite3, list(s3$proclamation, s3$pref), mean)
tapply(s3$Honest_composite3, list(s3$sometimes, s3$pref), mean)
tapply(s3$Honest_composite3, s3$proclamation, mean)
tapply(s3$Honest_composite3, s3$sometimes, mean)


#Preferences Regression - SI
SI.lm <- lm(SI_composite3 ~ sometimes + rarely + sometimes*pref.center + rarely*pref.center, data= s3)
summary(SI.lm )

#Look at mean SI ratings by proclamation and preferences 
tapply(s3$SI_composite3, list(s3$proclamation, s3$pref), mean)
tapply(s3$SI_composite3, s3$sometimes, mean)
tapply(s3$SI_composite3, s3$sometimes, sd)


#Logistic Regression (trust) with own attitudes towards honesty
rv3.3.glm <- glm(rv ~ sometimes*pref.center,
              data=s3, family = binomial(link = "logit"))
summary(rv3.3.glm) 

#Frequencies
table(s3$rv, s3$pref, s3$sometimes)
#note that separate tables 0 = never/rarely , 1 = sometimes; within tables, 0 = verify, 1 = rely
#total per cell
table(s3$pref)

#Percentages RELY on never/rarely
#always 2/4, 50%
#often, 2/9 22%
#sometimes, 23/144 16%
#rarely, 107/330 32%
#never, 44/109, 40%

#Percentages RELY on sometimes
#always 0/4, 0%
#often, 1/9 11%
#sometimes, 26/144 18%
#rarely, 30/330 9%
#never, 4/109 4%



```

#Attitudes as a Covariate - exploration

```{r}
#Preferences Covariate - Hypocrisy
Hypocrisy3.pref.center <- aov_car(Hypocrisy_composite3 ~ proclamation * behavior + pref.center + Error(ID), s3, factorize = FALSE, anova_table = list(es = "pes"))
summary(Hypocrisy3.pref.center)

#Preferences Covariate- Morality
Moral3.pref.center <- aov_car(Moral_composite3 ~ proclamation * behavior + pref.center + Error(ID), s3, factorize = FALSE, anova_table = list(es = "pes"))
summary(Moral3.pref.center)

#Preferences Covariate - Future honesty
honest3.pref.center <- aov_car(Honest_composite3 ~ proclamation * behavior + pref.center + Error(ID), s3, factorize = FALSE, anova_table = list(es = "pes"))
summary(honest3.pref.center)

#Preferences Covariate - SI
SI.pref.center <- aov_car(SI_composite3 ~ proclamation * behavior + pref.center + Error(ID), s3, factorize = FALSE, anova_table = list(es = "pes"))
summary(SI.pref.center)

```

#Notes

The moderated mediation models on moral character and trust behavior were conducted in SPSS. The syntax is copied below for use within SPSS.

# Syntax

Study 3 Trust: First, Open "HypocrisyStudy3_cleaned.xlsx" within SPSS. This excel file is available in this R project and on the OSF page for this project. Then run the code below.

*1. Recreate composite variables*

COMPUTE Hypocrisy_C=MEAN(Hypocrisy_1,Hypocrisy_2,Hypocrisy_3,Hypocrisy_4,Hypocrisy_5).
EXECUTE.

COMPUTE Honesty_C=MEAN(Honest_frequency,Honest_likely,Honest_extreme,Honest_committment).
EXECUTE.

COMPUTE SocBen_C=MEAN(Social_benefit1, Social_benefit2).
EXECUTE.

*2. Run mediation analysis to get indirect effects. - use point and click within Process Macro*

*Run Hayes’ (2016) PROCESS Macro for SPSS, Model 7, 10,000 bootstraps*
IV = sometimes
M1 = Honesty_C
M2 = Hypocrisy_C
M3 = SocBen_C
Y = rv
W = behavlie

*3. Run regressions to get X-->M and M-->Y pathways for each level of moderator.*

SORT CASES  BY behavlie.
SPLIT FILE LAYERED BY behavlie.

*Test M-->Y pathways*

LOGISTIC REGRESSION VARIABLES rv
  /METHOD=ENTER Hypocrisy_C Honesty_C sometimes  SocBen_C
  /CRITERIA=PIN(.05) POUT(.10) ITERATE(20) CUT(.5).


*Test X-->M1 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Honesty_C
  /METHOD=ENTER sometimes.

*Test X-->M2 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Hypocrisy_C
  /METHOD=ENTER sometimes.


*Test X-->M3 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT  SocBen_C
  /METHOD=ENTER sometimes.
  
Study 3 Morality: Use the same data file in SPSS.

*1. Recreate composite variables*

COMPUTE Hypocrisy_C=MEAN(Hypocrisy_1,Hypocrisy_2,Hypocrisy_3,Hypocrisy_4,Hypocrisy_5).
EXECUTE.

COMPUTE Honesty_C=MEAN(Honest_frequency,Honest_likely,Honest_extreme,Honest_committment).
EXECUTE.

COMPUTE SocBen_C=MEAN(Social_benefit1, Social_benefit2).
EXECUTE.

COMPUTE Moral_C=MEAN(Moral_1, Moral_2, Moral_3).
EXECUTE.

*2. Run mediation analysis to get indirect effects. - use point and click within Process Macro*

*Run Hayes’ (2016) PROCESS Macro for SPSS, Model 7, 10,000 bootstraps*
X = sometimes
M1 = Hypocrisy_C
M2 = Honesty_C
M3 = SocBen_C
Y = Moral_C
W = behavlie

*3. Run regressions to get X-->M and M-->Y pathways for each level of moderator.*

SORT CASES  BY behavlie.
SPLIT FILE LAYERED BY behavlie.

*Test M-->Y pathways*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Moral_C
  /METHOD=ENTER Hypocrisy_C Honesty_C sometimes  SocBen_C.

*Test X-->M1 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Hypocrisy_C
  /METHOD=ENTER sometimes.

*Test X-->M2 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Honesty_C
  /METHOD=ENTER sometimes.


*Test X-->M3 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT  SocBen_C
  /METHOD=ENTER sometimes.
  
  
