---
title: "StudySI4"
author: "Elizabeth Huppert"
date: "1/18/2021"
output: html_document
---

#Set-up and Read in Data

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-apa
-psych
-dplyr
-emmeans


```{r setup, include=FALSE}

library(here)
library(tidyverse)
library(afex)
library(apa)
library(psych)
library(dplyr)
library(emmeans)

#read in data

s9 <- read.csv(here("HypocrisyStudySI_4.csv")) #433

```


Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


# Models

Key variable names (also see codebook for more information):

1. Proclamation:
Assignment to absolute vs. flexible honesty stance vs. control

2. Advisor 
Assignment to no advisor prep for the interview vs. political advisor prep for the interview.

3. vote = Likelihood of voting for Matthew Johnson 

4. d1 = Perceived lying behavior

5. g1 = Honesty ideals

6. imm = Perceived immorality of lying generally (not specific to Matthew Johnson)

# Composite DVs

Look at agreement with hypocrisy and morality.


```{r}
#Hypocrisy
hypocrisy9_check.df <- data.frame(s9$h1, s9$h2, s9$h3, s9$h4, s9$h5)
summary(hypocrisy9_check.df )
psych::alpha(hypocrisy9_check.df ) #alpha = 0.89
s9<-  mutate(s9, 
              Hypocrisy_composite9 = ((s9$h1 + s9$h2 + s9$h3 + s9$h4+ s9$h4)/5))

#Morality
moral9.check.df <- data.frame(s9$m1, s9$m2, s9$m3)
summary(moral9.check.df)
psych::alpha(moral9.check.df) #alpha = 0.96
s9 <- mutate(s9, 
             Moral_composite9 = ((s9$m1 + s9$m2 + s9$m3)/3))

```

# Models 

Exclude Control Condition from 2 x 2 Anovas

```{r}
#Eliminate control from this 2 x 2 ANOVA
s9_no_control <- s9%>%
  filter(proclamation != "control")%>%
  droplevels()
```

# Voting Intentions

```{r}
#ANOVA
vote9.afex <-aov_car(vote ~ proclamation*advisor + Error(ID), data=s9_no_control)
summary(vote9.afex) 
anova_apa(vote9.afex)
```

#Voting Intentions - Descriptives

```{r}
#Across Proclamation*Advisor
tapply(s9_no_control$vote, list(s9_no_control$proclamation, s9_no_control$advisor), mean)
tapply(s9_no_control$vote, list(s9_no_control$proclamation, s9_no_control$advisor), sd)
tapply(s9_no_control$vote, list(s9_no_control$proclamation, s9_no_control$advisor), length)

#Across Proclamations
tapply(s9_no_control$vote, s9_no_control$proclamation, mean)
tapply(s9_no_control$vote, s9_no_control$proclamation, sd)
tapply(s9_no_control$vote, s9_no_control$proclamation, length)

#Across Advisor
tapply(s9_no_control$vote, s9_no_control$advisor, mean)
tapply(s9_no_control$vote, s9_no_control$advisor, sd)
tapply(s9_no_control$vote, s9_no_control$advisor, length)
```

# Hypocrisy

```{r}
#ANOVA
hypocrisy9.afex <-aov_car(Hypocrisy_composite9 ~ proclamation*advisor + Error(ID), data=s9_no_control)
summary(hypocrisy9.afex) 
anova_apa(hypocrisy9.afex)
```

# Hypocrisy - Descriptives

```{r}
#Across Proclamation*Advisor
tapply(s9_no_control$Hypocrisy_composite9, list(s9_no_control$proclamation, s9_no_control$advisor), mean)
tapply(s9_no_control$Hypocrisy_composite9, list(s9_no_control$proclamation, s9_no_control$advisor), sd)
tapply(s9_no_control$Hypocrisy_composite9, list(s9_no_control$proclamation, s9_no_control$advisor), length)

#Across Proclamations
tapply(s9_no_control$Hypocrisy_composite9, s9_no_control$proclamation, mean)
tapply(s9_no_control$Hypocrisy_composite9, s9_no_control$proclamation, sd)
tapply(s9_no_control$Hypocrisy_composite9, s9_no_control$proclamation, length)

#Across Advisor
tapply(s9_no_control$Hypocrisy_composite9, s9_no_control$advisor, mean)
tapply(s9_no_control$Hypocrisy_composite9, s9_no_control$advisor, sd)
tapply(s9_no_control$Hypocrisy_composite9, s9_no_control$advisor, length)
```

# Morality

```{r}
#ANOVA
morality9.afex <-aov_car(Moral_composite9 ~ proclamation*advisor + Error(ID), data=s9_no_control)
summary(morality9.afex)
anova_apa(morality9.afex )
```

# Moral Descriptives

```{r}
#Across Proclamation*Advisor
tapply(s9_no_control$Moral_composite9, list(s9_no_control$proclamation, s9_no_control$advisor), mean)
tapply(s9_no_control$Moral_composite9, list(s9_no_control$proclamation, s9_no_control$advisor), sd)
tapply(s9_no_control$Moral_composite9, list(s9_no_control$proclamation, s9_no_control$advisor), length)

#Across Proclamations
tapply(s9_no_control$Moral_composite9, s9_no_control$proclamation, mean)
tapply(s9_no_control$Moral_composite9, s9_no_control$proclamation, sd)
tapply(s9_no_control$Moral_composite9, s9_no_control$proclamation, length)

#Across Advisor
tapply(s9_no_control$Moral_composite9, s9_no_control$advisor, mean)
tapply(s9_no_control$Moral_composite9, s9_no_control$advisor, sd)
tapply(s9_no_control$Moral_composite9, s9_no_control$advisor, length)
```

# Lying Behavior

```{r}
#ANOVA
liebehavior9.afex <-aov_car(d1 ~ proclamation*advisor + Error(ID), data=s9_no_control)
summary(liebehavior9.afex )
anova_apa(liebehavior9.afex )
```

# Lying Behavior - Descriptives

```{r}
#Across Proclamation*Advisor
tapply(s9_no_control$d1, list(s9_no_control$proclamation, s9_no_control$advisor), mean)
tapply(s9_no_control$d1, list(s9_no_control$proclamation, s9_no_control$advisor), sd)
tapply(s9_no_control$d1, list(s9_no_control$proclamation, s9_no_control$advisor), length)

#Across Proclamations
tapply(s9_no_control$d1, s9_no_control$proclamation, mean)
tapply(s9_no_control$d1, s9_no_control$proclamation, sd)
tapply(s9_no_control$d1, s9_no_control$proclamation, length)

#Across Advisor
tapply(s9_no_control$d1, s9_no_control$advisor, mean)
tapply(s9_no_control$d1, s9_no_control$advisor, sd)
tapply(s9_no_control$d1, s9_no_control$advisor, length)
```

# Honesty Ideals

```{r}
#ANOVA
intentions9.afex <-aov_car(g1 ~ proclamation*advisor + Error(ID), data=s9_no_control)
summary(intentions9.afex)
anova_apa(intentions9.afex)
```

# Honesty Ideals _ Descriptives

```{r}
#Across Proclamation*Advisor
tapply(s9_no_control$g1, list(s9_no_control$proclamation, s9_no_control$advisor), mean)
tapply(s9_no_control$g1, list(s9_no_control$proclamation, s9_no_control$advisor), sd)
tapply(s9_no_control$g1, list(s9_no_control$proclamation, s9_no_control$advisor), length)

#Across Proclamations
tapply(s9_no_control$g1, s9_no_control$proclamation, mean)
tapply(s9_no_control$g1, s9_no_control$proclamation, sd)
tapply(s9_no_control$g1, s9_no_control$proclamation, length)

#Across Advisor
tapply(s9_no_control$g1, s9_no_control$advisor, mean)
tapply(s9_no_control$g1, s9_no_control$advisor, sd)
tapply(s9_no_control$g1, s9_no_control$advisor, length)
```

#Examination of the Control Condition

```{r}
#Moral rating by proc type
tapply(s9$Moral_composite, s9$proclamation, FUN = mean)
tapply(s9$Moral_composite, s9$proclamation, FUN = sd)


#Moral ratings by proclamation within just no advisor type
no_advisor_df <- s9 %>%
  filter(advisor == "no") %>%
  droplevels()
tapply(no_advisor_df$Moral_composite, no_advisor_df$proclamation, FUN = mean)

#Compare moral ratings of candidates who make the abs to flex proc
t.test(Moral_composite9  ~ proclamation, s9_no_control, var.equal = TRUE)
t_apa(t.test(Moral_composite9  ~ proclamation, s9_no_control, var.equal = TRUE)) # abs v flex significant

#Compare moral ratings of candidates who make the abs to flex with no advisor prep
s9_no_control2 <- no_advisor_df  %>%
   filter(proclamation != "control")%>%
  droplevels()

#Compare moral ratings of candidates who make the abs to flex proc
t.test(Moral_composite9  ~ proclamation, s9_no_control2, var.equal = TRUE)
t_apa(t.test(Moral_composite9  ~ proclamation, s9_no_control2, var.equal = TRUE)) # abs v flex significant


#Compare moral ratings of candidate who make the flex proc to control
s9_no_abs<- s9 %>%
   filter(proclamation != "absolute")%>%
  droplevels()

t.test(Moral_composite9  ~ proclamation, s9_no_abs, var.equal = TRUE)
t_apa(t.test(Moral_composite9  ~ proclamation, s9_no_abs, var.equal = TRUE)) # abs v flex significant

#Aagin no advisor prep flex vs. control
s9_no_abs2 <- no_advisor_df %>%
   filter(proclamation != "absolute")%>%
  droplevels()

t.test(Moral_composite9  ~ proclamation, s9_no_abs2, var.equal = TRUE)
t_apa(t.test(Moral_composite9  ~ proclamation, s9_no_abs2, var.equal = TRUE)) # abs v flex significant


#Compare moral ratings of candidate who makes the abs proc to control
s9_no_flex <- s9 %>%
   filter(proclamation != "flexible")%>%
  droplevels()

t.test(Moral_composite9  ~ proclamation, s9_no_flex, var.equal = TRUE)
t_apa(t.test(Moral_composite9  ~ proclamation, s9_no_flex, var.equal = TRUE)) # abs v flex significant

#Again no advisor, abs vs. control
s9_no_flex2 <- no_advisor_df %>%
   filter(proclamation != "flexible")%>%
  droplevels()

t.test(Moral_composite9  ~ proclamation, s9_no_flex2, var.equal = TRUE)
t_apa(t.test(Moral_composite9  ~ proclamation, s9_no_flex2, var.equal = TRUE)) # abs v flex significant


#moral by proc and advisor
tapply(s9$Moral_composite9, list(s9$proclamation, s9$advisor), FUN = mean)
```

# Perceived Immorality

```{r}
#Does perceived immorality predict moral ratings?
#ANOVA
imm.afex <-aov_car(Moral_composite9 ~ imm*proclamation + Error(ID), data=s9_no_control)
summary(imm.afex) 
anova_apa(imm.afex) 

tapply(s9$Moral_composite9, list(s9$imm, s9$proclamation), FUN = mean)
#bar graph
ggplot(data = s9_no_control) +
geom_smooth(mapping = aes(x = imm, y = Moral_composite9, color = proclamation))

```

