---
title: "Supplemental Study 3 (Study 8)"
author: "Elizabeth Huppert"
date: "5/4/2020"
output: pdf_document
---



#Set-up and Read in Data

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-reshape2
-psych
-dplyr
-apa

```{r setup, include = FALSE}

library(here)
library(tidyverse)
library(afex)
library(apa)
library(reshape2)
library(psych)
library(dplyr)

#read in data

s9 <- read.csv(here("HypocrisyStudySI_3.csv"))

```


Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


# Models

Key Variable Names (also see codebook for more information):

1. Proclamation: 
Assignment to absolute vs. flexible honesty stance

2. Lie Amount:
Assignment to a single lie vs. repeated lie 

3. Discounting_1:
Perceived lying frequency (Options: Never, Rarely, Sometimes, Often, Always)
(discounting_2/goal_2 are the same variables at time two after the lie is revealed)

4. Goal_1:
Honesty ideals (Options: Never, Rarely, Sometimes, Often, Always)
(discounting_2/goal_2 are the same variables at time two after the lie is revealed)

# Factorize Subject (ID)

```{r}
s9$ID <- as.factor(s9$ID)
```


# Composite Evaluation Variables

Items with high agreement were combined as per our pre-registration.

```{r}
#Hypocrisy
hypocrisySI3_df <- data.frame(s9$hypocrisy_1, s9$hypocrisy_2, s9$hypocrisy_3, s9$hypocrisy_4)
summary(hypocrisySI3_df)
describe(hypocrisySI3_df)
psych::alpha(hypocrisySI3_df) #alpha = 0.86
s9 <- mutate(s9, HypocrisySI3_composite  = ((s9$hypocrisy_1 + s9$hypocrisy_2 + s9$hypocrisy_3 + s9$hypocrisy_4)/4))

#Morality
moralSI3_df <- data.frame(s9$moral_1, s9$moral_2, s9$moral_3)
summary(moralSI3_df)
describe(moralSI3_df)
psych::alpha(moralSI3_df) #alpha = 0.94
s9 <- mutate(s9, MoralSI3_composite  = ((s9$moral_1 + s9$moral_2 + s9$moral_3)/3))

```

Evaluation variables:

HypocrisySI3_composite  = hypocrisy composite of 4 items (Ratings: 1-7)
MoralSI3_composite = morality composite of 3 items (Ratings: 1-7)


# Hypocrisy Model

```{r pressure, echo=FALSE}
#ANOVA
hypocrisy_8.afex <- aov_car(HypocrisySI3_composite ~ proclamation * lie + Error(ID), s9)
summary(hypocrisy_8.afex)
anova_apa(hypocrisy_8.afex)
```


# Hypocrisy Descriptives

```{r}
#Cells
tapply(s9$HypocrisySI3_composite, list(s9$proclamation, s9$lie), mean)
tapply(s9$HypocrisySI3_composite, list(s9$proclamation, s9$lie), sd)
tapply(s9$HypocrisySI3_composite, list(s9$proclamation, s9$lie), length)

#Across Proclamation
tapply(s9$HypocrisySI3_composite, s9$proclamation, mean)
tapply(s9$HypocrisySI3_composite, s9$proclamation, sd)
tapply(s9$HypocrisySI3_composite, s9$proclamation, length)

#Across Lie Amount
tapply(s9$HypocrisySI3_composite, s9$lie, mean)
tapply(s9$HypocrisySI3_composite, s9$lie, sd)
tapply(s9$HypocrisySI3_composite, s9$lie, length)

#Overall
mean(s9$HypocrisySI3_composite)
sd(s9$HypocrisySI3_composite)
length(s9$HypocrisySI3_composite)
```

#Morality Model

```{r}
#ANOVA
moral_8.afex <- aov_car(MoralSI3_composite ~ proclamation * lie + Error(ID), s9)
summary(moral_8.afex)
anova_apa(moral_8.afex)
```

#Morality Descriptives

```{r}
#Cells
tapply(s9$MoralSI3_composite, list(s9$proclamation, s9$lie), mean)
tapply(s9$MoralSI3_composite, list(s9$proclamation, s9$lie), sd)
tapply(s9$MoralSI3_composite, list(s9$proclamation, s9$lie), length)

#Across Proclamation
tapply(s9$MoralSI3_composite, s9$proclamation, mean)
tapply(s9$MoralSI3_composite, s9$proclamation, sd)
tapply(s9$MoralSI3_composite, s9$proclamation, length)

#Across Lie Amount
tapply(s9$MoralSI3_composite, s9$lie, mean)
tapply(s9$MoralSI3_composite, s9$lie, sd)
tapply(s9$MoralSI3_composite, s9$lie, length)

#Overall
mean(s9$MoralSI3_composite)
sd(s9$MoralSI3_composite)
length(s9$MoralSI3_composite)
```

# Perceived Lying Frequency (Discounting) Model

# Between-subjects ANOVA at Each Time Point

```{r}
#Time one ANOVA
discounting_1.afex <- aov_car(discounting_1 ~ proclamation * lie + Error(ID), s9)
summary(discounting_1.afex)
anova_apa(discounting_1.afex)
#1 = never, 5 = always 

#Time two ANOVA
discounting_2.afex <- aov_car(discounting_2 ~ proclamation * lie + Error(ID), s9)
summary(discounting_2.afex)
anova_apa(discounting_2.afex)

```

# Frequencies - Perceived Lying Frequency  / Discounting

```{r}
#Time one
table(s9$discounting_1, s9$proclamation) 

#Absolute (299)
#36 never - 12%
#150 rarely - 50%
#105 sometimes - 35%

#Flexible (291)
#196 sometimes - 67%
#52 often - 18%

#Time two 
table(s9$discounting_2, s9$proclamation) 

#Absolute  (299)
#152 sometimes -51%
#102 often - 34%

#Flexible (291)
#140 sometimes - 48%
#132 often - 25% 

```

# Perceived Lying Frequency  / Discounting Descriptives

```{r}
#Time 1 - main effect of proclamtion

#Across Proclamation
tapply(s9$discounting_1, s9$proclamation, mean)
tapply(s9$discounting_1, s9$proclamation, sd)
tapply(s9$discounting_1, s9$proclamation, length)

#Time 2 - main effect of proclamation and lie amount

#Across Proclamation
tapply(s9$discounting_2, s9$proclamation, mean)
tapply(s9$discounting_2, s9$proclamation, sd)
tapply(s9$discounting_2, s9$proclamation, length)

#Across Lie Amount
tapply(s9$discounting_2, s9$lie, mean)
tapply(s9$discounting_2, s9$lie, sd)
tapply(s9$discounting_2, s9$lie, length)

```

#Within subjects mixed anova and descriptives across time for perceived lying frequency / discounting

```{r}
#Perceived lying frequency / Discounting  Dataframe
s9_discounting <-melt(s9, 
                id.vars=c("lie", "ID", "proclamation"),
                #measure command is for the DV
                measure.vars=c("discounting_1","discounting_2"),
                variable.name="discount.time",
                value.name="discount.value"
)

#ANOVA
discount_time.afex <- aov_car(
  discount.value ~ proclamation*lie*discount.time + Error(ID/discount.time),
  data=s9_discounting)
summary(discount_time.afex)
anova_apa(discount_time.afex)


#Descriptives 
#Cells
tapply(s9_discounting$discount.value, 
       list(s9_discounting$proclamation, s9_discounting$lie, s9_discounting$discount.time), 
       FUN = mean)

tapply(s9_discounting$discount.value, 
       list(s9_discounting$proclamation, s9_discounting$lie, s9_discounting$discount.time), 
       FUN = sd)

tapply(s9_discounting$discount.value, 
       list(s9_discounting$proclamation, s9_discounting$lie, s9_discounting$discount.time), 
       FUN = length)

#Across Proclamation and Time
tapply(s9_discounting$discount.value, list(s9_discounting$proclamation, s9_discounting$discount.time), mean)
tapply(s9_discounting$discount.value, list(s9_discounting$proclamation, s9_discounting$discount.time), sd)
tapply(s9_discounting$discount.value, list(s9_discounting$proclamation, s9_discounting$discount.time), length)

#Across Lie Amount and Time
tapply(s9_discounting$discount.value, list(s9_discounting$lie, s9_discounting$discount.time), mean)
tapply(s9_discounting$discount.value, list(s9_discounting$lie, s9_discounting$discount.time), sd)
tapply(s9_discounting$discount.value, list(s9_discounting$lie, s9_discounting$discount.time), length)

#Across Proclamation
tapply(s9_discounting$discount.value, s9_discounting$proclamation, mean)
tapply(s9_discounting$discount.value, s9_discounting$proclamation, sd)
tapply(s9_discounting$discount.value, s9_discounting$proclamation, length)

#Across Lie Amount
tapply(s9_discounting$discount.value, s9_discounting$lie, mean)
tapply(s9_discounting$discount.value, s9_discounting$lie, sd)
tapply(s9_discounting$discount.value, s9_discounting$lie, length)

#Aross Time
tapply(s9_discounting$discount.value, s9_discounting$discount.time, mean)
tapply(s9_discounting$discount.value, s9_discounting$discount.time, sd)
tapply(s9_discounting$discount.value, s9_discounting$discount.time, length)

```

#Difference in absolute v flexible just within repeat liars at time two

```{r}
#Effect of proclamation just within multiple liars only at time two
proc_multiplelies <- s9_discounting %>%
  filter(lie == "repeat") #N = 588

proc_multiplelies_time2 <- proc_multiplelies %>%
  filter(discount.time == "discounting_2") 


t.test(discount.value ~ proclamation, data = proc_multiplelies_time2, var.equal = TRUE)
t_apa(t.test(discount.value ~ proclamation, data = proc_multiplelies_time2, var.equal = TRUE))


```


# Honesty Ideals (Goals) Model

# Between-subjects ANOVA at Each Time Point and Descriptives

```{r}
#Time one ANOVA
goal_1.afex <- aov_car(goal_1 ~ proclamation * lie + Error(ID), s9)
summary(goal_1.afex )
anova_apa(goal_1.afex )

#Across Proclamation
tapply(s9$goal_1, s9$proclamation, mean)
tapply(s9$goal_1, s9$proclamation, sd)
tapply(s9$goal_1, s9$proclamation, length)

#Time two ANOVA
goal_2.afex <- aov_car(goal_2 ~ proclamation * lie + Error(ID), s9)
summary(goal_2.afex)
anova_apa(goal_2.afex)

#Across Proclamation
tapply(s9$goal_2, s9$proclamation, mean)
tapply(s9$goal_2, s9$proclamation, sd)
tapply(s9$goal_2, s9$proclamation, length)

#Across Lie Amount
tapply(s9$goal_2, s9$lie, mean)
tapply(s9$goal_2, s9$lie, sd)
tapply(s9$goal_2, s9$lie, length)

```

# Frequencies - Honesty Ideals

```{r}
#Time one
table(s9$goal_1, s9$proclamation) 

#Absolute (299)
#164 never - 55%
#96 rarely - 32%

#Flexible (291)
#224 sometimes - 77%

#Time two
table(s9$goal_2, s9$proclamation) 

#Absolute (299)
#25 never - 88%
#153 sometimes - 52%

#Flexible (291)
#151 sometimes - 52%
#116 often - 40%

```


# Within subjects mixed anova and descriptives across time for honesty ideals

```{r}
#Dataframe for Honesty Ideals
s9_goals <-melt(s9, 
                id.vars=c("lie", "ID", "proclamation"),
                #measure command is for the DV
                measure.vars=c("goal_1","goal_2"),
                variable.name="goal.time",
                value.name="goal.value"
)


#ANOVA
goals_time.afex <- aov_car(
  goal.value ~ proclamation*lie*goal.time + Error(ID/goal.time),
  data=s9_goals)
summary(goals_time.afex)
anova_apa(goals_time.afex)

#Descriptives
#Cells
tapply(s9_goals$goal.value, 
       list(s9_goals$proclamation, s9_goals$lie, s9_goals$goal.time), 
       FUN = mean)

tapply(s9_goals$goal.value, 
       list(s9_goals$proclamation, s9_goals$lie, s9_goals$goal.time), 
       FUN = sd)

tapply(s9_goals$goal.value, 
       list(s9_goals$proclamation, s9_goals$lie, s9_goals$goal.time), 
       FUN = length)

#Across Proclamation and Time 
tapply(s9_goals$goal.value, list(s9_goals$proclamation, s9_goals$goal.time), mean)
tapply(s9_goals$goal.value, list(s9_goals$proclamation, s9_goals$goal.time), sd)
tapply(s9_goals$goal.value, list(s9_goals$proclamation, s9_goals$goal.time), length)

#Across Lie Amount and Time 
tapply(s9_goals$goal.value, list(s9_goals$lie, s9_goals$goal.time), mean)
tapply(s9_goals$goal.value, list(s9_goals$lie, s9_goals$goal.time), sd)
tapply(s9_goals$goal.value, list(s9_goals$lie, s9_goals$goal.time), length)

#Across Proclamation
tapply(s9_goals$goal.value, s9_goals$proclamation, mean)
tapply(s9_goals$goal.value, s9_goals$proclamation, sd)
tapply(s9_goals$goal.value, s9_goals$proclamation, length)

#Across Lie Amount
tapply(s9_goals$goal.value, s9_goals$lie, mean)
tapply(s9_goals$goal.value, s9_goals$lie, sd)
tapply(s9_goals$goal.value, s9_goals$lie, length)

#Across Time
tapply(s9_goals$goal.value, s9_goals$goal.time, mean)
tapply(s9_goals$goal.value, s9_goals$goal.time, sd)
tapply(s9_goals$goal.value, s9_goals$goal.time, length)


```

# Difference in absolute v flexible just within repeat liars at time two - honesty ideals

```{r}
#Effect of proclamation just within multiple liars only at time two
proc_multiplelies_ideals <- s9_goals%>%
  filter(lie == "repeat") 

proc_multiplelies_ideals2 <- proc_multiplelies_ideals %>%
  filter(goal.time == "goal_2") 


t.test(goal.value ~ proclamation, data = proc_multiplelies_ideals2, var.equal = TRUE)
t_apa(t.test(goal.value ~ proclamation, data = proc_multiplelies_ideals2, var.equal = TRUE))


```

#Supplemental - Counts as Lying

```{r}
#Ratings in agreement with, "This person believes that his/her behavior during the Random Outcome Task counts as lying"

#Time one ANOVA
counts.afex <- aov_car(counts ~ proclamation * lie + Error(ID), s9)
summary(counts.afex)
anova_apa(counts.afex)


#Descriptives for Main Effects
#Across Proclamation
tapply(s9$counts, s9$proclamation, mean)
tapply(s9$counts, s9$proclamation, sd)
tapply(s9$counts, s9$proclamation, length)

#Across Lie Amount
tapply(s9$counts, s9$lie, mean)
tapply(s9$counts, s9$lie, sd)
tapply(s9$counts, s9$lie, length)

```

See the R script StudySI3_mediation.R  for mediation results.
