---
title: "Supplemental Study 2 (Study7)"
author: "Elizabeth Huppert"
date: "5/4/2020"
output: pdf_document
---

#Set-up

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-psych
-apa
-psych
-dplyr
-emmeans

```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(psych)
library(afex)
library(apa)
library(psych)
library(dplyr)
library(emmeans)

#read in data

s7 <- read.csv(here("HypocrisyStudySI_2.csv")) #327

```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


# Models

Key variable names (also see codebook for more information):

1. Proclamation:
Assignment to absolute vs. flexible honesty stance

2. Lie.motives:
Assignment to prosocial vs. selfish lie

3. Discomfort_1:
Discomfort (Ratings: 1-7)

4. Trust:
Trustworthy (Ratings: 1-7)

# Composite  Evaluation Variables

Items with high agreement were combined as per our pre-registration.

```{r}
#Hypocrisy
hypocrisy7_df <- data.frame(s7$hypocrisy_1, s7$hypocrisy_2, s7$hypocrisy_3)
summary(hypocrisy7_df)
describe(hypocrisy7_df)
psych::alpha(hypocrisy7_df) #alpha = 0.86
s7<- mutate(s7, hypocrisy7_composite = ((s7$hypocrisy_1 + s7$hypocrisy_2 + s7$hypocrisy_3)/3))

#Morality
cor.test(s7$moral_1, s7$moral_2) #r = 0.91
s7<- mutate(s7, moral7_composite  = ((s7$moral_1 + s7$moral_2)/2))

#Benevolence
ben_7check <- data.frame(s7$benevolence_1, s7$benevolence_2, s7$benevolence_3, s7$honest)
summary(ben_7check)
describe(ben_7check)
psych::alpha(ben_7check) #alpha = .88
s7 <- mutate(s7, benevolence7_composite = ((s7$benevolence_1 + s7$benevolence_2 + s7$benevolence_3 + s7$honest)/3))

```

Evaluation variables:

hypocrisy7_composite = hypocrisy composite of 3 items (Ratings: 1-7)
moral7_composite = morality composite of 2 items (Ratings: 1-7)
benevolence7_composite = benevolence composite of 4 items (Ratings: 1-7)


# Hypocrisy Model

```{r}
#ANOVA
hypocrisy7.afex <-aov_car(hypocrisy7_composite ~ proclamation*lie.motives + Error(ID), data=s7)
summary(hypocrisy7.afex)
anova_apa(hypocrisy7.afex)
```

# Hypocrisy Descriptives

```{r}
#Cells
tapply(s7$hypocrisy7_composite, list(s7$proclamation, s7$lie.motives), FUN = mean)
tapply(s7$hypocrisy7_composite, list(s7$proclamation, s7$lie.motives), FUN = sd)
tapply(s7$hypocrisy7_composite, list(s7$proclamation, s7$lie.motives), FUN = length)

#Across Proclamation
tapply(s7$hypocrisy7_composite, s7$proclamation,FUN = length)
tapply(s7$hypocrisy7_composite, s7$proclamation,FUN = mean)
tapply(s7$hypocrisy7_composite, s7$proclamation,FUN = sd)

#Across Lie.motives
tapply(s7$hypocrisy7_composite, s7$lie.motives,FUN = length)
tapply(s7$hypocrisy7_composite, s7$lie.motives,FUN = mean)
tapply(s7$hypocrisy7_composite, s7$lie.motives,FUN = sd)

#Overall
mean(s7$hypocrisy7_composite)
sd(s7$hypocrisy7_composite)
length(s7$hypocrisy7_composite)

```

# Hypocrisy Simple Effects

```{r}
#Lie motives on proclamations
absolute_test <- s7 %>%
  filter(proclamation == "absolute") 

t.test(hypocrisy7_composite ~ lie.motives, data = absolute_test, var.equal = TRUE)
t_apa(t.test(hypocrisy7_composite ~ lie.motives, data = absolute_test, var.equal = TRUE))

ambiguous_test <- s7 %>%
  filter(proclamation == "ambiguous") 

t.test(hypocrisy7_composite ~ lie.motives, data = ambiguous_test, var.equal = TRUE)
t_apa(t.test(hypocrisy7_composite ~ lie.motives, data = ambiguous_test, var.equal = TRUE))

#Proclamation on lie motives
prosocial_test <- s7 %>%
  filter(lie.motives == "prosocial") 

t.test(hypocrisy7_composite ~ proclamation, data = prosocial_test, var.equal = TRUE)
t_apa(t_test(hypocrisy7_composite ~ proclamation, data = prosocial_test, var.equal = TRUE))

selfish_test <- s7 %>%
  filter(lie.motives == "selfish") 

t.test(hypocrisy7_composite ~ proclamation, data = selfish_test, var.equal = TRUE)
t_apa(t_test(hypocrisy7_composite ~ proclamation, data = selfish_test, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
hyp_model = aov_ez('ID', 'hypocrisy7_composite', s7,
                    within = c (),
                    between = c ('proclamation', 'lie.motives'),
                    anova_table = list(es = 'pes'))
print(hyp_model)
means <- emmeans(hyp_model, ~ proclamation|lie.motives)
print(means)
post1 <- emmeans(hyp_model, ~ proclamation|lie.motives)
pairs(post1) 
post2 <- emmeans(hyp_model, ~ lie.motives|proclamation)
pairs(post2) 
```

#Morality Model

```{r}
#ANOVA
morality7.afex <-aov_car(moral7_composite ~ proclamation*lie.motives + Error(ID), data=s7)
summary(morality7.afex)
anova_apa(morality7.afex)
```

# Morality Descriptives

```{r}
#Cells
tapply(s7$moral7_composite, list(s7$proclamation, s7$lie.motives), FUN = mean)
tapply(s7$moral7_composite, list(s7$proclamation, s7$lie.motive), FUN = sd)
tapply(s7$moral7_composite, list(s7$proclamation, s7$lie.motive), FUN = length)

#Across Proclamation
tapply(s7$moral7_composite, s7$proclamation,FUN = length)
tapply(s7$moral7_composite, s7$proclamation,FUN = mean)
tapply(s7$moral7_composite, s7$proclamation,FUN = sd)

#Across Lie.motives
tapply(s7$moral7_composite, s7$lie.motive,FUN = length)
tapply(s7$moral7_composite, s7$lie.motive,FUN = mean)
tapply(s7$moral7_composite, s7$lie.motive,FUN = sd)

#Overall
mean(s7$moral7_composite)
sd(s7$moral7_composite)
length(s7$moral7_composite)
```


# Guilt Model

```{r}
#ANOVA
discomfort7.afex <-aov_car(discomfort_1 ~ proclamation*lie.motives + Error(ID), data=s7)
summary(discomfort7.afex) 
anova_apa(discomfort7.afex)
```

#Guilt Descriptives


```{r}
#Cells
tapply(s7$discomfort_1, list(s7$proclamation, s7$lie.motives), FUN = mean)
tapply(s7$discomfort_1, list(s7$proclamation, s7$lie.motives), FUN = sd)
tapply(s7$discomfort_1, list(s7$proclamation, s7$lie.motives), FUN = length)

#Across Proclamation
tapply(s7$discomfort_1, s7$proclamation,FUN = length)
tapply(s7$discomfort_1, s7$proclamation,FUN = mean)
tapply(s7$discomfort_1, s7$proclamation,FUN = sd)

#Across Lie.motives
tapply(s7$discomfort_1, s7$lie.motives,FUN = length)
tapply(s7$discomfort_1, s7$lie.motives,FUN = mean)
tapply(s7$discomfort_1, s7$lie.motives,FUN = sd)

#Overall
mean(s7$discomfort_1)
sd(s7$discomfort_1)
length(s7$discomfort_1)
```

#Attitudinal Trust Model

```{r}
#ANOVA
trust7.afex <-aov_car(trust ~ proclamation*lie.motives + Error(ID), data=s7)
summary(trust7.afex) 
anova_apa(trust7.afex) 
```

#Attitudinal Trust Descriptives

```{r}
#Cells
tapply(s7$trust, list(s7$proclamation, s7$lie.motives), FUN = mean)
tapply(s7$trust, list(s7$proclamation, s7$lie.motives), FUN = sd)
tapply(s7$trust, list(s7$proclamation, s7$lie.motives), FUN = length)

#Across Proclamation
tapply(s7$trust, s7$proclamation,FUN = length)
tapply(s7$trust, s7$proclamation,FUN = mean)
tapply(s7$trust, s7$proclamation,FUN = sd)

#Across Lie.motives
tapply(s7$trust, s7$lie.motives,FUN = length)
tapply(s7$trust, s7$lie.motives,FUN = mean)
tapply(s7$trust, s7$lie.motives,FUN = sd)

#Overall
mean(s7$trust)
sd(s7$trust)
length(s7$trust)
```

#Benevolence Model

```{r}
#ANOVA
benevolence7.afex <-aov_car(benevolence7_composite ~ proclamation*lie.motives + Error(ID), data=s7)
summary(benevolence7.afex)
anova_apa(benevolence7.afex) 
```

#Benevolence Descriptives

```{r}
#Cells
tapply(s7$benevolence7_composite, list(s7$proclamation, s7$lie.motives), FUN = mean)
tapply(s7$benevolence7_composite, list(s7$proclamation, s7$lie.motives), FUN = sd)
tapply(s7$benevolence7_composite, list(s7$proclamation, s7$lie.motives), FUN = length)

#Across Proclamation
tapply(s7$benevolence7_composite, s7$proclamation,FUN = length)
tapply(s7$benevolence7_composite, s7$proclamation,FUN = mean)
tapply(s7$benevolence7_composite, s7$proclamation,FUN = sd)

#Across Lie.motives
tapply(s7$benevolence7_composite, s7$lie.motives,FUN = length)
tapply(s7$benevolence7_composite, s7$lie.motives,FUN = mean)
tapply(s7$benevolence7_composite, s7$lie.motives,FUN = sd)

#Overall
mean(s7$benevolence7_composite)
sd(s7$benevolence7_composite)
length(s7$benevolence7_composite)

```


See R script StudySI2_mediation.R for mediation results.