---
title: "Supplemental Study 5 (Study 10)"

author: "Elizabeth Huppert"
date: "8/9/2021"
output: html_document
---
#Set-up

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-psych
-reshape2
-apa
-dplyr
-emmeans

#Load Packages and Data

```{r, include = FALSE}
library(here)
library(tidyverse)
library(psych)
library(reshape2)
library(afex)
library(apa)
library(dplyr)
library(emmeans)

#read in data

s10 <- read.csv(here("HypocrisyStudySI_5.csv"))

```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.

Models

Key Variable Names (also see codebook for more information):

1. Condition:
Assignment to absolute vs. flexible honesty stance

#Re-code condition for ease of interpretation - "proc"

```{r}
s10$proc[s10$condition=="1"] <- "absolute"
s10$proc[s10$condition=="2"] <- "flexible"
```


# Factorize Country and Subject (id)

Note: Country 1 is India and Country 2 is the US.

```{r}
s10$Country <- as.factor(s10$Country)
s10$id<- as.factor(s10$id)
```

# Composite variables

```{r}
#time point 1 - hypocrisy
#hypocrisy_1 - this person is a hypocrite
s10$h1[s10$hypocrite=="Strongly disagree"] <- "1"
s10$h1[s10$hypocrite=="Disagree"] <- "2"
s10$h1[s10$hypocrite=="Somewhat disagree"] <- "3"
s10$h1[s10$hypocrite=="Neither agree nor disagree"] <- "4"
s10$h1[s10$hypocrite=="Somewhat agree"] <- "5"
s10$h1[s10$hypocrite=="Agree"] <- "6"
s10$h1[s10$hypocrite=="Strongly agree"] <- "7"
s10$h1 <- as.numeric(s10$h1)
#inauthentic
s10$h2[s10$inauthentic=="Strongly disagree"] <- "1"
s10$h2[s10$inauthentic=="Disagree"] <- "2"
s10$h2[s10$inauthentic=="Somewhat disagree"] <- "3"
s10$h2[s10$inauthentic=="Neither agree nor disagree"] <- "4"
s10$h2[s10$inauthentic=="Somewhat agree"] <- "5"
s10$h2[s10$inauthentic=="Agree"] <- "6"
s10$h2[s10$inauthentic=="Strongly agree"] <- "7"
s10$h2 <- as.numeric(s10$h2)
#disingenuous
s10$h3[s10$disingenuous=="Strongly disagree"] <- "1"
s10$h3[s10$disingenuous=="Disagree"] <- "2"
s10$h3[s10$disingenuous=="Somewhat disagree"] <- "3"
s10$h3[s10$disingenuous=="Neither agree nor disagree"] <- "4"
s10$h3[s10$disingenuous=="Somewhat agree"] <- "5"
s10$h3[s10$disingenuous=="Agree"] <- "6"
s10$h3[s10$disingenuous=="Strongly agree"] <- "7"
s10$h3 <- as.numeric(s10$h3)
#cronbachs alpha for 3  hypocrisy items - time one
hypoSI5_df <- data.frame(s10$h1, s10$h2, s10$h3)
summary(hypoSI5_df)
describe(hypoSI5_df)
psych::alpha(hypoSI5_df) # raw = 0.95
#hypocrisy items over 0.6 so create a composite
s10 <- mutate(s10, 
                   SI5_hcomposite = 
                     ((s10$h1+s10$h2+s10$h3)/3))

#time two hypocrisy
#hypo_2 - this person is a hypocrite
s10$h1.2[s10$hypo_2 =="Strongly disagree"] <- "1"
s10$h1.2[s10$hypo_2 =="Disagree"] <- "2"
s10$h1.2[s10$hypo_2 =="Somewhat disagree"] <- "3"
s10$h1.2[s10$hypo_2 =="Neither agree nor disagree"] <- "4"
s10$h1.2[s10$hypo_2 =="Somewhat agree"] <- "5"
s10$h1.2[s10$hypo_2 =="Agree"] <- "6"
s10$h1.2[s10$hypo_2 =="Strongly agree"] <- "7"
s10$h1.2 <- as.numeric(s10$h1.2)
#inauth_2 
s10$h2.2[s10$inauth_2 =="Strongly disagree"] <- "1"
s10$h2.2[s10$inauth_2 =="Disagree"] <- "2"
s10$h2.2[s10$inauth_2 =="Somewhat disagree"] <- "3"
s10$h2.2[s10$inauth_2 =="Neither agree nor disagree"] <- "4"
s10$h2.2[s10$inauth_2 =="Somewhat agree"] <- "5"
s10$h2.2[s10$inauth_2 =="Agree"] <- "6"
s10$h2.2[s10$inauth_2 =="Strongly agree"] <- "7"
s10$h2.2 <- as.numeric(s10$h2.2)
#disingen_2
s10$h3.2[s10$disingen_2=="Strongly disagree"] <- "1"
s10$h3.2[s10$disingen_2=="Disagree"] <- "2"
s10$h3.2[s10$disingen_2=="Somewhat disagree"] <- "3"
s10$h3.2[s10$disingen_2=="Neither agree nor disagree"] <- "4"
s10$h3.2[s10$disingen_2=="Somewhat agree"] <- "5"
s10$h3.2[s10$disingen_2=="Agree"] <- "6"
s10$h3.2[s10$disingen_2=="Strongly agree"] <- "7"
s10$h3.2 <- as.numeric(s10$h3.2)
#cronbachs alpha for 3  hypocrisy items - time two
hypoSI5_df2 <- data.frame(s10$h1.2, s10$h2.2, s10$h3.2)
summary(hypoSI5_df2)
describe(hypoSI5_df2)
psych::alpha(hypoSI5_df2) # raw = 0.94
#hypocrisy items over 0.6 so create a composite
s10 <- mutate(s10, 
                   SI5_hcomposite2 = 
                     ((s10$h1.2 + s10$h2.2 + s10$h3.2)/3))

#Honesty time 1
#honest_freq, reverse code
s10$hf1[s10$lie_freq=="Not often at all"] <- "7"
s10$hf1[s10$lie_freq=="Not very often"] <- "6"
s10$hf1[s10$lie_freq=="Slightly often"] <- "5"
s10$hf1[s10$lie_freq=="Somewhat often"] <- "4"
s10$hf1[s10$lie_freq=="Moderately often"] <- "3"
s10$hf1[s10$lie_freq=="Very often"] <- "2"
s10$hf1[s10$lie_freq=="Extremely often"] <- "1"
s10$hf1 <- as.numeric(s10$hf1)
#honest_likely, reverse code
s10$hl1[s10$future_lie=="Not at all likely"] <- "7"
s10$hl1[s10$future_lie=="Not very likely"] <- "6"
s10$hl1[s10$future_lie=="Slightly likely"] <- "5"
s10$hl1[s10$future_lie=="Somewhat likely"] <- "4"
s10$hl1[s10$future_lie=="Moderately likely"] <- "3"
s10$hl1[s10$future_lie=="Very likely"] <- "2"
s10$hl1[s10$future_lie=="Extremely likely"] <- "1"
s10$hl1 <- as.numeric(s10$hl1)
#honest_extreme
s10$he1[s10$extreme_lie=="Not at all extreme"] <-  "1"
s10$he1[s10$extreme_lie=="Not very extreme"] <- "2"
s10$he1[s10$extreme_lie=="Slightly extreme"] <- "3"
s10$he1[s10$extreme_lie=="Somewhat extreme"] <- "4"
s10$he1[s10$extreme_lie=="Moderately extreme"] <- "5"
s10$he1[s10$extreme_lie=="Very extreme"] <- "6"
s10$he1[s10$extreme_lie=="The most extreme"] <- "7"
s10$he1 <- as.numeric(s10$he1)
#committment_honest_1
s10$ch1[s10$comm_h=="Not at all"] <- " 1"
s10$ch1[s10$comm_h=="Not very"] <- "2"
s10$ch1[s10$comm_h=="Slightly"] <- "3"
s10$ch1[s10$comm_h=="Somewhat"] <- "4"
s10$ch1[s10$comm_h=="Moderately"] <- "5"
s10$ch1[s10$comm_h=="Very"] <- "6"
s10$ch1[s10$comm_h=="Extremely"] <- "7"
s10$ch1 <- as.numeric(s10$ch1)
#look at different honesty items - 4
SI5_honesty_df <- data.frame(s10$hf1, s10$hl1, s10$he1, s10$ch1)
summary(SI5_honesty_df)
describe(SI5_honesty_df)
psych::alpha(SI5_honesty_df) # raw= 0.67
#over .6 so combine
s10 <- mutate(s10, 
                   SI_honest_composite = 
                     ((s10$hf1 + s10$hl1 + s10$he1 + s10$ch1)/4))

#Honesty composite time two

#honest_freq, reverse code
s10$hf1.2[s10$lie_freq2=="Not often at all"] <- "7"
s10$hf1.2[s10$lie_freq2=="Not very often"] <- "6"
s10$hf1.2[s10$lie_freq2=="Slightly often"] <- "5"
s10$hf1.2[s10$lie_freq2=="Somewhat often"] <- "4"
s10$hf1.2[s10$lie_freq2=="Moderately often"] <- "3"
s10$hf1.2[s10$lie_freq2=="Very often"] <- "2"
s10$hf1.2[s10$lie_freq2=="Extremely often"] <- "1"
s10$hf1.2<- as.numeric(s10$hf1.2)
#honest_likely, reverse code
s10$hl1.2[s10$future_lie2=="Not at all likely"] <- "7"
s10$hl1.2[s10$future_lie2=="Not very likely"] <- "6"
s10$hl1.2[s10$future_lie2=="Slightly likely"] <- "5"
s10$hl1.2[s10$future_lie2=="Somewhat likely"] <- "4"
s10$hl1.2[s10$future_lie2=="Moderately likely"] <- "3"
s10$hl1.2[s10$future_lie2=="Very likely"] <- "2"
s10$hl1.2[s10$future_lie2=="Extremely likely"] <- "1"
s10$hl1.2 <- as.numeric(s10$hl1.2)
#honest_extreme
s10$he1.2[s10$extreme_lie2=="Not at all extreme"] <-  "1"
s10$he1.2[s10$extreme_lie2=="Not very extreme"] <- "2"
s10$he1.2[s10$extreme_lie2=="Slightly extreme"] <- "3"
s10$he1.2[s10$extreme_lie2=="Somewhat extreme"] <- "4"
s10$he1.2[s10$extreme_lie2=="Moderately extreme"] <- "5"
s10$he1.2[s10$extreme_lie2=="Very extreme"] <- "6"
s10$he1.2[s10$extreme_lie2=="The most extreme"] <- "7"
s10$he1.2 <- as.numeric(s10$he1.2)
#committment_honest_1
s10$ch1.2[s10$comm_h2=="Not at all"] <- " 1"
s10$ch1.2[s10$comm_h2=="Not very"] <- "2"
s10$ch1.2[s10$comm_h2=="Slightly"] <- "3"
s10$ch1.2[s10$comm_h2=="Somewhat"] <- "4"
s10$ch1.2[s10$comm_h2=="Moderately"] <- "5"
s10$ch1.2[s10$comm_h2=="Very"] <- "6"
s10$ch1.2[s10$comm_h2=="Extremely"] <- "7"
s10$ch1.2 <- as.numeric(s10$ch1.2)
#look at different honesty items - 4
SI5_honesty_df2 <- data.frame(s10$hf1.2, s10$hl1.2, s10$he1.2, s10$ch1.2)
summary(SI5_honesty_df2)
describe(SI5_honesty_df2)
psych::alpha(SI5_honesty_df2) # raw= 0.70
#over .6 so combine
s10 <- mutate(s10, 
                   SI_honest_composite2 = 
                     ((s10$hf1.2 + s10$hl1.2 + s10$he1.2 + s10$ch1.2)/4))

#Moral
#time 1
#moral
s10$m1[s10$moral =="Not at all"] <- "1"
s10$m1[s10$moral =="Not very"] <- "2"
s10$m1[s10$moral =="Slightly"] <- "3"
s10$m1[s10$moral =="Somewhat"] <- "4"
s10$m1[s10$moral =="Moderately"] <- "5"
s10$m1[s10$moral =="Very"] <- "6"
s10$m1[s10$moral =="Extremely"] <- "7"
s10$m1 <- as.numeric(s10$m1)
#moral_2
s10$m2[s10$ethical=="Not at all"] <- "1"
s10$m2[s10$ethical=="Not very"] <- "2"
s10$m2[s10$ethical=="Slightly"] <- "3"
s10$m2[s10$ethical=="Somewhat"] <- "4"
s10$m2[s10$ethical=="Moderately"] <- "5"
s10$m2[s10$ethical=="Very"] <- "6"
s10$m2[s10$ethical=="Extremely"] <- "7"
s10$m2 <- as.numeric(s10$m2)
#moral_3
s10$m3[s10$trust =="Not at all"] <- "1"
s10$m3[s10$trust =="Not very"] <- "2"
s10$m3[s10$trust =="Slightly"] <- "3"
s10$m3[s10$trust =="Somewhat"] <- "4"
s10$m3[s10$trust =="Moderately"] <- "5"
s10$m3[s10$trust =="Very"] <- "6"
s10$m3[s10$trust =="Extremely"] <- "7"
s10$m3 <- as.numeric(s10$m3)
#moral composite
SI5_moral_df <- data.frame(s10$m1, s10$m2, s10$m3)
summary(SI5_moral_df)
describe(SI5_moral_df)
psych::alpha(SI5_moral_df) # raw = 0.93
s10 <- mutate(s10, 
                   SI_moral_composite = ((s10$m1+s10$m2+s10$m3)/3))

#time 2
#moral
s10$m1.2[s10$moral_2=="Not at all"] <- "1"
s10$m1.2[s10$moral_2=="Not very"] <- "2"
s10$m1.2[s10$moral_2=="Slightly"] <- "3"
s10$m1.2[s10$moral_2=="Somewhat"] <- "4"
s10$m1.2[s10$moral_2=="Moderately"] <- "5"
s10$m1.2[s10$moral_2=="Very"] <- "6"
s10$m1.2[s10$moral_2=="Extremely"] <- "7"
s10$m1.2<- as.numeric(s10$m1.2)
#moral_2
s10$m2.2[s10$ethical_2=="Not at all"] <- "1"
s10$m2.2[s10$ethical_2=="Not very"] <- "2"
s10$m2.2[s10$ethical_2=="Slightly"] <- "3"
s10$m2.2[s10$ethical_2=="Somewhat"] <- "4"
s10$m2.2[s10$ethical_2=="Moderately"] <- "5"
s10$m2.2[s10$ethical_2=="Very"] <- "6"
s10$m2.2[s10$ethical_2=="Extremely"] <- "7"
s10$m2.2 <- as.numeric(s10$m2.2)
#moral_3
s10$m3.2[s10$trust_2 =="Not at all"] <- "1"
s10$m3.2[s10$trust_2 =="Not very"] <- "2"
s10$m3.2[s10$trust_2 =="Slightly"] <- "3"
s10$m3.2[s10$trust_2 =="Somewhat"] <- "4"
s10$m3.2[s10$trust_2 =="Moderately"] <- "5"
s10$m3.2[s10$trust_2 =="Very"] <- "6"
s10$m3.2[s10$trust_2=="Extremely"] <- "7"
s10$m3.2 <- as.numeric(s10$m3.2)
#moral composite
SI5_moral_df2 <- data.frame(s10$m1.2, s10$m2.2, s10$m3.2)
summary(SI5_moral_df2)
describe(SI5_moral_df2)
psych::alpha(SI5_moral_df2) # raw = 0.97
s10 <- mutate(s10, 
                   SI_moral_composite2 = ((s10$m1.2 + s10$m2.2 + s10$m3.2 )/3))

```

# Analysis

# Hypocrisy
```{r}
#Dataframe for Hypocrisy
hypo5_SI_df <-melt(s10, 
                    id.vars=c("condition", "id", "proc", "Country"),
                    #measure command is for the DV
                    measure.vars=c("SI5_hcomposite","SI5_hcomposite2"),
                    variable.name="h5.time",
                    value.name="h5value"
)

#ANOVA
hSI5.afex <- aov_car(
  h5value ~ proc*h5.time + Error(id/h5.time),
  data = hypo5_SI_df)
summary(hSI5.afex)
anova_apa(hSI5.afex)
```

# Hypocrisy descriptives

```{r}
#Cells: Proclamation and Time
tapply(hypo5_SI_df$h5value, list(hypo5_SI_df$proc, hypo5_SI_df$h5.time),
       FUN = length)

tapply(hypo5_SI_df$h5value, list(hypo5_SI_df$proc, hypo5_SI_df$h5.time),
       FUN = mean)

tapply(hypo5_SI_df$h5value, list(hypo5_SI_df$proc, hypo5_SI_df$h5.time),
       FUN = sd)

#Across proclamation
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc, FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc,FUN = length)

#Across Time
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = length)

```

# Country and Hypocrisy (analysis, descriptives)

```{r}
#ANOVA
hSI5_c.afex <- aov_car(
  h5value ~ proc*h5.time*Country + Error(id/h5.time),
  data = hypo5_SI_df)
summary(hSI5_c.afex )
anova_apa(hSI5_c.afex )

#Country
tapply(hypo5_SI_df$h5value, hypo5_SI_df$Country,FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$Country,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$Country,FUN = length)


#Country*Time 
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = mean)
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = sd)
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = length)

#Cells
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = mean)

tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = sd)

tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = length)
```

# Morality

```{r}
moral5_SI_df <-melt(s10, 
                     id.vars=c("condition", "id", "proc", "Country"),
                     #measure command is for the DV
                     measure.vars=c("SI_moral_composite", "SI_moral_composite2"),
                     variable.name="m5.time",
                     value.name="m5value"
)

#ANOVA
m_SI5.afex <- aov_car(
  m5value ~ proc*m5.time + Error(id/m5.time),
  data = moral5_SI_df)
summary(m_SI5.afex)
anova_apa(m_SI5.afex)
```

# Morality descriptives

```{r}
#Cells: Proclamation and Time
tapply(moral5_SI_df$m5value , list(moral5_SI_df$proc, moral5_SI_df$m5.time),
       FUN = length)

tapply(moral5_SI_df$m5value , list(moral5_SI_df$proc, moral5_SI_df$m5.time),
       FUN = mean)

tapply(moral5_SI_df$m5value , list(moral5_SI_df$proc, moral5_SI_df$m5.time),
       FUN = sd)


#Across Proclamation
tapply(moral5_SI_df$m5value, moral5_SI_df$proc, FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$proc,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$proc,FUN = length)

#Across Time
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = length)

```


# Country and morality (analysis, descriptives)

```{r}
#ANOVA
m_SI5_c.afex <- aov_car(
  m5value ~ proc*m5.time*Country + Error(id/m5.time),
  data = moral5_SI_df)
summary(m_SI5_c.afex)
anova_apa(m_SI5_c.afex)

#Country
tapply(moral5_SI_df$m5value, moral5_SI_df$Country,FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$Country,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$Country,FUN = length)


#Country*Time 
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = mean)
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = sd)
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = length)


#Cells
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = mean)

tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = sd)

tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = length)
```

# Moral Country T-tests at time two

```{r}
#T-test at time two absolute vs. flexible by country
#US
US_only <- s10 %>%
  filter(Country == "2")
India_only <- s10 %>%
  filter(Country == "1")


t.test(SI_moral_composite2 ~ proc, US_only, var.equal = TRUE)
t_apa(t.test(SI_moral_composite2 ~ proc, US_only, var.equal = TRUE))

t.test(SI_moral_composite2 ~ proc, India_only, var.equal = TRUE)
t_apa(t.test(SI_moral_composite2 ~ proc, India_only, var.equal = TRUE))

```


# Honesty

```{r}
honest5_SI_df <-melt(s10, 
                   id.vars=c("condition", "id", "proc", "Country"),
                   #measure command is for the DV
                   measure.vars=c("SI_honest_composite","SI_honest_composite2"),
                   variable.name="honest5.time",
                   value.name="honest5value"
)

#ANOVA
hon_SI5.afex <- aov_car(
  honest5value ~ proc*honest5.time + Error(id/honest5.time),
  data = honest5_SI_df)
summary(hon_SI5.afex)
anova_apa(hon_SI5.afex)
```

# Honesty descriptives

```{r}
#Cells: Proclamation and Time
tapply(honest5_SI_df$honest5value , list(honest5_SI_df$proc, honest5_SI_df$honest5.time),
       FUN = length)

tapply(honest5_SI_df$honest5value , list(honest5_SI_df$proc, honest5_SI_df$honest5.time),
       FUN = mean)

tapply(honest5_SI_df$honest5value , list(honest5_SI_df$proc, honest5_SI_df$honest5.time),
       FUN = sd)


#Across Proclamation
tapply(honest5_SI_df$honest5value, honest5_SI_df$proc, FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$proc,FUN = sd)
tapply(honest5_SI_df$honest5value, hhonest5_SI_df$proc,FUN = length)

#Across Time
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = sd)
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = length)

```

# Honesty t-test

```{r}
#T-test at time two
t.test(SI_honest_composite2 ~ proc, s10, var.equal = TRUE)
t_apa(t.test(SI_honest_composite2~ proc, s10, var.equal = TRUE))
```

# Country and honesty (analysis, descriptives)

```{r}
#ANOVA
hon_SI5_c.afex <- aov_car(
  honest5value ~ proc*honest5.time*Country + Error(id/honest5.time),
  data = honest5_SI_df)
summary(hon_SI5_c.afex)
anova_apa(hon_SI5_c.afex)

#Country
tapply(honest5_SI_df$honest5value, honest5_SI_df$Country,FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$Country,FUN = sd)
tapply(honest5_SI_df$honest5value, honest5_SI_df$Country,FUN = length)


#Country*Time 
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = mean)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = sd)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = length)

#Country*proc 
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$proc), 
       FUN = mean)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$proc), 
       FUN = sd)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$proc), 
       FUN = length)

#Cells
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$proc, honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = mean)

tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$proc, honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = sd)

tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$proc, honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = length)
```

# Country t-tests for Committment to Honesty

```{r}
t.test(SI_honest_composite2 ~ proc, US_only, var.equal = TRUE)
t_apa(t.test(SI_honest_composite2 ~ proc, US_only, var.equal = TRUE))

t.test(SI_honest_composite2 ~ proc, India_only, var.equal = TRUE)
t_apa(t.test(SI_honest_composite2 ~ proc, India_only, var.equal = TRUE))
```

# Trust - Advice Game

```{r}
#remove subject 113 from this analysis since same guess as advice at T1

trust_df <- s10 %>%
  subset(s10$id != "113")


#ANOVA
trust.afex <- aov_car(
  advice ~ proc + Error(id),
  data = trust_df)
summary(trust.afex)
anova_apa(trust.afex)
```

# Culture and Advice Game

```{r}
#ANOVA
trust2.afex <- aov_car(
  advice ~ proc*Country + Error(id),
  data = trust_df)
summary(trust2.afex)
anova_apa(trust2.afex)

#Country
tapply(trust_df$advice, trust_df$Country,FUN = mean)
tapply(trust_df$advice, trust_df$Country,FUN = sd)
tapply(trust_df$advice, trust_dff$Country,FUN = length)
```

