---
title: "Study 2"
author: "Elizabeth Huppert"
date: "11/7/2022"
output: pdf_document
---

#Set-up and Read in Data

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-apa
-psych
-dplyr
-reshape2


```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(afex)
library(apa)
library(psych)
library(dplyr)
library(lavaan)
library(reshape2)

#read in data

s2 <- read.csv(here("HypocrisyStudy2_cleaned.csv")) #564
```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


Key variable names (also see codebook for more information):

1. Proclamation:
Assignment to absolute honesty stance vs. flexible honesty stance vs. control

2. Voting:
Likelihood of voting for Matthew Johnson (1 -7)


# Factorize Subject (id) and Proclamation

```{r}
s2$ID <- as.factor(s2$ID)
s2$Proclamation <- as.factor(s2$Proclamation)


```

# Composite Evaluation Variables 

Items with high agreement were combined as per our pre-registration.

# Time One Variables

```{r}
#Moral
moral2_t1_check <- data.frame(s2$Moral1_T1, s2$Moral2_T1, s2$Moral3_T1)
summary(moral2_t1_check)
describe(moral2_t1_check)
psych::alpha(moral2_t1_check) #alpha = 0.98
s2 <- mutate(s2, 
             Moral_composite2_t1 = 
               ((s2$Moral1_T1 + s2$Moral2_T1 + s2$Moral3_T1)/3))

#Future Honesty
honesty2_t1_check  <- data.frame(s2$Honest_frequencyT1, s2$Honest_likelihoodT1,
                                 s2$Honest_extremeT1, s2$Honest_committmentT1)
summary(honesty2_t1_check)
describe(honesty2_t1_check)
psych::alpha(honesty2_t1_check) #alpha = 0.89
s2 <- mutate(s2, Honest_composite2_t1 = 
               ((s2$Honest_frequencyT1+ s2$Honest_likelihoodT1+
                   s2$Honest_extremeT1 + s2$Honest_committmentT1)/4))

```

Evaluation variables:

Moral_composite2_t1 = morality composite of 3 items (Ratings: 1-7)
Honest_composite2_t1 = honesty thresholds composite of 4 items (Ratings: 1-7)

# Time Two Variables

```{r}
#Hypocrisy
hypocrisy2_check <- data.frame(s2$Hypocrisy_1, s2$Hypocrisy_2, s2$Hypocrisy_3, s2$Hypocrisy_4, s2$Hypocrisy_5)
summary(hypocrisy2_check)
describe(hypocrisy2_check)
psych::alpha(hypocrisy2_check) #alpha = 0.88
s2 <- mutate(s2, Hypocrisy_composite2= 
               ((s2$Hypocrisy_1 + s2$Hypocrisy_2 + s2$Hypocrisy_3 +
                   s2$Hypocrisy_4 + s2$Hypocrisy_5)/5))

#Morality
moral2_t2_check <- data.frame(s2$Moral1_T2, s2$Moral2_T2, s2$Moral3_T2)
summary(moral2_t2_check)
describe(moral2_t2_check)
psych::alpha(moral2_t2_check) #alpha = 0.97
s2 <- mutate(s2, 
             Moral_composite2_t2 = 
               ((s2$Moral1_T2 + s2$Moral2_T2+s2$Moral3_T2)/3))

#Future Honesty
honesty2_t2_check  <- data.frame(s2$Honest_frequencyT2, s2$Honest_likelihoodT2, s2$Honest_extremeT2, s2$Honest_committmentT2)
summary(honesty2_t2_check)
describe(honesty2_t2_check)
psych::alpha(honesty2_t2_check) #alpha = 0.81
s2 <- mutate(s2, 
             Honest_composite2_t2 = 
               ((s2$Honest_frequencyT2 + s2$Honest_likelihoodT2 +
                   s2$Honest_extremeT2 + s2$Honest_committmentT2)/4))

```

Evaluation variables:

Hypocrisy_composite2 = hypocrisy composite of 5 items (Ratings: 1-7)
Moral_composite2_t2 = morality composite of 3 items (Ratings: 1-7)
Honest_composite2_t2 = honesty thresholds composite of 4 items (Ratings: 1-7)


# Voting Intentions Model

```{r}
#Dataframe for Voting
vote2_df <-melt(s2, 
                id.vars=c("ID", "Proclamation"),
                #measure command is for the DV
                measure.vars=c("Voting_T1","Voting_T2"),
                variable.name="vote.time",
                value.name="vote.value"
)

#ANOVA
vote2.afex <- aov_car(
  vote.value ~ Proclamation*vote.time + Error(ID/vote.time),
  data = vote2_df)
summary(vote2.afex)
anova_apa(vote2.afex)

```

# Voting Descriptives

```{r}
#Across Proclamation and Time
tapply(vote2_df$vote.value, list(vote2_df$Proclamation, vote2_df$vote.time),
       FUN = length)

tapply(vote2_df$vote.value, list(vote2_df$Proclamation, vote2_df$vote.time),
       FUN = mean)
tapply(vote2_df$vote.value, list(vote2_df$Proclamation, vote2_df$vote.time),
       FUN = sd)

#Across Proclamations 
tapply(vote2_df$vote.value, vote2_df$Proclamation, mean)
tapply(vote2_df$vote.value, vote2_df$Proclamation, sd)
tapply(vote2_df$vote.value, vote2_df$Proclamation, length)
#Across Time
tapply(vote2_df$vote.value, vote2_df$vote.time, mean)
tapply(vote2_df$vote.value, vote2_df$vote.time, sd)
tapply(vote2_df$vote.value, vote2_df$vote.time, length)

#Just at each time point

#Across Proclamations Time One
tapply(s2$Voting_T1, s2$Proclamation, mean)
tapply(s2$Voting_T1, s2$Proclamation, sd)
tapply(s2$Voting_T1, s2$Proclamation, length)

#Across Proclamations Time One
tapply(s2$Voting_T2, s2$Proclamation, mean)
tapply(s2$Voting_T2, s2$Proclamation, sd)
tapply(s2$Voting_T2, s2$Proclamation, length)
```

# Voting Simple Effects - Subsetting Data

```{r}
#Melted df should have 1128

#Subset for main effects tests
abs_exclude2 <- vote2_df %>%
  filter(Proclamation != "absolute") #788 (394 x 2)

flex_exclude2  <- vote2_df %>%
  filter(Proclamation != "flexible") #758 (379 x 2)

control_exclude2 <- vote2_df %>%
  filter(Proclamation != "control") #710 (355 x 2)

abs_only<- vote2_df %>%
  filter(Proclamation == "absolute") #340 (170 x 2)

flex_only<- vote2_df %>%
  filter(Proclamation == "flexible") #370 (185 x 2)

control_only<- vote2_df %>%
  filter(Proclamation == "control") #418 (209 x 2)

#Abs time effect
t.test(vote.value~ vote.time, abs_only, var.equal = TRUE)
t_apa(t.test(vote.value~ vote.time, abs_only, var.equal = TRUE))

#Flex time effect
t.test(vote.value~ vote.time, flex_only, var.equal = TRUE)
t_apa(t.test(vote.value~ vote.time, flex_only, var.equal = TRUE))

#Control  time effect
t.test(vote.value~ vote.time, control_only, var.equal = TRUE)
t_apa(t.test(vote.value~ vote.time, control_only, var.equal = TRUE))

# Main effect: abs vs. flex vs. control
#Abs vs. Flex 
t.test(vote.value~ Proclamation, control_exclude2, var.equal = TRUE)
t_apa(t.test(vote.value~ Proclamation, control_exclude2, var.equal = TRUE))

#Abs vs. control
t.test(vote.value~ Proclamation, flex_exclude2, var.equal = TRUE)
t_apa(t.test(vote.value~ Proclamation, flex_exclude2, var.equal = TRUE))

#Flex vs. control
t.test(vote.value~ Proclamation, abs_exclude2, var.equal = TRUE)
t_apa(t.test(vote.value ~ Proclamation, abs_exclude2, var.equal = TRUE))

#Abs v Flex at Time 2 alone
# Use the control exclude but subset for only time 2
nocontrol_time2 <- control_exclude2  %>%
  filter(vote.time != "Voting_T1") #355
# t test
t.test(vote.value ~ Proclamation, nocontrol_time2, var.equal = TRUE)
t_apa(t.test(vote.value ~ Proclamation, nocontrol_time2, var.equal = TRUE))

#Control v Flex at Time 2 alone
# Use the control exclude but subset for only time 2
noabs_time2 <- abs_exclude2  %>%
  filter(vote.time != "Voting_T1") #394
# t test
t.test(vote.value ~ Proclamation, noabs_time2, var.equal = TRUE)
t_apa(t.test(vote.value ~ Proclamation, noabs_time2, var.equal = TRUE))

#Control v Abs at Time 2 alone
# Use the flex exclude but subset for only time 2
noflex_time2 <- flex_exclude2  %>%
  filter(vote.time != "Voting_T1") #379
# t test
t.test(vote.value ~ Proclamation, noflex_time2, var.equal = TRUE)
t_apa(t.test(vote.value ~ Proclamation, noflex_time2, var.equal = TRUE))

#Look at Abs v Flex at Time 1 also
# Use the control exclude but subset for only time 1
nocontrol_time1 <- control_exclude2  %>%
  filter(vote.time != "Voting_T2") #355
# t test
t.test(vote.value ~ Proclamation, nocontrol_time1, var.equal = TRUE)
t_apa(t.test(vote.value ~ Proclamation, nocontrol_time1, var.equal = TRUE))
```

# Morality Model

```{r}
moral2_df <-melt(s2, 
                id.vars=c("ID", "Proclamation"),
                #measure command is for the DV
                measure.vars=c("Moral_composite2_t1","Moral_composite2_t2"),
                variable.name="moral.time",
                value.name="moral.value"
)

#ANOVA
moral2.afex <- aov_car(
moral.value ~ Proclamation*moral.time + Error(ID/moral.time),
  data = moral2_df)
summary(moral2.afex)
anova_apa(moral2.afex)

```

# Moral Descriptives

```{r}
#Across Proclamation and Time
tapply(moral2_df$moral.value, list(moral2_df$Proclamation, moral2_df$moral.time),
       FUN = length)

tapply(moral2_df$moral.value, list(moral2_df$Proclamation, moral2_df$moral.time),
       FUN = mean)
tapply(moral2_df$moral.value, list(moral2_df$Proclamation, moral2_df$moral.time),
       FUN = sd)

#Across Proclamations 
tapply(moral2_df$moral.value, moral2_df$Proclamation, mean)
tapply(moral2_df$moral.value, moral2_df$Proclamation, sd)
tapply(moral2_df$moral.value, moral2_df$Proclamation, length)
#Across Time
tapply(moral2_df$moral.value, moral2_df$moral.time, mean)
tapply(moral2_df$moral.value, moral2_df$moral.time, sd)
tapply(moral2_df$moral.value, moral2_df$moral.time, length)

#Just at each time point

#Across Proclamations Time One
tapply(s2$Moral_composite2_t1, s2$Proclamation, mean)
tapply(s2$Moral_composite2_t1, s2$Proclamation, sd)
tapply(s2$Moral_composite2_t1, s2$Proclamation, length)

#Across Proclamations Time One
tapply(s2$Moral_composite2_t2, s2$Proclamation, mean)
tapply(s2$Moral_composite2_t2, s2$Proclamation, sd)
tapply(s2$Moral_composite2_t2, s2$Proclamation, length)
```

# Subset Morality Data for Simple Effects tests

```{r}
#Subset for main effects tests
abs_exclude2m <- moral2_df %>%
  filter(Proclamation != "absolute") #788 (394 x 2)

flex_exclude2m  <- moral2_df %>%
  filter(Proclamation != "flexible") #758 (379 x 2)

control_exclude2m <- moral2_df %>%
  filter(Proclamation != "control") #710 (355 x 2)

abs_onlym <- moral2_df %>%
  filter(Proclamation == "absolute") #340 (170 x 2)

flex_onlym <- moral2_df %>%
  filter(Proclamation == "flexible") #370 (185 x 2)

control_onlym <- moral2_df %>%
  filter(Proclamation == "control") #418 (209 x 2)

#Main effect of time
#Abs time effect
t.test(moral.value~ moral.time, abs_onlym, var.equal = TRUE)
t_apa(t.test(moral.value~ moral.time, abs_onlym, var.equal = TRUE))

#Flex time effect
t.test(moral.value~ moral.time, flex_onlym, var.equal = TRUE)
t_apa(t.test(moral.value~ moral.time, flex_onlym, var.equal = TRUE))

#Control  time effect
t.test(moral.value~ moral.time, control_onlym, var.equal = TRUE)
t_apa(t.test(moral.value~ moral.time, control_onlym, var.equal = TRUE))

# Main effect: Proclamation

#Abs vs. Flex 
t.test(moral.value ~ Proclamation, control_exclude2m, var.equal = TRUE)
t_apa(t.test(moral.value ~ Proclamation, control_exclude2m, var.equal = TRUE))

#Abs vs. control
t.test(moral.value~ Proclamation, flex_exclude2m, var.equal = TRUE)
t_apa(t.test(moral.value ~ Proclamation, flex_exclude2m, var.equal = TRUE))

#Flex vs. control
t.test(moral.value~ Proclamation, abs_exclude2m, var.equal = TRUE)
t_apa(t.test(moral.value ~ Proclamation, abs_exclude2m, var.equal = TRUE))

#Abs v Flex at Time 2 alone
# Use the control exclude but subset for only time 2
nocontrol_time2m <- control_exclude2m  %>%
  filter(moral.time != "Moral_composite2_t1") #355
# t test
t.test(moral.value ~ Proclamation, nocontrol_time2m, var.equal = TRUE)
t_apa(t.test(moral.value ~ Proclamation, nocontrol_time2m, var.equal = TRUE))

#Control v Flex at Time 2 alone
# Use the control exclude but subset for only time 2
noabs_time2m <- abs_exclude2m  %>%
  filter(moral.time != "Moral_composite2_t1") #394
# t test
t.test(moral.value~ Proclamation, noabs_time2m, var.equal = TRUE)
t_apa(t.test(moral.value~ Proclamation, noabs_time2m, var.equal = TRUE))

#Control v Abs at Time 2 alone
# Use the flex exclude but subset for only time 2
noflex_time2m <- flex_exclude2m  %>%
  filter(moral.time != "Moral_composite2_t1") #379
# t test
t.test(moral.value ~ Proclamation, noflex_time2m, var.equal = TRUE)
t_apa(t.test(moral.value ~ Proclamation, noflex_time2m, var.equal = TRUE))

```

# Cohen's D for Morality Posthoc

```{r}
#Abs vs. Flex morality focal at time two - need cohen's D

#Method 1
#abs mean =   2.794118, sd = 1.332876, 170
#flex mean =  1.958559, sd = 1.009658, 185
#pooled SD = sqrt(((1.332876^2) + (1.009658^2))/2)
sqrt((((1.332876^2) + (1.009658^2))/2)) #1.182364

#cohens = (mean - mean)/SD pooeld
(2.794118-1.958559)/1.182364 #0.7066851

#Method 2
#Exclude control from full dataset to compare just Abs vs. Flex
control_exclude_full <- s2 %>%
  filter(Proclamation != "control") #355
d2 <- cohens_d(t_test(Moral_composite2_t2  ~ Proclamation, control_exclude_full)) 
d2 #Cohen's d abs. vs. flex. on morality (abs value)  = 0.7107867
```

# Future Honesty Model

```{r}
honest2_df <-melt(s2, 
                id.vars=c("ID", "Proclamation"),
                #measure command is for the DV
                measure.vars=c("Honest_composite2_t1","Honest_composite2_t2"),
                variable.name="honest.time",
                value.name="honest.value"
)

#ANOVA
honest2.afex <- aov_car(
honest.value ~ Proclamation*honest.time + Error(ID/honest.time),
  data = honest2_df)
summary(honest2.afex)
anova_apa(honest2.afex)

```

# Future Honesty Descriptives

```{r}
#Across Proclamation and Time
tapply(honest2_df$honest.value, list(honest2_df$Proclamation, honest2_df$honest.time),
       FUN = length)

tapply(honest2_df$honest.value, list(honest2_df$Proclamation, honest2_df$honest.time),
       FUN = mean)
tapply(honest2_df$honest.value, list(honest2_df$Proclamation, honest2_df$honest.time),
       FUN = sd)

#Across Proclamations 
tapply(honest2_df$honest.value, honest2_df$Proclamation, mean)
tapply(honest2_df$honest.value, honest2_df$Proclamation, sd)
tapply(honest2_df$honest.value, honest2_df$Proclamation, length)
#Across Time
tapply(honest2_df$honest.value, honest2_df$honest.time, mean)
tapply(honest2_df$honest.value, honest2_df$honest.time, sd)
tapply(honest2_df$honest.value, honest2_df$honest.time, length)

#Just at each time point

#Across Proclamations Time One
tapply(s2$Honest_composite2_t1, s2$Proclamation, mean)
tapply(s2$Honest_composite2_t1, s2$Proclamation, sd)
tapply(s2$Honest_composite2_t1, s2$Proclamation, length)

#Across Proclamations Time One
tapply(s2$Honest_composite2_t2, s2$Proclamation, mean)
tapply(s2$Honest_composite2_t2, s2$Proclamation, sd)
tapply(s2$Honest_composite2_t2, s2$Proclamation, length)
```

# Subset Honesty Data for Simple Effects tests

```{r}
#Subset for main effects tests
abs_exclude2h <- honest2_df %>%
  filter(Proclamation != "absolute") #788 (394 x 2)

flex_exclude2h  <- honest2_df %>%
  filter(Proclamation != "flexible") #758 (379 x 2)

control_exclude2h <- honest2_df %>%
  filter(Proclamation != "control") #710 (355 x 2)

abs_onlyh <- honest2_df %>%
  filter(Proclamation == "absolute") #340 (170 x 2)

flex_onlyh <- honest2_df %>%
  filter(Proclamation == "flexible") #370 (185 x 2)

control_onlyh <- honest2_df %>%
  filter(Proclamation == "control") #418 (209 x 2)

#Main effect of time
#Abs time effect
t.test(honest.value~ honest.time, abs_onlyh, var.equal = TRUE)
t_apa(t.test(honest.value~ honest.time, abs_onlyh, var.equal = TRUE))

#Flex time effect
t.test(honest.value~ honest.time, flex_onlyh, var.equal = TRUE)
t_apa(t.test(honest.value~ honest.time, flex_onlyh, var.equal = TRUE))

#Control  time effect
t.test(honest.value~ honest.time, control_onlyh, var.equal = TRUE)
t_apa(t.test(honest.value~ honest.time, control_onlyh, var.equal = TRUE))

# Main effect: Proclamation

#Abs vs. Flex 
t.test(honest.value ~ Proclamation, control_exclude2h, var.equal = TRUE)
t_apa(t.test(honest.value ~ Proclamation, control_exclude2h, var.equal = TRUE))

#Abs vs. control
t.test(honest.value~ Proclamation, flex_exclude2h, var.equal = TRUE)
t_apa(t.test(honest.value ~ Proclamation, flex_exclude2h, var.equal = TRUE))

#Flex vs. control
t.test(honest.value~ Proclamation, abs_exclude2h, var.equal = TRUE)
t_apa(t.test(honest.value ~ Proclamation, abs_exclude2h, var.equal = TRUE))

#Abs v Flex at Time 2 alone
# Use the control exclude but subset for only time 2
nocontrol_time2h <- control_exclude2h  %>%
  filter(honest.time != "Honest_composite2_t1") #355
# t test
t.test(honest.value ~ Proclamation, nocontrol_time2h, var.equal = TRUE)
t_apa(t.test(honest.value ~ Proclamation, nocontrol_time2h, var.equal = TRUE))

#Control v Flex at Time 2 alone
# Use the control exclude but subset for only time 2
noabs_time2h <- abs_exclude2h  %>%
  filter(honest.time != "Honest_composite2_t1") #394
# t test
t.test(honest.value~ Proclamation, noabs_time2h, var.equal = TRUE)
t_apa(t.test(honest.value~ Proclamation, noabs_time2h, var.equal = TRUE))

#Control v Abs at Time 2 alone
# Use the flex exclude but subset for only time 2
noflex_time2h <- flex_exclude2h %>%
  filter(honest.time != "Honest_composite2_t1") #379
# t test
t.test(honest.value ~ Proclamation, noflex_time2h, var.equal = TRUE)
t_apa(t.test(honest.value~ Proclamation, noflex_time2h, var.equal = TRUE))

```


# Hypocrisy Model

Hypocrisy is just at time two.

```{r}
hypocrisy_2.afex <-aov_car(Hypocrisy_composite2 ~ Proclamation + Error(ID), data= s2)
summary(hypocrisy_2.afex) 
anova_apa(hypocrisy_2.afex) 
```

# Hypocrisy Descriptives

```{r}
#Across Proclamations
tapply(s2$Hypocrisy_composite2, s2$Proclamation, mean)
tapply(s2$Hypocrisy_composite2, s2$Proclamation, sd)
tapply(s2$Hypocrisy_composite2, s2$Proclamation, length)

```

# Hypocrisy Simple Effects -

```{r}
#Subset data for each proc
#Exclude abs
hypo2_noabs <- s2 %>%
  filter(Proclamation != "absolute") #394

hypo2_noflex  <- s2 %>%
  filter(Proclamation != "flexible") #379

hypo2_nocontrol <- s2%>%
  filter(Proclamation != "control") #355

# Main effect: abs vs. flex vs. control
#Abs vs. Flex 
t.test(Hypocrisy_composite2 ~ Proclamation, hypo2_nocontrol, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite2 ~ Proclamation, hypo2_nocontrol, var.equal = TRUE))

#Abs vs. control
t.test(Hypocrisy_composite2 ~ Proclamation, hypo2_noflex, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite2 ~ Proclamation, hypo2_noflex, var.equal = TRUE))

#Flex vs. control
t.test(Hypocrisy_composite2 ~ Proclamation, hypo2_noabs , var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite2 ~ Proclamation, hypo2_noabs , var.equal = TRUE))

```




