---
title: "Supplemental Study 7 (Study 13)"
author: "Elizabeth Huppert"
date: "1/6/2021"
output: pdf_document
---

#Set-up and Read in Data

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-apa
-psych
-dplyr


```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(afex)
library(apa)
library(psych)
library(dplyr)
library(lavaan)

#read in data

s13 <- read.csv(here("HypocrisyStudySI_7.csv")) #265
```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


Key variable names (also see codebook for more information):

1. Proclamation:
Assignment to absolute honesty stance vs. flexible honesty stance vs. control

2. Voting:
Likelihood of voting for Matthew Johnson (1 -7)

3. Discount:
Extent to which participants actually think Matthew Johnson lies (1-7)

4. Goals
Extent to which participants actually think Matthew Johnsons thinks its okay to lie (1-7)

# Factorize Subject (id)

```{r}
s13$ID <- as.factor(s13$ID)
```

# Composite Evaluation Variables 

Items with high agreement were combined as per our pre-registration.

```{r}
#Hypocrisy
hypocrisy2_check <- data.frame(s13$Hypocrisy_1, s13$Hypocrisy_2, s13$Hypocrisy_3, s13$Hypocrisy_4, s13$Hypocrisy_5)
summary(hypocrisy2_check)
describe(hypocrisy2_check)
psych::alpha(hypocrisy2_check) #alpha = 0.89 
s13  <- mutate(s13, Hypocrisy_composite2= 
               ((s13$Hypocrisy_1 + s13$Hypocrisy_2 + s13$Hypocrisy_3 + s13$Hypocrisy_4 +  s13$Hypocrisy_5)/5))

#Morality
moral2_check <- data.frame(s13$Moral_1, s13$Moral_2, s13$Moral_3)
summary(moral2_check)
describe(moral2_check)
psych::alpha(moral2_check) #alpha = 0.94 

s13  <- mutate(s13 , Moral_composite2 = ((s13$Moral_1 + s13$Moral_2 +s13$Moral_3)/3))

#Future Honesty
honesty2_check  <- data.frame(s13$Honest_frequency, s13$Honest_likelihood, s13$Honest_extreme, s13$Honest_committment)
summary(honesty2_check)
describe(honesty2_check)
psych::alpha(honesty2_check) #alpha = 0.74
s13  <- mutate(s13, Honest_composite2 = 
               ((s13$Honest_frequency + s13$Honest_likelihood + s13$Honest_extreme + s13$Honest_committment)/4))

#Social benefit of the proclamation
cor.test(s13$Social_1, s13$Social_2) #r = 0.87

s13  <- mutate(s13 , SI_composite2 = ((s13$Social_1 + s13$Social_2)/2))

```

Evaluation variables:

Hypocrisy_composite2 = hypocrisy composite of 5 items (Ratings: 1-7)
Moral_composite2 = morality composite of 3 items (Ratings: 1-7)
Honest_composite2 = honesty thresholds composite of 4 items (Ratings: 1-7)
SI_composite2 = perceived social benefit of the proclamation composite of 2 items (Ratings: 1-7)


# Voting Intentions Model

```{r}
Voting_2.afex <-aov_car(Voting ~ Proclamation + Error(ID), data= s13 )
summary(Voting_2.afex) 
anova_apa(Voting_2.afex)  
```

# Voting Descriptives

```{r}
#Across Proclamations
tapply(s13$Voting, s13$Proclamation, mean)
tapply(s13$Voting, s13$Proclamation, sd)
tapply(s13$Voting, s13$Proclamation, length)
```

# Voting Simple Effects - Subsetting Data

```{r}
#Subset for main effects tests
abs_exclude <- s13  %>%
  filter(Proclamation != "absolute") #182

flex_exclude  <- s13  %>%
  filter(Proclamation != "flexible") #186 - rarely

control_exclude <- s13  %>%
  filter(Proclamation != "control") #162


# Main effect: abs vs. flex vs. control
#Abs vs. Flex 
t.test(Voting ~ Proclamation, control_exclude, var.equal = TRUE)
t_apa(t.test(Voting ~ Proclamation, control_exclude, var.equal = TRUE))

#Abs vs. control
t.test(Voting ~ Proclamation, flex_exclude, var.equal = TRUE)
t_apa(t.test(Voting ~ Proclamation, flex_exclude, var.equal = TRUE))

#Flex vs. control
t.test(Voting ~ Proclamation, abs_exclude, var.equal = TRUE)
t_apa(t.test(Voting ~ Proclamation, abs_exclude, var.equal = TRUE))

```


# Hypocrisy Model

```{r}
hypocrisy_2.afex <-aov_car(Hypocrisy_composite2 ~ Proclamation + Error(ID), data= s13 )
summary(hypocrisy_2.afex) 
anova_apa(hypocrisy_2.afex)  
```

# Hypocrisy Descriptives

```{r}
#Across Proclamations
tapply(s13$Hypocrisy_composite2, s13$Proclamation, mean)
tapply(s13$Hypocrisy_composite2, s13$Proclamation, sd)
tapply(s13$Hypocrisy_composite2, s13$Proclamation, length)

```

# Hypocrisy Simple Effects - Use Subsetted Data from Voting Intentions Model

```{r}
# Main effect: abs vs. flex vs. control
#Abs vs. Flex 
t.test(Hypocrisy_composite2 ~ Proclamation, control_exclude, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite2 ~ Proclamation, control_exclude, var.equal = TRUE))

#Abs vs. control
t.test(Hypocrisy_composite2 ~ Proclamation, flex_exclude, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite2 ~ Proclamation, flex_exclude, var.equal = TRUE))

#Flex vs. control
t.test(Hypocrisy_composite2 ~ Proclamation, abs_exclude, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite2 ~ Proclamation, abs_exclude, var.equal = TRUE))

```

# Morality Model

Also Cohen's d for morality for post-hoc power.

```{r}
morality_2.afex <-aov_car(Moral_composite2 ~ Proclamation + Error(ID), data= s13 )
summary(morality_2.afex) 
anova_apa(morality_2.afex)

#Abs vs. Flex morality focal - need cohen's D
#abs mean = 2.698795, sd = 1.073977, 83 
#flex mean =  2.392405, sd = 1.100064, 79
#pooled SD = sqrt(((1.073977^2) + (1.100064^2))/2)
sqrt((((1.073977^2) + (1.100064^2))/2)) #1.087099

#cohens = (mean - mean)/SD pooeld
(2.698795-2.392405)/1.087099 #0.282

d2 <- cohens_d(t_test(Moral_composite2 ~ Proclamation, control_exclude)) 
#see Subset Data section below to exclude control and use subsetted data
#comparing abs vs. flex only
d2 #Cohen's d abs. vs. flex. on morality (abs value)  = 0.282, enter 0.28

```

# Morality Descriptives

```{r}
#Across Proclamations
tapply(s13$Moral_composite2, s13$Proclamation, mean)
tapply(s13$Moral_composite2, s13$Proclamation, sd)
tapply(s13$Moral_composite2, s13$Proclamation, length)

```

# Morality Simple Effects - Use Subsetted Data from Voting Intentions Model

```{r}
# Main effect: abs vs. flex vs. control
#Abs vs. Flex 
t.test(Moral_composite2 ~ Proclamation, control_exclude, var.equal = TRUE)
t_apa(t.test(Moral_composite2 ~ Proclamation, control_exclude, var.equal = TRUE))

#Abs vs. control
t.test(Moral_composite2 ~ Proclamation, flex_exclude, var.equal = TRUE)
t_apa(t.test(Moral_composite2 ~ Proclamation, flex_exclude, var.equal = TRUE))

#Flex vs. control
t.test(Moral_composite2 ~ Proclamation, abs_exclude, var.equal = TRUE)
t_apa(t.test(Moral_composite2 ~ Proclamation, abs_exclude, var.equal = TRUE))
```

# Future Honesty Model

```{r}
honesty_2.afex <-aov_car(Honest_composite2 ~ Proclamation + Error(ID), data= s13 )
summary(honesty_2.afex) 
anova_apa(honesty_2.afex)  
```

# Future Honesty Descriptives

```{r}
#Across Proclamations
tapply(s13$Honest_composite2, s13$Proclamation, mean)
tapply(s13$Honest_composite2, s13$Proclamation, sd)
tapply(s13$Honest_composite2, s13$Proclamation, length)

```

# Future Honesty Simple Effects - Use Subsetted Data from Voting Intentions Model

```{r}
# Main effect: abs vs. flex vs. control
#Abs vs. Flex 
t.test(Honest_composite2 ~ Proclamation, control_exclude, var.equal = TRUE)
t_apa(t.test(Honest_composite2 ~ Proclamation, control_exclude, var.equal = TRUE))

#Abs vs. control
t.test(Honest_composite2 ~ Proclamation, flex_exclude, var.equal = TRUE)
t_apa(t.test(Honest_composite2 ~ Proclamation, flex_exclude, var.equal = TRUE))

#Flex vs. control
t.test(Honest_composite2 ~ Proclamation, abs_exclude, var.equal = TRUE)
t_apa(t.test(Honest_composite2 ~ Proclamation, abs_exclude, var.equal = TRUE))
```



# Social Benefit of the Proclamation Model

Use the previously subsetted data from earlier section.

```{r}
SI_2.afex <-aov_car(SI_composite2 ~ Proclamation + Error(ID), data= control_exclude)
summary(SI_2.afex) 
anova_apa(SI_2.afex)
```

# Social Benefit of the Proclamation Descriptives

```{r}
#Across Proclamations
tapply(s13$SI_composite2, s13$Proclamation, mean)
tapply(s13$SI_composite2, s13$Proclamation, sd)
tapply(s13$SI_composite2, s13$Proclamation, length)
```

# Lying Behavior Model (Discounting)

```{r}
Discounting2.afex <-aov_car(Discount ~ Proclamation + Error(ID), data= s13 )
summary(Discounting2.afex) 
anova_apa(Discounting2.afex) 
```

# Lying Behavior (Discounting) Descriptives

```{r}
#Across Proclamations
tapply(s13$Discount, s13$Proclamation, mean)
tapply(s13$Discount, s13$Proclamation, sd)
tapply(s13$Discount, s13$Proclamation, length)
```

# Honesty Intentions (Goals)  Model

```{r}
goals13.afex <-aov_car(Goals ~ Proclamation + Error(ID), data= s13 )
summary(goals13.afex) 
anova_apa(goals13.afex)  
```

# Honesty Intentions (Goals) Descriptives

```{r}
#Across Proclamations
tapply(s13$Goals, s13$Proclamation, mean)
tapply(s13$Goals, s13$Proclamation, sd)
tapply(s13$Goals, s13$Proclamation, length)
```

# Exploratory Continued

See the attached R script "Study2_mediation.R" for the multiple mediation analyses. As mentioned, further analysis notes available upon request. 

