---
title: "Supplemental Study 6 (Study 11)"
author: "Elizabeth Huppert"
date: "8/12/2021"
output: html_document
---

#Set-up

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-psych
-reshape2
-apa
-dplyr
-emmeans

#Load Packages and Data

```{r, include = FALSE}
library(here)
library(tidyverse)
library(psych)
library(reshape2)
library(afex)
library(apa)
library(dplyr)
library(emmeans)

#read in data
s11 <- read.csv(here("HypocrisyStudySI_6.csv"))

```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.

Key Variable Names (also see codebook for more information):

1. Condition:
Assignment to broad vs. specific stance (all absolute)

Condition 1 is broad (never okay to lie)
Condition 2 is specific (never okay to lie about PAC donations)

# Factorize Condition, Sex, Subject (id)

```{r}
s11$condition <- as.factor(s11$condition)
s11$PID <- as.factor(s11$PID)
s11$sex  <- as.factor(s11$sex)

```

# Composite Variables

```{r}
#Hypocrsiy
check_hypocrisy.df <- data.frame(s11$hypocrisy_1, s11$hypocrisy_2, s11$hypocrisy_3, s11$hypocrisy_4, s11$hypocrisy_5)
summary(check_hypocrisy.df)
describe(check_hypocrisy.df)
psych::alpha(check_hypocrisy.df) # alpha = .88 so combined

#Combine for Hypocrisy Composite
s11 <- mutate(s11, hypo_composite = 
                ((s11$hypocrisy_1 + s11$hypocrisy_2 +s11$hypocrisy_3 + s11$hypocrisy_4 + s11$hypocrisy_5)/5))

#Moral
check_moral.df <- data.frame(
  s11$moral_1, s11$moral_2, s11$moral_3)
summary(check_moral.df)
describe(check_moral.df)
psych::alpha(check_moral.df) # alpha = .95 so combined

#Combine for Morality Composite
s11 <- mutate(s11, 
         moral_composite = ((s11$moral_1 + s11$moral_2 + s11$moral_3)/3))
```

# Analysis

# Voting

Descriptives and t-tests:

```{r}
#t-test
t.test(vote_likely  ~ condition, s11, var.equal = TRUE)
t_apa((t.test(vote_likely  ~ condition, s11, var.equal = TRUE)))

#Descriptives
tapply(s11$vote_likely, s11$condition, FUN = mean)
tapply(s11$vote_likely, s11$condition, FUN = sd)

```

# Hypocrisy 

Descriptives and t-tests:

```{r}
#t tests
t.test(hypo_composite  ~ condition, s11, var.equal = TRUE)
t_apa((t.test(hypo_composite ~ condition, s11, var.equal = TRUE)))

#Descriptives
tapply(s11$hypo_composite, s11$condition, FUN = mean)
tapply(s11$hypo_composite, s11$condition, FUN = sd)

```

# Morality

Descriptives and t-tests:

```{r}
#t-test
t.test(moral_composite  ~ condition, s11, var.equal = TRUE)
t_apa((t.test(moral_composite ~ condition, s11, var.equal = TRUE)))

#Descriptives
tapply(s11$moral_composite, s11$condition, FUN = mean)
tapply(s11$moral_composite, s11$condition, FUN = sd)

```


