---
title: "Study 6 and Pilot Study 3 (CivicPulse Data)"
author: "Elizabeth Huppert"
date: "8/17/2021"
output: html_document
---

#Set-up

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-psych
-apa
-dplyr


#Load Packages and Data

```{r}
library(here)
library(tidyverse)
library(afex)
library(psych)
library(apa)
library(dplyr)

CP <- read.csv(here("HypocrisyStudy6_public_access_dataset.csv"))
               
```

Note: The current csv file imported for this analysis is a publicly 
available version of data collected with CivicPulse. We collected Pilot Study 3 and Study 6 as two different modules within the same survey that was sent to government officials, which is why this data is combined. 

This survey also included modules for an unrelated project and those items have been deleted from this dataset for this analysis.

The code for Study 6 is listed first.

# Study 6

# Absolute estimates - variables

Create a numeric trust variable for the questions assessing predictions in the absolute context.

```{r}
#lie_stan_abs 166; NA = 10 
CP$abtrust[CP$Lie_stan_abs_nomedia=="Would not trust me at all"] <- "1"
CP$abtrust[CP$Lie_stan_abs_nomedia=="Would only trust me a little"] <- "2"
CP$abtrust[CP$Lie_stan_abs_nomedia=="Would somewhat trust me"] <-  "3"
CP$abtrust[CP$Lie_stan_abs_nomedia=="Would completely trust me"] <-  "4"
CP$abtrust[CP$Lie_stan_abs_nomedia=="Would mostly trust me"] <- "5"
CP$abtrust <- as.numeric(CP$abtrust) #166

#means without na
cp_omit1 <- CP %>%
  drop_na(abtrust) #N = 156
mean(cp_omit1$abtrust) # mean = 4 
sd(cp_omit1$abtrust) # sd = 1.19
length(cp_omit1$abtrust)

#Post lie, NA = 21
CP$abtrust2[CP$Lie_stan_abs_media=="Would not trust me at all"] <- "1"
CP$abtrust2[CP$Lie_stan_abs_media=="Would only trust me a little"] <- "2"
CP$abtrust2[CP$Lie_stan_abs_media=="Would somewhat trust me"] <-  "3"
CP$abtrust2[CP$Lie_stan_abs_media=="Would completely trust me"] <-  "4"
CP$abtrust2[CP$Lie_stan_abs_media=="Would mostly trust me"] <- "5"
CP$abtrust2 <- as.numeric(CP$abtrust2) #166

#means without na
cp_omit1.2 <- CP %>%
  drop_na(abtrust2) #N = 145
mean(cp_omit1.2$abtrust2) # mean = 2.33 
sd(cp_omit1.2$abtrust2) # sd = 1.46
```


Absolute predictions over time.

```{r}
#Compare change in group by using cp_omit1.2
#Confirm cp_omit1.2 has no NAs left in abstrust (same NA carried over +more)
unique(cp_omit1.2$abtrust) #yes
#look only at the sample with all responses
mean(cp_omit1.2$abtrust)
sd(cp_omit1.2$abtrust)
mean(cp_omit1.2$abtrust2)
sd(cp_omit1.2$abtrust2)
length(cp_omit1.2$abtrust)
length(cp_omit1.2$abtrust2)

#Within subj so paired t-test
t.test(cp_omit1.2$abtrust, cp_omit1.2$abtrust2, paired = TRUE)
t_apa((t.test(cp_omit1.2$abtrust, cp_omit1.2$abtrust2, paired = TRUE)))


```


# Flexible estimates - variables

Create a numeric trust variable for the questions assessing predictions in the flexible context.

```{r}
#lie_stan_rel 166; NA = 14
CP$flextrust[CP$Lie_stan_rel_nomedia=="Would not trust me at all"] <- "1"
CP$flextrust[CP$Lie_stan_rel_nomedia=="Would only trust me a little"] <- "2"
CP$flextrust[CP$Lie_stan_rel_nomedia =="Would somewhat trust me"] <-  "3"
CP$flextrust[CP$Lie_stan_rel_nomedia =="Would completely trust me"] <-  "4"
CP$flextrust[CP$Lie_stan_rel_nomedia =="Would mostly trust me"] <- "5"
CP$flextrust <- as.numeric(CP$flextrust) #166

#means without na
cp_omit2 <- CP %>%
  drop_na(flextrust) #N = 152
mean(cp_omit2$flextrust) # mean = 1.6 
sd(cp_omit2$flextrust) # sd = 1.03


#lie_stan_rel 166; NA = 21 
CP$flextrust2[CP$Lie_stan_rel_media=="Would not trust me at all"] <- "1"
CP$flextrust2[CP$Lie_stan_rel_media=="Would only trust me a little"] <- "2"
CP$flextrust2[CP$Lie_stan_rel_media =="Would somewhat trust me"] <-  "3"
CP$flextrust2[CP$Lie_stan_rel_media =="Would completely trust me"] <-  "4"
CP$flextrust2[CP$Lie_stan_rel_media =="Would mostly trust me"] <- "5"
CP$flextrust2 <- as.numeric(CP$flextrust2) #166

#means without na
cp_omit2.2 <- CP %>%
  drop_na(flextrust2) #N = 145
mean(cp_omit2.2$flextrust2) # mean = 1.6 
sd(cp_omit2.2$flextrust2) # sd = 1.13
length(cp_omit2.2$flextrust2) 
#this df includes 14 NA omitted from first measure too
```

Flexible predictions over time.

```{r}
#look only at the sample with all responses
length(cp_omit2.2$flextrust)
mean(cp_omit2.2$flextrust)
sd(cp_omit2.2$flextrust)
length(cp_omit2.2$flextrust2)
mean(cp_omit2.2$flextrust2)
sd(cp_omit2.2$flextrust2)

#within subj so paired t-test
t.test(cp_omit2.2$flextrust, cp_omit2.2$flextrust2, paired = TRUE) 
t_apa((t.test(cp_omit2.2$flextrust, cp_omit2.2$flextrust2, paired = TRUE)))
```

# Compare Absolute and Flexible Conditions Directly

```{r}
#Different NAs per set
#First, start with cp_omit2.2 since this excludes any NA from flex set
#Now need to drop NAs from abstrust2 here
cp_omit_full <-  cp_omit2.2%>%
  drop_na(abtrust2) # = 138

#Confirm no NAs
unique(cp_omit_full$flextrust)
unique(cp_omit_full$abtrust)
unique(cp_omit_full$flextrust2)
unique(cp_omit_full$abtrust2)

#Now paired t-test on this subset df
t.test(cp_omit_full$abtrust2, cp_omit_full$flextrust2, paired = TRUE) 
t_apa((t.test(cp_omit_full$abtrust2, cp_omit_full$flextrust2, paired = TRUE)))

#Also add Time one 
t.test(cp_omit_full$abtrust, cp_omit_full$flextrust, paired = TRUE) 
t_apa((t.test(cp_omit_full$abtrust, cp_omit_full$flextrust, paired = TRUE)))


```

Now we list the code for Pilot Study 3.

# Pilot Study 3 

# Attitudes Towards Honesty

```{r}
#Lie personal beliefs 166; NA = 32 s
#only never, rarely, sometimes chosen
CP$personalbelief[CP$Lie_pers_belief =="Lying is never okay."] <- "1"
CP$personalbelief[CP$Lie_pers_belief=="Lying is rarely okay."] <- "2"
CP$personalbelief[CP$Lie_pers_belief=="Lying is sometimes okay."] <-  "3"
CP$personalbelief <- as.numeric(CP$personalbelief) #166

#means without na
cp_omit3 <- CP %>%
  drop_na(personalbelief) 
mean(cp_omit3$personalbelief) # mean = 1.4 
sd(cp_omit3$personalbelief) # sd = 0.56
length(cp_omit3$personalbelief) #N = 134
table(cp_omit3$personalbelief)
# never is 87 - 65%
# rarely 42 - 31%
# sometimes 5 - 3%

#frequency with full sample
table(CP$personalbelief, useNA = "ifany")
#never 87
#rarely 42
#sometimes 5
#NA 32

#Proportion out of full sample
#52% never
#25% rarely
#3% sometimes
#19% choose not to response


#Lie behaviors 166; NA = 39
#only never, rarely, sometimes chosen
CP$liebehav[CP$Lie_pers_behav =="I never lie."] <- "1"
CP$liebehav[CP$Lie_pers_behav=="I rarely lie."] <- "2"
CP$liebehav[CP$Lie_pers_behav=="I sometimes lie."] <-  "3"
CP$liebehav <- as.numeric(CP$liebehav) #166

#means without na
cp_omit3.2 <- CP %>%
  drop_na(liebehav) 
mean(cp_omit3.2$liebehav) # mean = 1.6 
sd(cp_omit3.2$liebehav) # sd = 0.60
length(cp_omit3.2$liebehav) #N = 127
table(cp_omit3.2$liebehav)

#Behavior freq
#59 never - 46%
#61 rarely - 48%
#7 sometimes - 6%

#frequency with full sample
table(CP$liebehav, useNA = "ifany")
#Behavior freq - full sample with NA
#59 never - 36%
#61 rarely - 37%
#7 sometimes - 4%
#NA 39 - 23%

#Public beliefs 166; NA = 42 
#only never, rarely, sometimes chosen
CP$public[CP$Lie_pub_trust =="Lying is never okay."] <- "1"
CP$public[CP$Lie_pub_trust=="Lying is rarely okay."] <- "2"
CP$public[CP$Lie_pub_trust=="Lying is sometimes okay."] <-  "3"
CP$public <- as.numeric(CP$public) #166

#means without na
cp_omit3.3 <- CP %>%
  drop_na(public) 
mean(cp_omit3.3$public) # mean = 1.2 
sd(cp_omit3.3$public) # sd = 0.46
length(cp_omit3.3$public) #N = 124
table(cp_omit3.3$public)

#97 never - 78%
#25 rarely - 20%
#2 sometimes - 2%

# with full sample
table(CP$public, useNA = "ifany")
#97 never - 58%
#25 rarely - 15%
#2 sometimes - 1%
#42 NA  - 25%

```

# Compare private v. public differences

```{r}
#Does the proportion of sometimes stance differ in attitudes and public?
#used full sample for this so same
flex_test <- prop.test(x = c(5, 2), n = c(166, 166), correct = TRUE)
flex_test # doesn't differ (also not really appr test since so small)

#does the proportion of sometimes stance differ in behavior and public?
flex_test2 <- prop.test(x = c(7, 2), n = c(166, 166), correct = TRUE)
flex_test2# doesn't differ (also not really appr test since so small)

#does the proportion of the absolute stance differ in attitudes and public?
abs_test <- prop.test(x = c(87, 97), n = c(166, 166), correct = TRUE)
abs_test #no, p =  .32

#does the proportion of the absolute stance differ in behavior and public?
abs_test2 <- prop.test(x = c(59, 97), n = c(166, 166), correct = TRUE)
abs_test2 #yes this does, p < .001

#does the proportion of the absolute stance differ in attitudes and behavior
abs_test3 <- prop.test(x = c(87, 59), n = c(166, 166), correct = TRUE)
abs_test3 #yes, p =  .003

#does the proportion of the rarely stance differ in attitudes and public?
rarely_test <- prop.test(x = c(42, 25), n = c(166, 166), correct = TRUE)
rarely_test #no, p =  .32

#does the proportion of the rarely stance differ in behavior and public?
rarely_test2 <- prop.test(x = c(61, 25), n = c(166, 166), correct = TRUE)
rarely_test2 #yes this does, p < .001
```

# Examine trust between-subjects for only condition shown first

The variable lying-stance refers to the order in which each scenario was presented.

In this variable:
"relative_first" means the flexible condition was shown first.
"absolute_first" means the absolute condition was shown first.

```{r}
#Subset to look at just first scenario
#absolute_first only includes Lie_stan_abs_nomedia and Lie_stan_abs_media
#relative_first only includes lie_rel_nomedia and lie_rel_media
#no media in both variables refers to stance alone
#media in both variables refers to lie (media revealed lie)

#Subset to only absolute_first
btwnsubj_test1 <- cp_omit_full %>%
  filter(lying_stance == "absolute_first") #N = 63

#Remove flexible evaluation from the abs first df
btwnsubj_test1 <- btwnsubj_test1 %>%
  select(-flextrust, -flextrust2)

#Subset to only relevant columns for ease of reshape
btwnsubj_test1 <- btwnsubj_test1 %>%
  select(CP_Survey_ID, abtrust, abtrust2)

#Subset to just flexible = relative_first
btwnsubj_test2 <- cp_omit_full %>%
  filter(lying_stance == "relative_first") #N = 75

#Remove absolute evaluation from the flex first df
btwnsubj_test2 <- btwnsubj_test2 %>%
  select(-abtrust, -abtrust2)

#Subset to only relevant columns for ease of reshape
btwnsubj_test2 <- btwnsubj_test2 %>%
  select(CP_Survey_ID, flextrust, flextrust2)

#Now btwnsubject_test1 only has absolute evaluations for Ps who saw this first
#Now btwnsubject_test2 only has flexible evaluations for Ps who saw this first
#Merge this df, will have N = 138 again but only one set of evaluations/person
btwnsubj_test3 <- bind_rows(btwnsubj_test1, btwnsubj_test2)

#reshape wide to long
#trust time one
btwnsubj_test_long1 <-melt(btwnsubj_test3, 
                id.vars=c("CP_Survey_ID"),
                #measure command is for the DV
                measure.vars=c("abtrust","flextrust"),
                variable.name="stance_eval",
                value.name="stance.value"
)

#trust time two
btwnsubj_test_long2 <-melt(btwnsubj_test3, 
                id.vars=c("CP_Survey_ID"),
                #measure command is for the DV
                measure.vars=c("abtrust2","flextrust2"),
                variable.name="behav_eval",
                value.name="behav.value"
)

#merge btwnsubj_test_long1 and btwnsubj_test_long2
btwnsubj_test_merge <- rbind(btwnsubj_test_long1, btwnsubj_test_long2)

```

