---
title: "Study4"
author: "Elizabeth Huppert"
date: "1/14/2020"
output: pdf_document
---

#Set-up and Read in Data

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-apa
-psych
-dplyr
-emmeans

```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(afex)
library(apa)
library(psych)
library(dplyr)
library(emmeans)

#read in data

s4 <- read.csv(here("HypocrisyStudy4_cleaned.csv"))

```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


# Models

Key variable names (also see codebook for more information):

1. Proclamation:
Assignment to one of three conditions: "Lying is never [rarely/sometimes] okay" (absolute vs. ambitious vs. flexible)

2. Behavior:
Assignment to "prosocial.truth" vs. "selfish.lie" 

3. Behavlie:
selfish lie = 1, prosocial truth = 0

4. rv:
Decisions to RELY (1) or VERIFY (0) in the RV game

5. Sometimes:
Dummy-coded proclamation variable (sometimes = 1, rarely/never = 0)

6. Rarely:
Dummy-coded proclamation variable (rarley = 1, sometimes/never = 0)

7. Never:
Dummy-coded proclamation variable (never = 1, sometimes/rarely = 0)


Supplemental:

Pref = Attitudes towards honesty; 1-5 statement
("Lying is always [often/sometimes/rarely/never] okay" = 1-5)

# Factorize Subject (id) and Trust (rv game pass or rely)

```{r}
s4$ID <- as.factor(s4$ID)
s4$rv_f <- as.factor(s4$rv)
```

#Composite Evaluation Variables

Items with high agreement were combined as per our pre-registration.

```{r}
#Hypocrisy
hypocrisy_4_check  <- data.frame(s4$Hypocrisy_1, s4$Hypocrisy_2, s4$Hypocrisy_3, s4$Hypocrisy_4, s4$Hypocrisy_5)
summary(hypocrisy_4_check)
describe(hypocrisy_4_check)
psych::alpha(hypocrisy_4_check) #alpha = 0.96
s4 <- mutate(s4, Hypocrisy_composite4 = ((s4$Hypocrisy_1 + s4$Hypocrisy_2 + s4$Hypocrisy_3 + s4$Hypocrisy_4 + s4$Hypocrisy_5)/5))
                                            
#Morality
moral_4_check <- data.frame(s4$Moral_1, s4$Moral_2, s4$Moral_3)
summary(moral_4_check)
describe(moral_4_check)
psych::alpha(moral_4_check) #alpha = 0.98
s4 <- mutate(s4, Moral_composite4 = ((s4$Moral_1 + s4$Moral_2 + s4$Moral_3)/3))

#Commitment to Honesty
honest_4_check <- data.frame(s4$Honest_frequency, s4$Honest_likely, s4$Honest_extreme, s4$Honest_committment)
summary(honest_4_check)
describe(honest_4_check)
psych::alpha(honest_4_check) #alpha = 0.92
s4 <- mutate(s4, Honest_composite4 = ((s4$Honest_frequency + s4$Honest_likely + s4$Honest_extreme + s4$Honest_committment)/4))
                                             
#Social Influence
cor.test(s4$Social_benefit1, s4$Social_benefit2) #r = 0.84
s4 <- mutate(s4, SI_composite4 = ((s4$Social_benefit1 + s4$Social_benefit2)/2))

```

Evaluation variables:

Hypocrisy_composite4 = hypocrisy composite of 5 items (Ratings: 1-7)
Moral_composite4 = morality composite of 3 items (Ratings: 1-7)
Honest_composite4 = future honesty composite of 4 items (Ratings: 1-7)
SI_composite4 = social influence composite of 2 items  (Ratings: 1-7)


#Hypocrisy Model

```{r}
#ANOVA
hypocrisy_4.afex <- aov_car(Hypocrisy_composite4 ~ proclamation * behavior + Error(ID), s4)
summary(hypocrisy_4.afex)
anova_apa(hypocrisy_4.afex)

```

#Hypocrisy Descriptives

```{r}
#Cells
tapply(s4$Hypocrisy_composite4, list(s4$proclamation, s4$behavior), mean)
tapply(s4$Hypocrisy_composite4, list(s4$proclamation, s4$behavior), sd)
tapply(s4$Hypocrisy_composite4, list(s4$proclamation, s4$behavior), length)

#Across Proclamation
tapply(s4$Hypocrisy_composite4, s4$proclamation, mean)
tapply(s4$Hypocrisy_composite4, s4$proclamation, sd)
tapply(s4$Hypocrisy_composite4, s4$proclamation, length)

#Across Behavior
tapply(s4$Hypocrisy_composite4, s4$behavior, mean)
tapply(s4$Hypocrisy_composite4, s4$behavior, sd)
tapply(s4$Hypocrisy_composite4, s4$behavior, length)

#Overall
mean(s4$Hypocrisy_composite4)
sd(s4$Hypocrisy_composite4)
length(s4$Hypocrisy_composite4)

```

#Hypocrisy Simple Effects - Subsetting Data

```{r}
#How does behavior vary by proclamation type?
#Subset for main effects tests

never_s4 <- s4 %>%
  filter(proclamation == "never") #201 - never

rarely_s4 <- s4 %>%
  filter(proclamation == "rarely") #197 - rarely

sometimes_s4 <- s4 %>%
  filter(proclamation == "sometimes") #198 - never


#Subset for one level of one factor 

never_exclude_5 <- s4 %>%
  filter(proclamation != "never")  #395, rarely and sometimes

rarely_exclude_5 <- s4 %>%
  filter(proclamation != "rarely") #399, never and sometimes

sometimes_exclude_5 <- s4 %>%
  filter(proclamation != "sometimes") #398, never and rarely


#Selfish lie - rarely vs sometimes
never_lie_5 <- never_exclude_5 %>%
  filter(behavior  == "selfish.lie") #197

#Prosocial truth - rarely vs sometimes
never_truth_5 <- never_exclude_5 %>%
  filter(behavior == "prosocial.truth") #198

#Selfish lie - never vs sometimes
rarely_lie_5 <- rarely_exclude_5 %>%
  filter(behavior == "selfish.lie") #205

#Prosocial truth - never vs sometimes
rarely_truth_5 <- rarely_exclude_5 %>%
  filter(behavior == "prosocial.truth") #194

#Selfish lie - never vs rarely
sometimes_lie_5 <- sometimes_exclude_5 %>%
  filter(behavior == "selfish.lie") #200

#Prosocial truth - never vs rarely
sometimes_truth_5 <- sometimes_exclude_5 %>%
  filter(behavior == "prosocial.truth") #198

```

#Hypocrisy Simple Effects - T-tests

```{r}
#Main effect
#Rarely vs. never
t.test(Hypocrisy_composite4 ~ proclamation, sometimes_exclude_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite4 ~ proclamation, sometimes_exclude_5, var.equal = TRUE))

#Never vs. sometimes  
t.test(Hypocrisy_composite4 ~ proclamation, rarely_exclude_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite4 ~ proclamation, rarely_exclude_5, var.equal = TRUE))

#Rarely vs. sometimes  
t.test(Hypocrisy_composite4 ~ proclamation, never_exclude_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite4 ~ proclamation, never_exclude_5, var.equal = TRUE))


#Within levels of behavior 

#Selfish lie: sometimes vs. rarely
t.test(Hypocrisy_composite4 ~ proclamation, never_lie_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite4 ~ proclamation, never_lie_5, var.equal = TRUE))

#Prosocial truth: sometimes vs. rarely
t.test(Hypocrisy_composite4 ~ proclamation, never_truth_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite4 ~ proclamation, never_truth_5, var.equal = TRUE))

#Selfish lie: sometimes vs. never
t.test(Hypocrisy_composite4 ~ proclamation, rarely_lie_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite4 ~ proclamation, rarely_lie_5, var.equal = TRUE))

#Prosocial truth: sometimes vs. never
t.test(Hypocrisy_composite4 ~ proclamation, rarely_truth_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite4 ~ proclamation, rarely_truth_5, var.equal = TRUE))

#Selfish lie: never vs. rarely
t.test(Hypocrisy_composite4 ~ proclamation, sometimes_lie_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite4 ~ proclamation, sometimes_lie_5, var.equal = TRUE))

#Prosocial truth never vs. rarely
t.test(Hypocrisy_composite4 ~ proclamation, sometimes_truth_5, var.equal = TRUE)
t_apa(t.test(Hypocrisy_composite4 ~ proclamation, sometimes_truth_5, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
hyp_model = aov_ez('ID', 'Hypocrisy_composite4', s4,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(hyp_model)
cellmeans <- emmeans(hyp_model, ~ proclamation|behavior)
print(cellmeans)
mmeans <- emmeans(hyp_model, ~ proclamation)
print(mmeans)
post1 <- emmeans(hyp_model, ~ proclamation)
pairs(post1)  
post2 <- emmeans(hyp_model, ~ proclamation|behavior)
pairs(post2) 
post3 <- emmeans(hyp_model, ~ proclamation*behavior)
pairs(post3) 
```

# Morality Model

```{r}
#ANOVA
moral_4.afex <- aov_car(Moral_composite4 ~ proclamation * behavior + Error(ID), s4)
summary(moral_4.afex)
anova_apa(moral_4.afex)

#Abs vs. Flex morality focal - need cohen's D
#abs mean =   4.222222, sd = 2.116426, 201 
#flex mean =  3.587542, sd = 1.632966 , 198
#pooled SD = sqrt(((2.116426^2) + (1.632966 ^2))/2)
sqrt((((2.116426^2) + (1.632966 ^2))/2)) #1.890217

#cohens = (mean - mean)/SD pooeld
(4.222222-3.587542)/1.890217 #0.335771

d4 <- cohens_d(t_test(Moral_composite4 ~ proclamation, rarely_exclude_5)) 
#see Hypocrisy Simple Effects above to exclude rarely, N = 399
d4 #Cohen's d abs. vs. flex. on morality (abs value)  = 0.3354498 (0.34)

```

# Morality Descriptives

```{r}
#Cells
tapply(s4$Moral_composite4, list(s4$proclamation, s4$behavior), mean)
tapply(s4$Moral_composite4, list(s4$proclamation, s4$behavior), sd)
tapply(s4$Moral_composite4, list(s4$proclamation, s4$behavior), length)

#Across Proclamation
tapply(s4$Moral_composite4, s4$proclamation, mean)
tapply(s4$Moral_composite4, s4$proclamation, sd)
tapply(s4$Moral_composite4, s4$proclamation, length)

#Across behavior
tapply(s4$Moral_composite4, s4$behavior, mean)
tapply(s4$Moral_composite4, s4$behavior, sd)
tapply(s4$Moral_composite4, s4$behavior, length)

#Overall
mean(s4$Moral_composite4)
sd(s4$Moral_composite4)
length(s4$Moral_composite4)

```

# Morality Simple Effects

Note: For these tests, use subsetted data from Hypocrisy simple effects test (previous code chunk).


```{r}
#Main Effect
#Never vs. rarely
t.test(Moral_composite4 ~ proclamation, sometimes_exclude_5, var.equal = TRUE)
t_apa(t.test(Moral_composite4 ~ proclamation, sometimes_exclude_5, var.equal = TRUE))

#Never vs. sometimes 
t.test(Moral_composite4 ~ proclamation, rarely_exclude_5, var.equal = TRUE)
t_apa(t.test(Moral_composite4 ~ proclamation, rarely_exclude_5, var.equal = TRUE))

#Rarely vs. sometimes  
t.test(Moral_composite4 ~ proclamation, never_exclude_5, var.equal = TRUE)
t_apa(t.test(Moral_composite4 ~ proclamation, never_exclude_5, var.equal = TRUE))


#Within levels of behaviors 

#Prosocial truth: rarely vs. sometimes
t.test(Moral_composite4 ~ proclamation, never_truth_5, var.equal = TRUE)
t_apa(t.test(Moral_composite4 ~ proclamation, never_truth_5, var.equal = TRUE))

#Selfish lie: rarely vs. sometimes
t.test(Moral_composite4 ~ proclamation, never_lie_5, var.equal = TRUE)
t_apa(t.test(Moral_composite4 ~ proclamation, never_lie_5, var.equal = TRUE))


#Prosocial truth: never vs. sometimes
t.test(Moral_composite4 ~ proclamation, rarely_truth_5, var.equal = TRUE)
t_apa(t.test(Moral_composite4 ~ proclamation, rarely_truth_5, var.equal = TRUE))

#Selfish lie: never vs. sometimes
t.test(Moral_composite4 ~ proclamation, rarely_lie_5, var.equal = TRUE)
t_apa(t.test(Moral_composite4 ~ proclamation, rarely_lie_5, var.equal = TRUE))

#Prosocial truth: never vs. rarely
t.test(Moral_composite4 ~ proclamation, sometimes_truth_5, var.equal = TRUE)
t_apa(t.test(Moral_composite4 ~ proclamation, sometimes_truth_5, var.equal = TRUE))

#Selfish lie: never vs. rarely
t.test(Moral_composite4 ~ proclamation, sometimes_lie_5, var.equal = TRUE)
t_apa(t.test(Moral_composite4 ~ proclamation, sometimes_lie_5, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
mor_model = aov_ez('ID', 'Moral_composite4', s4,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(mor_model)
cellmeans <- emmeans(mor_model, ~ proclamation|behavior)
print(cellmeans)
mmeans <- emmeans(mor_model, ~ proclamation)
print(mmeans)
post1 <- emmeans(mor_model, ~ proclamation|behavior)
pairs(post1)  
post2 <- emmeans(mor_model, ~ proclamation)
pairs(post2) 
post3 <- emmeans(mor_model, ~ proclamation*behavior)
pairs(post3)
```

#Commitment to Honesty

```{r}
# ANOVA
honesty_4.afex <- aov_car(Honest_composite4 ~ proclamation * behavior + Error(ID), s4)
summary(honesty_4.afex)
anova_apa(honesty_4.afex)
```

# Commitment to Honesty Descriptives

```{r}
#Cells
tapply(s4$Honest_composite4, list(s4$proclamation, s4$behavior), mean)
tapply(s4$Honest_composite4, list(s4$proclamation, s4$behavior), sd)
tapply(s4$Honest_composite4, list(s4$proclamation, s4$behavior), length)

#Across Proclamation
tapply(s4$Honest_composite4, s4$proclamation, mean)
tapply(s4$Honest_composite4, s4$proclamation, sd)
tapply(s4$Honest_composite4, s4$proclamation, length)

#Across Behavior
tapply(s4$Honest_composite4, s4$behavior, mean)
tapply(s4$Honest_composite4, s4$behavior, sd)
tapply(s4$Honest_composite4, s4$behavior, length)

#Overall
mean(s4$Honest_composite4)
sd(s4$Honest_composite4)
length(s4$Honest_composite4)

```

# Commitment to Honesty Simple Effects

Note: For these tests, use subsetted data from Hypocrisy simple effects test (previous code chunk).


```{r}
#Main Effect
#Never vs. rarely
t.test(Honest_composite4  ~ proclamation, sometimes_exclude_5, var.equal = TRUE)
t_apa(t.test(Honest_composite4  ~ proclamation, sometimes_exclude_5, var.equal = TRUE))

#Never vs. sometimes  
t.test(Honest_composite4  ~ proclamation, rarely_exclude_5, var.equal = TRUE)
t_apa(t.test(Honest_composite4  ~ proclamation, rarely_exclude_5, var.equal = TRUE))

#Rarely  vs. sometimes 
t.test(Honest_composite4 ~ proclamation, never_exclude_5, var.equal = TRUE)
t_apa(t.test(Honest_composite4 ~ proclamation, never_exclude_5, var.equal = TRUE))

#Within levels of behavior 

#Prosocial truth: rarely vs. sometimes
t.test(Honest_composite4  ~ proclamation, never_truth_5, var.equal = TRUE)
t_apa(t.test(Honest_composite4  ~ proclamation, never_truth_5, var.equal = TRUE))

#Selfish lie: rarely vs. sometimes
t.test(Honest_composite4  ~ proclamation, never_lie_5, var.equal = TRUE)
t_apa(t.test(Honest_composite4  ~ proclamation, never_lie_5, var.equal = TRUE))

#Prosocial truth: never vs. sometimes
t.test(Honest_composite4  ~ proclamation, rarely_truth_5, var.equal = TRUE)
t_apa(t.test(Honest_composite4  ~ proclamation, rarely_truth_5, var.equal = TRUE))

#Selfish lie: never vs. sometimes
t.test(Honest_composite4  ~ proclamation, rarely_lie_5, var.equal = TRUE)
t_apa(t.test(Honest_composite4  ~ proclamation, rarely_lie_5, var.equal = TRUE))

#Prosocial truth: never vs. rarely
t.test(Honest_composite4 ~ proclamation, sometimes_truth_5, var.equal = TRUE)
t_apa(t.test(Honest_composite4 ~ proclamation, sometimes_truth_5, var.equal = TRUE))

#Selfish lie: never vs. rarely
t.test(Honest_composite4 ~ proclamation, sometimes_lie_5, var.equal = TRUE)
t_apa(t.test(Honest_composite4 ~ proclamation, sometimes_lie_5, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
hon_model = aov_ez('ID', 'Honest_composite4', s4,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(hon_model)
cellmeans <- emmeans(hon_model, ~ proclamation|behavior)
print(cellmeans)
mmeans <- emmeans(hon_model, ~ proclamation)
print(mmeans)
post1 <- emmeans(hon_model, ~ proclamation|behavior)
pairs(post1)  
post2 <- emmeans(hon_model, ~ proclamation)
pairs(post2)  
```

# Social Influence

```{r}
#ANOVA
SI.afex <- aov_car(SI_composite4 ~ proclamation * behavior + Error(ID), s4)
summary(SI.afex )
anova_apa(SI.afex)
```

# Social Influence Descriptives

```{r}
#Cells
tapply(s4$SI_composite4, list(s4$proclamation, s4$behavior), mean)
tapply(s4$SI_composite4, list(s4$proclamation, s4$behavior), sd)
tapply(s4$SI_composite4, list(s4$proclamation, s4$behavior), length)

#Across Proclamation
tapply(s4$SI_composite4, s4$proclamation, mean)
tapply(s4$SI_composite4, s4$proclamation, sd)
tapply(s4$SI_composite4, s4$proclamation, length)

#Across Behavior
tapply(s4$SI_composite4, s4$behavior, mean)
tapply(s4$SI_composite4, s4$behavior, sd)
tapply(s4$SI_composite4, s4$behavior, length)

#Overall
mean(s4$SI_composite4)
sd(s4$SI_composite4)
length(s4$SI_composite4)

```

# Social Benefit Simple Effects 

Note: For these tests, use subsetted data from Hypocrisy simple effects test (previous code chunk).


```{r}
#Proclamation within subsetted data
#Never vs. rarely
t.test(SI_composite4  ~ proclamation, sometimes_exclude_5, var.equal = TRUE)
t_apa(t.test(SI_composite4  ~ proclamation, sometimes_exclude_5, var.equal = TRUE))

#Never vs. sometimes  
t.test(SI_composite4  ~ proclamation, rarely_exclude_5, var.equal = TRUE)
t_apa(t.test(SI_composite4  ~ proclamation, rarely_exclude_5, var.equal = TRUE))

#Rarely vs. sometimes 
t.test(SI_composite4 ~ proclamation, never_exclude_5, var.equal = TRUE)
t_apa(t.test(SI_composite4 ~ proclamation, never_exclude_5, var.equal = TRUE))

#Within levels of behavior 

#Prosocial truth: rarely vs. sometimes
t.test(SI_composite4  ~ proclamation, never_truth_5, var.equal = TRUE)
t_apa(t.test(SI_composite4  ~ proclamation, never_truth_5, var.equal = TRUE))

#Selfish lie: rarely vs. sometimes
t.test(SI_composite4  ~ proclamation, never_lie_5, var.equal = TRUE)
t_apa(t.test(SI_composite4  ~ proclamation, never_lie_5, var.equal = TRUE))

#Prosocial truth: never vs. sometimes
t.test(SI_composite4  ~ proclamation, rarely_truth_5, var.equal = TRUE)
t_apa(t.test(SI_composite4  ~ proclamation, rarely_truth_5, var.equal = TRUE))

#Selfish lie: never vs. sometimes
t.test(SI_composite4  ~ proclamation, rarely_lie_5, var.equal = TRUE)
t_apa(t.test(SI_composite4  ~ proclamation, rarely_lie_5, var.equal = TRUE))

#Prosocial truth: never vs. rarely
t.test(SI_composite4 ~ proclamation, sometimes_truth_5, var.equal = TRUE)
t_apa(t.test(SI_composite4 ~ proclamation, sometimes_truth_5, var.equal = TRUE))

#Selfish lie: never vs. rarely
t.test(SI_composite4 ~ proclamation, sometimes_lie_5, var.equal = TRUE)
t_apa(t.test(SI_composite4 ~ proclamation, sometimes_lie_5, var.equal = TRUE))

#Alternative ANOVA and tukey post-hoc tests
SI_model = aov_ez('ID', 'SI_composite4', s4,
                    within = c (),
                    between = c ('proclamation', 'behavior'),
                    anova_table = list(es = 'pes'))
print(SI_model)
means <- emmeans(SI_model, ~ proclamation)
print(means)
post1 <- emmeans(SI_model, ~ proclamation)
pairs(post1)  

```

# Behavior in the RELY-or-VERIFY game

```{r}
# Reported Model
rv_4.glm <- glm(rv_f ~ sometimes + rarely + behavlie 
                + sometimes*behavlie + rarely*behavlie, 
                data=s4, family = binomial(link = "logit"))
summary(rv_4.glm)

# Replicate with factorized dummy variables to confirm 
s4$sometimes_f <- as.factor(s4$sometimes)
s4$rarely_f <- as.factor(s4$rarely)
s4$behavlie_f <- as.factor(s4$behavlie)

#re-run model
rv_4_test.glm <- glm(rv_f ~ sometimes_f + rarely_f + behavlie_f 
                + sometimes_f*behavlie_f + rarely_f*behavlie_f, 
                data=s4, family = binomial(link = "logit"))
summary(rv_4_test.glm)

#Exploratory
rv.glm4_2 <- glm(rv ~ never + rarely + behavlie + 
                never*behavlie + rarely*behavlie,
              data=s4, family = binomial(link = "logit"))
summary(rv.glm4_2)

# Replicate with factorized dummy variables to confirm 
s4$never_f <- as.factor(s4$never)

rv_test.glm4_2 <- glm(rv ~ never_f + rarely_f + behavlie_f + 
                never_f*behavlie_f + rarely_f*behavlie_f,
              data=s4, family = binomial(link = "logit"))
summary(rv_test.glm4_2)

#Frequencies - proclamation
table(s4$proclamation, s4$rv_f) 

#never rely:  95/201, 47%
#rarely rely: 83/197, 42%
#sometimes rely: 61/198, 31%


#never 106/201 verify, 53%
#rarely 114/197  verify, 58%
#sometimes 137/198 verify, 69%

#Frequencies proclamation and behavior by cell
table(s4$proclamation, s4$behavior, s4$rv_f)
table(s4$behavior, s4$rv_f) 

#178 prosocial rely, 117 verify - 178/295; 60%
#61 selfish rely, 240 selfish verify - 61/01 - 20%

```

#Attitudes Towards Honesty Measure

#Distribution of Responses

```{r}
#Distributions

table(s4$pref)
#109 "never" (5) / 596, 18%
#330 "rarely" (4) / 596, 55%
#144 "sometimes" (3) / 596, 24%
#9 "often" (2) 
#4 "always" (1)

```


#Center honesty preferences for use in models

```{r}
s4 <- mutate(s4, pref.center = scale(s4$pref))
s4 <- mutate(s4, pref.center.2 = scale(s4$pref, scale = FALSE))

```

# SI Appendix 3 - Regressions

```{r}
#Preferences Regression - Hypocrisy
#Scaled by mean and SD
hypocrisy_4.lm <- lm(Hypocrisy_composite4 ~ sometimes*pref.center, data= s4)
summary(hypocrisy_4.lm )

#Mean centered
hypocrisy_4.lm2 <- lm(Hypocrisy_composite4 ~ sometimes*pref.center.2, data= s4)
summary(hypocrisy_4.lm2)


#Look at mean hypocrisy ratings by proclamation and preferences 
tapply(s4$Hypocrisy_composite4, list(s4$proclamation, s4$pref), mean)
tapply(s4$Hypocrisy_composite4, list(s4$proclamation, s4$pref), sd)
tapply(s4$Hypocrisy_composite4, list(s4$sometimes, s4$pref), mean)
tapply(s4$Hypocrisy_composite4, s4$proclamation, mean)
tapply(s4$Hypocrisy_composite4, s4$pref, mean)
tapply(s4$Hypocrisy_composite4, s4$rarely, mean)
tapply(s4$Hypocrisy_composite4, s4$rarely, sd)
tapply(s4$Hypocrisy_composite4, s4$sometimes, mean)
tapply(s4$Hypocrisy_composite4, s4$sometimes, sd)

#Preferences Regression - Morality
#Scaled by mean and SD
moral_4.lm <- lm(Moral_composite4 ~ sometimes*pref.center, data= s4)
summary(moral_4.lm)

#Mean centered
moral_4.lm2 <- lm(Moral_composite4 ~ sometimes*pref.center.2, data= s4)
summary(moral_4.lm2)

#Look at mean morality ratings by proclamation and preferences 
tapply(s4$Moral_composite4, list(s4$proclamation, s4$pref), mean)
tapply(s4$Moral_composite4, list(s4$proclamation, s4$pref), sd)
tapply(s4$Moral_composite4, list(s4$sometimes, s4$pref), mean)
tapply(s4$Moral_composite4, s4$proclamation, mean)
tapply(s4$Moral_composite4, s4$sometimes, mean)
tapply(s4$Moral_composite4, s4$sometimes, sd)
tapply(s4$Moral_composite4, s4$rarely, mean)
tapply(s4$Moral_composite4, s4$rarely, sd)


#Preferences Regression - Commitment to Honesty
#Scaled by mean and SD
honest_4.lm <- lm(Honest_composite4 ~ sometimes*pref.center, data= s4)
summary(honest_4.lm)

#Mean centered
honest_4.lm2 <- lm(Honest_composite4 ~ sometimes*pref.center.2, data= s4)
summary(honest_4.lm2)

#Look at mean commitment to honesty ratings by proclamation and preferences 
tapply(s4$Honest_composite4, list(s4$proclamation, s4$pref), mean)
tapply(s4$Honest_composite4, list(s4$proclamation, s4$pref), sd)
tapply(s4$Honest_composite4, list(s4$sometimes, s4$pref), mean)
tapply(s4$Honest_composite4, s4$proclamation, mean)
tapply(s4$Honest_composite4, s4$sometimes, mean)
tapply(s4$Honest_composite4, s4$sometimes, sd)
tapply(s4$Honest_composite4, s4$rarely, mean)
tapply(s4$Honest_composite4, s4$rarely, sd)


#Preferences Regression - Social Benefit (SI)
#Scaled by mean and SD
SI.lm <- lm(SI_composite4 ~ sometimes*pref.center, data= s4)
summary(SI.lm )

#Mean centered
SI.lm2 <- lm(SI_composite4 ~ sometimes*pref.center.2, data= s4)
summary(SI.lm2)

#Look at mean SI ratings by proclamation and preferences 
tapply(s4$SI_composite4, list(s4$proclamation, s4$pref), mean)
tapply(s4$SI_composite4, list(s4$proclamation, s4$pref), sd)
tapply(s4$SI_composite4, s4$sometimes, mean)
tapply(s4$SI_composite4, s4$sometimes, sd)
tapply(s4$SI_composite4, s4$rarely, mean)
tapply(s4$SI_composite4, s4$rarely, sd) 


#Logistic Regression (trust) with own attitudes towards honesty
rv4.4.glm <- glm(rv_f ~ sometimes*pref.center,
              data=s4, family = binomial(link = "logit"))
summary(rv4.4.glm) 

#Frequencies
table(s4$rv_f, s4$pref, s4$sometimes)
#0 = verify, 1 = rely
table(s4$rv_f, s4$pref, s4$proclamation)
#Percentages RELY on never
#always 1/4 25%
#often 1/9 11%
#sometimes 15/144 10%
#rarely 45/330 14%
#never 33/109 30%

#Percentages that RELY on rarely
#always 1/4 25%
#often 1/9 11%
#sometimes 8/144 6%
#rarely 62/330 19%
#never 11/109 10%

#note that separate tables 0 = never/rarely, 1 = sometimes; 
#within tables, 0 = verify, 1 = rely
#total per cell
table(s4$pref)

#Percentages RELY on never/rarely
#always 2/4, 50%
#often, 2/9 22%
#sometimes, 23/144 16%
#rarely, 107/330 32%
#never, 44/109, 40%

#Percentages RELY on sometimes
#always 0/4, 0%
#often, 1/9 11%
#sometimes, 26/144 18%
#rarely, 30/330 9%
#never, 4/109 4%
```

#Attitudes as a Covariate - exploration

```{r}
#Preferences Covariate - Hypocrisy
Hypocrisy4.pref.center <- aov_car(Hypocrisy_composite4 ~ proclamation * behavior + pref.center + Error(ID), s4, factorize = FALSE, anova_table = list(es = "pes"))
summary(Hypocrisy4.pref.center)

#Preferences Covariate- Morality
Moral4.pref.center <- aov_car(Moral_composite4 ~ proclamation * behavior + pref.center + Error(ID), s4, factorize = FALSE, anova_table = list(es = "pes"))
summary(Moral4.pref.center)

#Preferences Covariate - Future honesty
honest4.pref.center <- aov_car(Honest_composite4 ~ proclamation * behavior + pref.center + Error(ID), s4, factorize = FALSE, anova_table = list(es = "pes"))
summary(honest4.pref.center)

#Preferences Covariate - SI
SI.pref.center <- aov_car(SI_composite4 ~ proclamation * behavior + pref.center + Error(ID), s4, factorize = FALSE, anova_table = list(es = "pes"))
summary(SI.pref.center)

```

#Notes

The moderated mediation models on moral character and trust behavior were conducted in SPSS. The syntax is copied below for use within SPSS.

# Syntax

Study 4 Trust: First, Open "HypocrisyStudy4_cleaned.xlsx" within SPSS. This excel file is available in this R project and on the OSF page for this project. Then run the code below.

*1. Recreate composite variables*

COMPUTE Hypocrisy_C=MEAN(Hypocrisy_1,Hypocrisy_2,Hypocrisy_3,Hypocrisy_4,Hypocrisy_5).
EXECUTE.

COMPUTE Honesty_C=MEAN(Honest_frequency,Honest_likely,Honest_extreme,Honest_committment).
EXECUTE.

COMPUTE SocBen_C=MEAN(Social_benefit1, Social_benefit2).
EXECUTE.

*2. Run mediation analysis to get indirect effects. - use point and click within Process Macro*

*Run Hayes’ (2017) PROCESS Macro for SPSS, Model 7, 10,000 bootstraps*
IV = sometimes
M1 = Honesty_C
M2 = Hypocrisy_C
M3 = SocBen_C
Y = rv
W = behavlie

*3. Run regressions to get X-->M and M-->Y pathways for each level of moderator.*

SORT CASES  BY behavlie.
SPLIT FILE LAYERED BY behavlie.

*Test M-->Y pathways*

LOGISTIC REGRESSION VARIABLES rv
  /METHOD=ENTER Hypocrisy_C Honesty_C sometimes  SocBen_C
  /CRITERIA=PIN(.05) POUT(.10) ITERATE(20) CUT(.5).


*Test X-->M1 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Honesty_C
  /METHOD=ENTER sometimes.

*Test X-->M2 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Hypocrisy_C
  /METHOD=ENTER sometimes.


*Test X-->M3 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT  SocBen_C
  /METHOD=ENTER sometimes.
  
Study 4 Morality: Use the same data file in SPSS.

*1. Recreate composite variables*

COMPUTE Hypocrisy_C=MEAN(Hypocrisy_1,Hypocrisy_2,Hypocrisy_3,Hypocrisy_4,Hypocrisy_5).
EXECUTE.

COMPUTE Honesty_C=MEAN(Honest_frequency,Honest_likely,Honest_extreme,Honest_committment).
EXECUTE.

COMPUTE SocBen_C=MEAN(Social_benefit1, Social_benefit2).
EXECUTE.

COMPUTE Moral_C=MEAN(Moral_1, Moral_2, Moral_3).
EXECUTE.

*2. Run mediation analysis to get indirect effects. - use point and click within Process Macro*

*Run Hayes’ (2016) PROCESS Macro for SPSS, Model 7, 10,000 bootstraps*
X = sometimes
M1 = Hypocrisy_C
M2 = Honesty_C
M3 = SocBen_C
Y = Moral_C
W = behavlie

*3. Run regressions to get X-->M and M-->Y pathways for each level of moderator.*

SORT CASES  BY behavlie.
SPLIT FILE LAYERED BY behavlie.

*Test M-->Y pathways*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Moral_C
  /METHOD=ENTER Hypocrisy_C Honesty_C sometimes  SocBen_C.

*Test X-->M1 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Hypocrisy_C
  /METHOD=ENTER sometimes.

*Test X-->M2 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT Honesty_C
  /METHOD=ENTER sometimes.


*Test X-->M3 pathway*

REGRESSION
  /MISSING LISTWISE
  /STATISTICS COEFF OUTS R ANOVA
  /CRITERIA=PIN(.05) POUT(.10)
  /NOORIGIN 
  /DEPENDENT  SocBen_C
  /METHOD=ENTER sometimes.
  
  
