---
title: "Supplemental Study 1 (Study 6)"
author: "Elizabeth Huppert"
date: "5/4/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Set-up

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-psych
-reshape2
-apa
-psych
-dplyr


```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(psych)
library(reshape2)
library(afex)
library(apa)
library(psych)
library(dplyr)

#read in data

s6 <- read.csv(here("HypocrisyStudySI_1.csv"))

```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.


# Models

Key variable names (also see codebook for more information):

1. Proclamation:
Assignment to absolute honesty vs. control 

2. Lie.motives:
Reasons for lying in the deception game: prosocial vs. selfish motives

3.Hypocrisy_1:
This person is a hypocrite. (Ratings: 1-7)

4. Guilt:
This person felt uncomfortable about the decision to SEND a dishonest message. (Ratings: 1-7)

5. Moral:
Moral  (Ratings: 1-7)

6. Trustbeh:
KEEP or PASS in The Coin Flip Game, (0 = KEEP, 1 = PASS)

# Composite evaluation variables

Items with high agreement were combined as per our pre-registration.

```{r}
#Attitudinal Trust
cor.test(s6$trust_1, s6$trust_2) #r = 0.95
s6<- mutate(s6, att_trust = ((s6$trust_1 + s6$trust_2)/2))

#Benevolence
Benveolence_df <- data.frame(s6$benevolence_1, s6$benevolence_2, s6$benevolence_3)
summary(Benveolence_df )
describe(Benveolence_df )
psych::alpha(Benveolence_df ) #alpha = 0.79
s6 <- mutate(s6, Benevolence_composite = ((s6$benevolence_1 + s6$benevolence_2 + s6$benevolence_3)/3))

```

att_trust = composite of 2 items of trust items (Ratings: 1-7)
Benevolence_composite = composite of 3 items of benevolence (Ratings: 1-7)

# Hypocrisy Model

```{r}
#ANOVA
hypocrisy6.aov <-aov_car(hypocrisy_1 ~ proclamation*lie.motives + Error(ID), data=s6)
summary(hypocrisy6.aov) 
anova_apa(hypocrisy6.aov)

```

# Hypocrisy Descriptives

```{r}
#Cells
tapply(s6$hypocrisy_1, list(s6$proclamation, s6$lie.motives), FUN = length)
tapply(s6$hypocrisy_1, list(s6$proclamation, s6$lie.motives), FUN = mean)
tapply(s6$hypocrisy_1, list(s6$proclamation, s6$lie.motives), FUN = sd)

#Across Proclamation
tapply(s6$hypocrisy_1, s6$proclamation,FUN = length)
tapply(s6$hypocrisy_1, s6$proclamation,FUN = mean)
tapply(s6$hypocrisy_1, s6$proclamation,FUN = sd)

#Across Lie.motives
tapply(s6$hypocrisy_1, s6$lie.motives,FUN = length)
tapply(s6$hypocrisy_1, s6$lie.motives,FUN = mean)
tapply(s6$hypocrisy_1, s6$lie.motives,FUN = sd)

#Overall
mean(s6$hypocrisy_1)
sd(s6$hypocrisy_1)
length(s6$hypocrisy_1)

```

# Morality Model


```{r}
#ANOVA
morality1.aov <-aov_car(moral ~ proclamation*lie.motives + Error(ID), data=s6)
summary(morality1.aov)
anova_apa(morality1.aov)
```

# Morality Descriptives

```{r}
#Cells
tapply(s6$moral, list(s6$proclamation, s6$lie.motives), FUN = mean)
tapply(s6$moral, list(s6$proclamation, s6$lie.motives), FUN = sd)
tapply(s6$moral, list(s6$proclamation, s6$lie.motives), FUN = length)

#Across Proclamation
tapply(s6$moral, s6$proclamation,FUN = length)
tapply(s6$moral, s6$proclamation,FUN = mean)
tapply(s6$moral, s6$proclamation,FUN = sd)

#Across Lie.motives
tapply(s6$moral, s6$lie.motives,FUN = length)
tapply(s6$moral, s6$lie.motives,FUN = mean)
tapply(s6$moral, s6$lie.motives,FUN = sd)

#Overall
mean(s6$moral)
sd(s6$moral)
length(s6$moral)

```

# Guilt Model

```{r}
#ANOVA
discomfort1.aov <-aov_car(discomfort_1 ~ proclamation*lie.motives + Error(ID), data=s6)
summary(discomfort1.aov)
anova_apa(discomfort1.aov)
```

# Descriptives Guilt

```{r}
#Cells
tapply(s6$discomfort_1, list(s6$proclamation, s6$lie.motives), FUN = mean)
tapply(s6$discomfort_1, list(s6$proclamation, s6$lie.motives), FUN = sd)
tapply(s6$discomfort_1, list(s6$proclamation, s6$lie.motives), FUN = length)

#Across Proclamation
tapply(s6$discomfort_1, s6$proclamation,FUN = length)
tapply(s6$discomfort_1, s6$proclamation,FUN = mean) 
tapply(s6$discomfort_1, s6$proclamation,FUN = sd)

#Across Lie.motives
tapply(s6$discomfort_1, s6$lie.motives,FUN = length)
tapply(s6$discomfort_1, s6$lie.motives,FUN = mean)
tapply(s6$discomfort_1, s6$lie.motives,FUN = sd)

#Overall
mean(s6$discomfort_1)
sd(s6$discomfort_1)
length(s6$discomfort_1)

```

# Attitudinal Trust

```{r}
#ANOVA
trust1.aov <-aov_car(att_trust ~ proclamation*lie.motives + Error(ID), data=s6)
summary(trust1.aov)
anova_apa(trust1.aov)
```

# Attitudinal Trust Descriptives

```{r}
#Cells
tapply(s6$att_trust, list(s6$proclamation, s6$lie.motives), FUN = mean)
tapply(s6$att_trust, list(s6$proclamation, s6$lie.motives), FUN = sd)
tapply(s6$att_trust, list(s6$proclamation, s6$lie.motives), FUN = length)

#Across Proclamation
tapply(s6$att_trust, s6$proclamation,FUN = length)
tapply(s6$att_trust, s6$proclamation,FUN = mean) 
tapply(s6$att_trust, s6$proclamation,FUN = sd)

#Across Lie.motives
tapply(s6$att_trust, s6$lie.motives,FUN = length)
tapply(s6$att_trust, s6$lie.motives,FUN = mean)
tapply(s6$att_trust, s6$lie.motives,FUN = sd)

#Overall
mean(s6$att_trust)
sd(s6$att_trust)
length(s6$att_trust)

```

# Benevolence

```{r}
#ANOVA
ben.aov <- aov(Benevolence_composite ~ proclamation*lie.motives, data = s6)
summary(ben.aov)
anova_apa(ben.aov)
```

#Benevolence Descriptives

```{r}
#Cells
tapply(s6$Benevolence_composite, list(s6$proclamation, s6$lie.motives), FUN = mean)
tapply(s6$Benevolence_composite, list(s6$proclamation, s6$lie.motives), FUN = sd)
tapply(s6$Benevolence_composite, list(s6$proclamation, s6$lie.motives), FUN = length)

#Across Proclamation
tapply(s6$Benevolence_composite, s6$proclamation,FUN = length)
tapply(s6$Benevolence_composite, s6$proclamation,FUN = mean) 
tapply(s6$Benevolence_composite, s6$proclamation,FUN = sd)

#Across Lie.motives
tapply(s6$Benevolence_composite, s6$lie.motives,FUN = length)
tapply(s6$Benevolence_composite, s6$lie.motives,FUN = mean)
tapply(s6$Benevolence_composite, s6$lie.motives,FUN = sd)

#Overall
mean(s6$Benevolence_composite)
sd(s6$Benevolence_composite)
length(s6$Benevolence_composite)

```

# The Choice Game

```{r}
#Logistic regression
model.1 <- glm(trustbeh ~ proclamation*lie.motives, data=s6, family = binomial(link = "logit"))
summary(model.1)

#Follow-ups
chisq.test(s6$lie.motives, s6$trustbeh)
table(s6$lie.motives, s6$trustbeh)
table(s6$proclamation, s6$lie.motives, s6$trustbeh)

```


#Mediation

See R script Study6_mediation.R for mediation results.
