---
title: "Supplemental Study 6 (Study 12)"
author: "Elizabeth Huppert"
date: "8/12/2021"
output: html_document
---

#Set-up

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-psych
-reshape2
-apa
-dplyr
-emmeans

#Load Packages and Data

```{r, include = FALSE}
library(here)
library(tidyverse)
library(psych)
library(reshape2)
library(afex)
library(apa)
library(dplyr)
library(emmeans)

#read in data
s12 <- read.csv(here("HypocrisyStudySI_6.csv"))

```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.

Key Variable Names (also see codebook for more information):

1. Condition:
Assignment to broad vs. specific stance (all absolute)

Condition 1 is broad (never okay to lie)
Condition 2 is specific (never okay to lie about PAC donations)

# Factorize Condition, Sex, Subject (id)

```{r}
s12$condition <- as.factor(s12$condition)
s12$PID <- as.factor(s12$PID)
s12$sex  <- as.factor(s12$sex)

```

# Composite Variables

```{r}
#Hypocrisy
check_hypocrisy.df <- data.frame(s12$hypocrisy_1, s12$hypocrisy_2, s12$hypocrisy_3, s12$hypocrisy_4, s12$hypocrisy_5)
summary(check_hypocrisy.df)
describe(check_hypocrisy.df)
psych::alpha(check_hypocrisy.df) # alpha = .88 so combined

#Combine for Hypocrisy Composite
s12 <- mutate(s12, hypo_composite = 
                ((s12$hypocrisy_1 + s12$hypocrisy_2 +s12$hypocrisy_3 + s12$hypocrisy_4 + s12$hypocrisy_5)/5))

#Moral
check_moral.df <- data.frame(
  s12$moral_1, s12$moral_2, s12$moral_3)
summary(check_moral.df)
describe(check_moral.df)
psych::alpha(check_moral.df) # alpha = .95 so combined

#Combine for Morality Composite
s12 <- mutate(s12, 
         moral_composite = ((s12$moral_1 + s12$moral_2 + s12$moral_3)/3))
```


Evaluation variables:

hypo_composite = hypocrisy composite of 5 items 
moral_composite = morality composite of 3 items 

# Analysis

# Voting Intentions Model and Descriptives

Descriptives and t-tests:

```{r}
#t-test
t.test(vote_likely  ~ condition, s12, var.equal = TRUE)
t_apa((t.test(vote_likely  ~ condition, s12, var.equal = TRUE)))

#Descriptives
tapply(s12$vote_likely, s12$condition, FUN = mean)
tapply(s12$vote_likely, s12$condition, FUN = sd)

```

# Hypocrisy Model and Descriptives

Descriptives and t-tests:

```{r}
#t tests
t.test(hypo_composite  ~ condition, s12, var.equal = TRUE)
t_apa((t.test(hypo_composite ~ condition, s12, var.equal = TRUE)))

#Descriptives
tapply(s12$hypo_composite, s12$condition, FUN = mean)
tapply(s12$hypo_composite, s12$condition, FUN = sd)

```

# Morality Model and Descriptives

Descriptives and t-tests:

```{r}
#t-test
t.test(moral_composite  ~ condition, s12, var.equal = TRUE)
t_apa((t.test(moral_composite ~ condition, s12, var.equal = TRUE)))

#Descriptives
tapply(s12$moral_composite, s12$condition, FUN = mean)
tapply(s12$moral_composite, s12$condition, FUN = sd)

```


