---
title: "Supplemental Study 5 (Study 10)"

author: "Elizabeth Huppert"
date: "8/9/2021"
output: html_document
---
#Set-up

You need to install the following packages to run this code:

-here
-tidyverse
-afex
-psych
-reshape2
-apa
-dplyr
-emmeans

#Load Packages and Data

```{r, include = FALSE}
library(here)
library(tidyverse)
library(psych)
library(reshape2)
library(afex)
library(apa)
library(dplyr)
library(emmeans)

#read in data

s10 <- read.csv(here("HypocrisyStudySI_5.csv"))

```

Note: The current csv file imported for this analysis reflects cleaned data. 
The raw data and more information about the cleaning/coding of variables that went into making the current clean csv file is available in the Excel codebook. Additionally, more information is available upon request.

Models

Key Variable Names (also see codebook for more information):

1. Condition:
Assignment to absolute vs. flexible honesty stance

#Re-code condition for ease of interpretation - "proc"

```{r}
hypo_SI5$proc[hypo_SI5$condition=="1"] <- "absolute"
hypo_SI5$proc[hypo_SI5$condition=="2"] <- "flexible"
```

# Factorize Country

```{r}
hypo_SI5$Country <- as.factor(hypo_SI5$Country)
```

# Composite variables

```{r}
#time point 1 - hypocrisy
#hypocrisy_1 - this person is a hypocrite
hypo_SI5$h1[hypo_SI5$hypocrite=="Strongly disagree"] <- "1"
hypo_SI5$h1[hypo_SI5$hypocrite=="Disagree"] <- "2"
hypo_SI5$h1[hypo_SI5$hypocrite=="Somewhat disagree"] <- "3"
hypo_SI5$h1[hypo_SI5$hypocrite=="Neither agree nor disagree"] <- "4"
hypo_SI5$h1[hypo_SI5$hypocrite=="Somewhat agree"] <- "5"
hypo_SI5$h1[hypo_SI5$hypocrite=="Agree"] <- "6"
hypo_SI5$h1[hypo_SI5$hypocrite=="Strongly agree"] <- "7"
hypo_SI5$h1 <- as.numeric(hypo_SI5$h1)
#inauthentic
hypo_SI5$h2[hypo_SI5$inauthentic=="Strongly disagree"] <- "1"
hypo_SI5$h2[hypo_SI5$inauthentic=="Disagree"] <- "2"
hypo_SI5$h2[hypo_SI5$inauthentic=="Somewhat disagree"] <- "3"
hypo_SI5$h2[hypo_SI5$inauthentic=="Neither agree nor disagree"] <- "4"
hypo_SI5$h2[hypo_SI5$inauthentic=="Somewhat agree"] <- "5"
hypo_SI5$h2[hypo_SI5$inauthentic=="Agree"] <- "6"
hypo_SI5$h2[hypo_SI5$inauthentic=="Strongly agree"] <- "7"
hypo_SI5$h2 <- as.numeric(hypo_SI5$h2)
#disingenuous
hypo_SI5$h3[hypo_SI5$disingenuous=="Strongly disagree"] <- "1"
hypo_SI5$h3[hypo_SI5$disingenuous=="Disagree"] <- "2"
hypo_SI5$h3[hypo_SI5$disingenuous=="Somewhat disagree"] <- "3"
hypo_SI5$h3[hypo_SI5$disingenuous=="Neither agree nor disagree"] <- "4"
hypo_SI5$h3[hypo_SI5$disingenuous=="Somewhat agree"] <- "5"
hypo_SI5$h3[hypo_SI5$disingenuous=="Agree"] <- "6"
hypo_SI5$h3[hypo_SI5$disingenuous=="Strongly agree"] <- "7"
hypo_SI5$h3 <- as.numeric(hypo_SI5$h3)
#cronbachs alpha for 3  hypocrisy items - time one
hypoSI5_df <- data.frame(hypo_SI5$h1, hypo_SI5$h2, hypo_SI5$h3)
summary(hypoSI5_df)
describe(hypoSI5_df)
psych::alpha(hypoSI5_df) # raw = 0.95
#hypocrisy items over 0.6 so create a composite
hypo_SI5 <- mutate(hypo_SI5, 
                   SI5_hcomposite = 
                     ((hypo_SI5$h1+hypo_SI5$h2+hypo_SI5$h3)/3))

#time two hypocrisy
#hypo_2 - this person is a hypocrite
hypo_SI5$h1.2[hypo_SI5$hypo_2 =="Strongly disagree"] <- "1"
hypo_SI5$h1.2[hypo_SI5$hypo_2 =="Disagree"] <- "2"
hypo_SI5$h1.2[hypo_SI5$hypo_2 =="Somewhat disagree"] <- "3"
hypo_SI5$h1.2[hypo_SI5$hypo_2 =="Neither agree nor disagree"] <- "4"
hypo_SI5$h1.2[hypo_SI5$hypo_2 =="Somewhat agree"] <- "5"
hypo_SI5$h1.2[hypo_SI5$hypo_2 =="Agree"] <- "6"
hypo_SI5$h1.2[hypo_SI5$hypo_2 =="Strongly agree"] <- "7"
hypo_SI5$h1.2 <- as.numeric(hypo_SI5$h1.2)
#inauth_2 
hypo_SI5$h2.2[hypo_SI5$inauth_2 =="Strongly disagree"] <- "1"
hypo_SI5$h2.2[hypo_SI5$inauth_2 =="Disagree"] <- "2"
hypo_SI5$h2.2[hypo_SI5$inauth_2 =="Somewhat disagree"] <- "3"
hypo_SI5$h2.2[hypo_SI5$inauth_2 =="Neither agree nor disagree"] <- "4"
hypo_SI5$h2.2[hypo_SI5$inauth_2 =="Somewhat agree"] <- "5"
hypo_SI5$h2.2[hypo_SI5$inauth_2 =="Agree"] <- "6"
hypo_SI5$h2.2[hypo_SI5$inauth_2 =="Strongly agree"] <- "7"
hypo_SI5$h2.2 <- as.numeric(hypo_SI5$h2.2)
#disingen_2
hypo_SI5$h3.2[hypo_SI5$disingen_2=="Strongly disagree"] <- "1"
hypo_SI5$h3.2[hypo_SI5$disingen_2=="Disagree"] <- "2"
hypo_SI5$h3.2[hypo_SI5$disingen_2=="Somewhat disagree"] <- "3"
hypo_SI5$h3.2[hypo_SI5$disingen_2=="Neither agree nor disagree"] <- "4"
hypo_SI5$h3.2[hypo_SI5$disingen_2=="Somewhat agree"] <- "5"
hypo_SI5$h3.2[hypo_SI5$disingen_2=="Agree"] <- "6"
hypo_SI5$h3.2[hypo_SI5$disingen_2=="Strongly agree"] <- "7"
hypo_SI5$h3.2 <- as.numeric(hypo_SI5$h3.2)
#cronbachs alpha for 3  hypocrisy items - time two
hypoSI5_df2 <- data.frame(hypo_SI5$h1.2, hypo_SI5$h2.2, hypo_SI5$h3.2)
summary(hypoSI5_df2)
describe(hypoSI5_df2)
psych::alpha(hypoSI5_df2) # raw = 0.94
#hypocrisy items over 0.6 so create a composite
hypo_SI5 <- mutate(hypo_SI5, 
                   SI5_hcomposite2 = 
                     ((hypo_SI5$h1.2 + hypo_SI5$h2.2 + hypo_SI5$h3.2)/3))

#Honesty time 1
#honest_freq, reverse code
hypo_SI5$hf1[hypo_SI5$lie_freq=="Not often at all"] <- "7"
hypo_SI5$hf1[hypo_SI5$lie_freq=="Not very often"] <- "6"
hypo_SI5$hf1[hypo_SI5$lie_freq=="Slightly often"] <- "5"
hypo_SI5$hf1[hypo_SI5$lie_freq=="Somewhat often"] <- "4"
hypo_SI5$hf1[hypo_SI5$lie_freq=="Moderately often"] <- "3"
hypo_SI5$hf1[hypo_SI5$lie_freq=="Very often"] <- "2"
hypo_SI5$hf1[hypo_SI5$lie_freq=="Extremely often"] <- "1"
hypo_SI5$hf1 <- as.numeric(hypo_SI5$hf1)
#honest_likely, reverse code
hypo_SI5$hl1[hypo_SI5$future_lie=="Not at all likely"] <- "7"
hypo_SI5$hl1[hypo_SI5$future_lie=="Not very likely"] <- "6"
hypo_SI5$hl1[hypo_SI5$future_lie=="Slightly likely"] <- "5"
hypo_SI5$hl1[hypo_SI5$future_lie=="Somewhat likely"] <- "4"
hypo_SI5$hl1[hypo_SI5$future_lie=="Moderately likely"] <- "3"
hypo_SI5$hl1[hypo_SI5$future_lie=="Very likely"] <- "2"
hypo_SI5$hl1[hypo_SI5$future_lie=="Extremely likely"] <- "1"
hypo_SI5$hl1 <- as.numeric(hypo_SI5$hl1)
#honest_extreme
hypo_SI5$he1[hypo_SI5$extreme_lie=="Not at all extreme"] <-  "1"
hypo_SI5$he1[hypo_SI5$extreme_lie=="Not very extreme"] <- "2"
hypo_SI5$he1[hypo_SI5$extreme_lie=="Slightly extreme"] <- "3"
hypo_SI5$he1[hypo_SI5$extreme_lie=="Somewhat extreme"] <- "4"
hypo_SI5$he1[hypo_SI5$extreme_lie=="Moderately extreme"] <- "5"
hypo_SI5$he1[hypo_SI5$extreme_lie=="Very extreme"] <- "6"
hypo_SI5$he1[hypo_SI5$extreme_lie=="The most extreme"] <- "7"
hypo_SI5$he1 <- as.numeric(hypo_SI5$he1)
#committment_honest_1
hypo_SI5$ch1[hypo_SI5$comm_h=="Not at all"] <- " 1"
hypo_SI5$ch1[hypo_SI5$comm_h=="Not very"] <- "2"
hypo_SI5$ch1[hypo_SI5$comm_h=="Slightly"] <- "3"
hypo_SI5$ch1[hypo_SI5$comm_h=="Somewhat"] <- "4"
hypo_SI5$ch1[hypo_SI5$comm_h=="Moderately"] <- "5"
hypo_SI5$ch1[hypo_SI5$comm_h=="Very"] <- "6"
hypo_SI5$ch1[hypo_SI5$comm_h=="Extremely"] <- "7"
hypo_SI5$ch1 <- as.numeric(hypo_SI5$ch1)
#look at different honesty items - 4
SI5_honesty_df <- data.frame(hypo_SI5$hf1, hypo_SI5$hl1, hypo_SI5$he1, hypo_SI5$ch1)
summary(SI5_honesty_df)
describe(SI5_honesty_df)
psych::alpha(SI5_honesty_df) # raw= 0.67
#over .6 so combine
hypo_SI5 <- mutate(hypo_SI5, 
                   SI_honest_composite = 
                     ((hypo_SI5$hf1 + hypo_SI5$hl1 + hypo_SI5$he1 + hypo_SI5$ch1)/4))

#Honesty composite time two

#honest_freq, reverse code
hypo_SI5$hf1.2[hypo_SI5$lie_freq2=="Not often at all"] <- "7"
hypo_SI5$hf1.2[hypo_SI5$lie_freq2=="Not very often"] <- "6"
hypo_SI5$hf1.2[hypo_SI5$lie_freq2=="Slightly often"] <- "5"
hypo_SI5$hf1.2[hypo_SI5$lie_freq2=="Somewhat often"] <- "4"
hypo_SI5$hf1.2[hypo_SI5$lie_freq2=="Moderately often"] <- "3"
hypo_SI5$hf1.2[hypo_SI5$lie_freq2=="Very often"] <- "2"
hypo_SI5$hf1.2[hypo_SI5$lie_freq2=="Extremely often"] <- "1"
hypo_SI5$hf1.2<- as.numeric(hypo_SI5$hf1.2)
#honest_likely, reverse code
hypo_SI5$hl1.2[hypo_SI5$future_lie2=="Not at all likely"] <- "7"
hypo_SI5$hl1.2[hypo_SI5$future_lie2=="Not very likely"] <- "6"
hypo_SI5$hl1.2[hypo_SI5$future_lie2=="Slightly likely"] <- "5"
hypo_SI5$hl1.2[hypo_SI5$future_lie2=="Somewhat likely"] <- "4"
hypo_SI5$hl1.2[hypo_SI5$future_lie2=="Moderately likely"] <- "3"
hypo_SI5$hl1.2[hypo_SI5$future_lie2=="Very likely"] <- "2"
hypo_SI5$hl1.2[hypo_SI5$future_lie2=="Extremely likely"] <- "1"
hypo_SI5$hl1.2 <- as.numeric(hypo_SI5$hl1.2)
#honest_extreme
hypo_SI5$he1.2[hypo_SI5$extreme_lie2=="Not at all extreme"] <-  "1"
hypo_SI5$he1.2[hypo_SI5$extreme_lie2=="Not very extreme"] <- "2"
hypo_SI5$he1.2[hypo_SI5$extreme_lie2=="Slightly extreme"] <- "3"
hypo_SI5$he1.2[hypo_SI5$extreme_lie2=="Somewhat extreme"] <- "4"
hypo_SI5$he1.2[hypo_SI5$extreme_lie2=="Moderately extreme"] <- "5"
hypo_SI5$he1.2[hypo_SI5$extreme_lie2=="Very extreme"] <- "6"
hypo_SI5$he1.2[hypo_SI5$extreme_lie2=="The most extreme"] <- "7"
hypo_SI5$he1.2 <- as.numeric(hypo_SI5$he1.2)
#committment_honest_1
hypo_SI5$ch1.2[hypo_SI5$comm_h2=="Not at all"] <- " 1"
hypo_SI5$ch1.2[hypo_SI5$comm_h2=="Not very"] <- "2"
hypo_SI5$ch1.2[hypo_SI5$comm_h2=="Slightly"] <- "3"
hypo_SI5$ch1.2[hypo_SI5$comm_h2=="Somewhat"] <- "4"
hypo_SI5$ch1.2[hypo_SI5$comm_h2=="Moderately"] <- "5"
hypo_SI5$ch1.2[hypo_SI5$comm_h2=="Very"] <- "6"
hypo_SI5$ch1.2[hypo_SI5$comm_h2=="Extremely"] <- "7"
hypo_SI5$ch1.2 <- as.numeric(hypo_SI5$ch1.2)
#look at different honesty items - 4
SI5_honesty_df2 <- data.frame(hypo_SI5$hf1.2, hypo_SI5$hl1.2, hypo_SI5$he1.2, hypo_SI5$ch1.2)
summary(SI5_honesty_df2)
describe(SI5_honesty_df2)
psych::alpha(SI5_honesty_df2) # raw= 0.70
#over .6 so combine
hypo_SI5 <- mutate(hypo_SI5, 
                   SI_honest_composite2 = 
                     ((hypo_SI5$hf1.2 + hypo_SI5$hl1.2 + hypo_SI5$he1.2 + hypo_SI5$ch1.2)/4))

#Moral
#time 1
#moral
hypo_SI5$m1[hypo_SI5$moral =="Not at all"] <- "1"
hypo_SI5$m1[hypo_SI5$moral =="Not very"] <- "2"
hypo_SI5$m1[hypo_SI5$moral =="Slightly"] <- "3"
hypo_SI5$m1[hypo_SI5$moral =="Somewhat"] <- "4"
hypo_SI5$m1[hypo_SI5$moral =="Moderately"] <- "5"
hypo_SI5$m1[hypo_SI5$moral =="Very"] <- "6"
hypo_SI5$m1[hypo_SI5$moral =="Extremely"] <- "7"
hypo_SI5$m1 <- as.numeric(hypo_SI5$m1)
#moral_2
hypo_SI5$m2[hypo_SI5$ethical=="Not at all"] <- "1"
hypo_SI5$m2[hypo_SI5$ethical=="Not very"] <- "2"
hypo_SI5$m2[hypo_SI5$ethical=="Slightly"] <- "3"
hypo_SI5$m2[hypo_SI5$ethical=="Somewhat"] <- "4"
hypo_SI5$m2[hypo_SI5$ethical=="Moderately"] <- "5"
hypo_SI5$m2[hypo_SI5$ethical=="Very"] <- "6"
hypo_SI5$m2[hypo_SI5$ethical=="Extremely"] <- "7"
hypo_SI5$m2 <- as.numeric(hypo_SI5$m2)
#moral_3
hypo_SI5$m3[hypo_SI5$trust =="Not at all"] <- "1"
hypo_SI5$m3[hypo_SI5$trust =="Not very"] <- "2"
hypo_SI5$m3[hypo_SI5$trust =="Slightly"] <- "3"
hypo_SI5$m3[hypo_SI5$trust =="Somewhat"] <- "4"
hypo_SI5$m3[hypo_SI5$trust =="Moderately"] <- "5"
hypo_SI5$m3[hypo_SI5$trust =="Very"] <- "6"
hypo_SI5$m3[hypo_SI5$trust =="Extremely"] <- "7"
hypo_SI5$m3 <- as.numeric(hypo_SI5$m3)
#moral composite
SI5_moral_df <- data.frame(hypo_SI5$m1, hypo_SI5$m2, hypo_SI5$m3)
summary(SI5_moral_df)
describe(SI5_moral_df)
psych::alpha(SI5_moral_df) # raw = 0.93
hypo_SI5 <- mutate(hypo_SI5, 
                   SI_moral_composite = ((hypo_SI5$m1+hypo_SI5$m2+hypo_SI5$m3)/3))

#time 2
#moral
hypo_SI5$m1.2[hypo_SI5$moral_2=="Not at all"] <- "1"
hypo_SI5$m1.2[hypo_SI5$moral_2=="Not very"] <- "2"
hypo_SI5$m1.2[hypo_SI5$moral_2=="Slightly"] <- "3"
hypo_SI5$m1.2[hypo_SI5$moral_2=="Somewhat"] <- "4"
hypo_SI5$m1.2[hypo_SI5$moral_2=="Moderately"] <- "5"
hypo_SI5$m1.2[hypo_SI5$moral_2=="Very"] <- "6"
hypo_SI5$m1.2[hypo_SI5$moral_2=="Extremely"] <- "7"
hypo_SI5$m1.2<- as.numeric(hypo_SI5$m1.2)
#moral_2
hypo_SI5$m2.2[hypo_SI5$ethical_2=="Not at all"] <- "1"
hypo_SI5$m2.2[hypo_SI5$ethical_2=="Not very"] <- "2"
hypo_SI5$m2.2[hypo_SI5$ethical_2=="Slightly"] <- "3"
hypo_SI5$m2.2[hypo_SI5$ethical_2=="Somewhat"] <- "4"
hypo_SI5$m2.2[hypo_SI5$ethical_2=="Moderately"] <- "5"
hypo_SI5$m2.2[hypo_SI5$ethical_2=="Very"] <- "6"
hypo_SI5$m2.2[hypo_SI5$ethical_2=="Extremely"] <- "7"
hypo_SI5$m2.2 <- as.numeric(hypo_SI5$m2.2)
#moral_3
hypo_SI5$m3.2[hypo_SI5$trust_2 =="Not at all"] <- "1"
hypo_SI5$m3.2[hypo_SI5$trust_2 =="Not very"] <- "2"
hypo_SI5$m3.2[hypo_SI5$trust_2 =="Slightly"] <- "3"
hypo_SI5$m3.2[hypo_SI5$trust_2 =="Somewhat"] <- "4"
hypo_SI5$m3.2[hypo_SI5$trust_2 =="Moderately"] <- "5"
hypo_SI5$m3.2[hypo_SI5$trust_2 =="Very"] <- "6"
hypo_SI5$m3.2[hypo_SI5$trust_2=="Extremely"] <- "7"
hypo_SI5$m3.2 <- as.numeric(hypo_SI5$m3.2)
#moral composite
SI5_moral_df2 <- data.frame(hypo_SI5$m1.2, hypo_SI5$m2.2, hypo_SI5$m3.2)
summary(SI5_moral_df2)
describe(SI5_moral_df2)
psych::alpha(SI5_moral_df2) # raw = 0.97
hypo_SI5 <- mutate(hypo_SI5, 
                   SI_moral_composite2 = ((hypo_SI5$m1.2 + hypo_SI5$m2.2 + hypo_SI5$m3.2 )/3))


#Does country moderate these effects?
hypo_SI5$Country <- as.factor(hypo_SI5$Country)
```

# Analysis

# Hypocrisy
```{r}
#Dataframe for Hypocrisy
hypo5_SI_df <-melt(hypo_SI5, 
                    id.vars=c("condition", "id", "proc", "Country"),
                    #measure command is for the DV
                    measure.vars=c("SI5_hcomposite","SI5_hcomposite2"),
                    variable.name="h5.time",
                    value.name="h5value"
)

#ANOVA
hSI5.afex <- aov_car(
  h5value ~ proc*h5.time + Error(id/h5.time),
  data = hypo5_SI_df)
summary(hSI5.afex)
anova_apa(hSI5.afex)
```

# Hypocrisy descriptives

```{r}
#Cells: Proclamation and Time
tapply(hypo5_SI_df$h5value, list(hypo5_SI_df$proc, hypo5_SI_df$h5.time),
       FUN = length)

tapply(hypo5_SI_df$h5value, list(hypo5_SI_df$proc, hypo5_SI_df$h5.time),
       FUN = mean)

tapply(hypo5_SI_df$h5value, list(hypo5_SI_df$proclamation, hypo5_SI_df$h5.time),
       FUN = sd)

#Across Proclamation
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc, FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$proc,FUN = length)

#Across Time
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$h5.time,FUN = length)

```

# Country and Hypocrisy (analysis, descriptives)

```{r}
#ANOVA
hSI5_c.afex <- aov_car(
  h5value ~ proc*h5.time*Country + Error(id/h5.time),
  data = hypo5_SI_df)
summary(hSI5_c.afex )
anova_apa(hSI5_c.afex )

#Country
tapply(hypo5_SI_df$h5value, hypo5_SI_df$Country,FUN = mean)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$Country,FUN = sd)
tapply(hypo5_SI_df$h5value, hypo5_SI_df$Country,FUN = length)


#Country*Time 
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = mean)
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = sd)
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = length)

#Cells
tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = mean)

tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = sd)

tapply(hypo5_SI_df$h5value, 
       list(hypo5_SI_df$proc, hypo5_SI_df$Country, hypo5_SI_df$h5.time), 
       FUN = length)
```

# Morality

```{r}
moral5_SI_df <-melt(hypo_SI5, 
                     id.vars=c("condition", "id", "proc", "Country"),
                     #measure command is for the DV
                     measure.vars=c("SI_moral_composite", "SI_moral_composite2"),
                     variable.name="m5.time",
                     value.name="m5value"
)

#ANOVA
m_SI5.afex <- aov_car(
  m5value ~ proc*m5.time + Error(id/m5.time),
  data = moral5_SI_df)
summary(m_SI5.afex)
anova_apa(m_SI5.afex)
```

# Morality descriptives

```{r}
#Cells: Proclamation and Time
tapply(moral5_SI_df$m5value , list(moral5_SI_df$proc, moral5_SI_df$m5.time),
       FUN = length)

tapply(moral5_SI_df$m5value , list(moral5_SI_df$proc, moral5_SI_df$m5.time),
       FUN = mean)

tapply(moral5_SI_df$m5value , list(moral5_SI_df$proclamation, moral5_SI_df$m5.time),
       FUN = sd)


#Across Proclamation
tapply(moral5_SI_df$m5value, moral5_SI_df$proc, FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$proc,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$proc,FUN = length)

#Across Time
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$m5.time,FUN = length)

```


# Country and morality (analysis, descriptives)

```{r}
#ANOVA
m_SI5_c.afex <- aov_car(
  m5value ~ proc*m5.time*Country + Error(id/m5.time),
  data = moral5_SI_df)
summary(m_SI5_c.afex)
anova_apa(m_SI5_c.afex)

#Country
tapply(moral5_SI_df$m5value, moral5_SI_df$Country,FUN = mean)
tapply(moral5_SI_df$m5value, moral5_SI_df$Country,FUN = sd)
tapply(moral5_SI_df$m5value, moral5_SI_df$Country,FUN = length)


#Country*Time 
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = mean)
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = sd)
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = length)


#Cells
tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = mean)

tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = sd)

tapply(moral5_SI_df$m5value, 
       list(moral5_SI_df$proc, moral5_SI_df$Country, moral5_SI_df$m5.time), 
       FUN = length)
```


# Honesty

```{r}
honest5_SI_df <-melt(hypo_SI5, 
                   id.vars=c("condition", "id", "proc", "Country"),
                   #measure command is for the DV
                   measure.vars=c("SI_honest_composite","SI_honest_composite2"),
                   variable.name="honest5.time",
                   value.name="honest5value"
)

#ANOVA
hon_SI5.afex <- aov_car(
  honest5value ~ proc*honest5.time + Error(id/honest5.time),
  data = honest5_SI_df)
summary(hon_SI5.afex)
anova_apa(hon_SI5.afex)
```

# Honesty descriptives

```{r}
#Cells: Proclamation and Time
tapply(honest5_SI_df$honest5value , list(honest5_SI_df$proc, honest5_SI_df$honest5.time),
       FUN = length)

tapply(honest5_SI_df$honest5value , list(honest5_SI_df$proc, honest5_SI_df$honest5.time),
       FUN = mean)

tapply(honest5_SI_df$honest5value , list(honest5_SI_df$proclamation, honest5_SI_df$honest5.time),
       FUN = sd)


#Across Proclamation
tapply(honest5_SI_df$honest5value, honest5_SI_df$proc, FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$proc,FUN = sd)
tapply(honest5_SI_df$honest5value, hhonest5_SI_df$proc,FUN = length)

#Across Time
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = sd)
tapply(honest5_SI_df$honest5value, honest5_SI_df$honest5.time,FUN = length)

```

# Honesty t-test

```{r}
#T-test at time two
t.test(SI_honest_composite2 ~ proc, hypo_SI5, var.equal = TRUE)
t_apa(t.test(SI_honest_composite2~ proc, hypo_SI5, var.equal = TRUE))
```

# Country and honesty (analysis, descriptives)

```{r}
#ANOVA
hon_SI5_c.afex <- aov_car(
  honest5value ~ proc*honest5.time*Country + Error(id/honest5.time),
  data = honest5_SI_df)
summary(hon_SI5_c.afex)
anova_apa(hon_SI5_c.afex)

#Country
tapply(honest5_SI_df$honest5value, honest5_SI_df$Country,FUN = mean)
tapply(honest5_SI_df$honest5value, honest5_SI_df$Country,FUN = sd)
tapply(honest5_SI_df$honest5value, honest5_SI_df$Country,FUN = length)


#Country*Time 
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = mean)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = sd)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = length)

#Country*proc 
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$proc), 
       FUN = mean)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$proc), 
       FUN = sd)
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$Country, honest5_SI_df$proc), 
       FUN = length)

#Cells
tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$proc, honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = mean)

tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$proc, honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = sd)

tapply(honest5_SI_df$honest5value, 
       list(honest5_SI_df$proc, honest5_SI_df$Country, honest5_SI_df$honest5.time), 
       FUN = length)
```

# Trust - Advice Game

